### 2019-04-25 Paper_neural_coarse_graining_of_consciousness.tex
Updates from Overleaf

\documentclass[utf8]{article}

%% Language and font encoding
\usepackage[english]{babel}
%\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}

%% Sets page size and margins
%\usepackage[a4paper, top=3cm,bottom=2cm,left=3cm,right=3cm,marginparwidth=4cm]{geometry}
\usepackage[papersize={10in, 12in}, top=3cm,bottom=2cm,left=2in,right=2in,marginparwidth=1.8in]{geometry}

%% Title style
\usepackage{stringstrings}
\usepackage[explicit]{titlesec}
\usepackage{sectsty}

%% ============================== Useful packages ============================= %
\usepackage[dvipsnames,table,xcdraw]{xcolor}
\usepackage[round]{natbib}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage[colorlinks=true, allcolors=blue]{hyperref}
\usepackage{authblk}
\usepackage{float}
\usepackage{tikz}

%% ================================== acronym ================================= %
\usepackage{acronym}
\newacro{ntic}{non-trivial informational closure}
\newacro{ic}{informational closure}
\newacro{cg}{coarse-grain}
\newacro{cging}{coarse-graining}
\newacro{cged}{coarse-grained}
\newacro{ncg}{neural coarse-graining}

% The name of our theory
% ----------------------------------------------------------------------------
\newcommand{\tnamefull}{The Neural Coarse-graining Theory of Consciousness}
\newcommand{\tname}{NCGT} 	% TheoryNameShort
\newacro{\tname}{\tnamefull}
%\newacro{NCGT}{the neural coarse-graining theory of consciousness}

% =================================== Macro ================================== %
\usepackage[colorinlistoftodos]{todonotes}
\usepackage[at]{easylist}
\usepackage{tcolorbox}
\tcbuselibrary{skins}
\usepackage{comment}
\usepackage[framemethod=tikz]{mdframed}
\usetikzlibrary{shadows}
\usepackage{soul}
\usepackage{version}

% Meaning of colours --------------------------------------------------------- %
%	Red: Important and Critical
%	Orange: Todo
%	Blue: Topic and Guideline
%	Purple: Murmur
%	Green: Question, Call for help, Open for opinions and comments
%	Brown: Need Wording
% ---------------------------------------------------------------------------- %

% Real content
	% Outline items that can be integrated into main text
		\newenvironment{ants}
			{
			 \begin{easylist}[itemize]
		 	}
			{
			\end{easylist}
			} %

	% Writing Materials
    \newenvironment{WritingMaterials} %
    	{
            \begin{tcolorbox}[enhanced,
                title=-,
                size=small,
                colbacktitle=Aquamarine,
                drop fuzzy shadow,
                fontupper=\small,
                boxrule=0.4pt,
                colback=Aquamarine!10!white,
                sharp corners]
                Writing Materials
            \end{tcolorbox}
            \begin{easylist}[itemize]
    	}
    	{
            \end{easylist}  
            \begin{tcolorbox}[enhanced,
                halign=flush right,
                halign title=right,
                size=small,
                colbacktitle=Aquamarine,
                drop fuzzy shadow,
                fontupper=\small,
                boxrule=0.4pt,
                colback=Aquamarine,
                colupper=White,
                sharp corners]
                Writing Materials -
            \end{tcolorbox}        
    	}

    % \excludeversion{WritingMaterials}

% Functional content
	% Quotes: green
		\newcommand{\rewrite}[1]{\textcolor{ForestGreen}{\textit{"#1"}}\newline}

	% todo: orange
		% text todo
		\newcommand{\toWrite}[1]{\noindent
			\textcolor{Orange}{\textbf{[[ #1 ]]}}}

	% figure todo
        \newcommand{\includegraphicsTodo}[2][]{%
            \tcbox[enhanced,
                center,
            	adjusted title=\large To Be Modified ...,
            	halign title=center,
            	attach boxed title to top left={yshift=-3mm, xshift=1cm,yshifttext=-1mm}, boxed title style={drop fuzzy shadow},
            	colbacktitle=RedOrange!70!black,
            	coltitle=white,
            	colframe=RedOrange!50!black,
            	colback=white
        	]{\includegraphics[#1]{#2}}}

		% figure todo callout
        \newcommand{\needfig}[1]{%
			\ifthenelse{\equal{#1}{}}{%
				\todo[color=White, linecolor=Orange, bordercolor=RedOrange]{\textcolor{RedOrange}{Fig}}}{%
				\todo[color=White, linecolor=Orange, bordercolor=RedOrange]{\textcolor{RedOrange}{Fig: #1}}%
			}%
		}

		% rewording
		\newcommand{\rewording}[1]{\textcolor{RawSienna}{[[ REWORDING | #1 ]]}}

		% Need reference
		\newcommand{\needref}[1]{%
			\ifthenelse{\equal{#1}{}}{%
				\todo[color=White, linecolor=Orange, bordercolor=Orange]{\textcolor{Orange}{Ref}}}{%
				\todo[color=White, linecolor=Orange, bordercolor=Orange]{\textcolor{Orange}{Ref: #1}}%
			}%
		}

	% Highlight: Yellow or Red
		% Highlight only
		\newcommand{\highlight}[2][Yellow!75!white]{\colorbox{#1}{#2}}

		% Highlight and comment
        \newcommand{\highlightAndComment}[3][Yellow]{\sethlcolor{#1}\hl{#2}\todo[color=#1, linecolor=Yellow]{#3}}

		% Critical point
		\newcommand{\critical}[1]{%
			\todo[color=OrangeRed!80!white]{#1}
		}

	% idea: Purple
		% text idea
			\newcommand{\idea}[2][Plum]{\noindent
				\textcolor{#1}{[[ #2 ]]}}

		% box idea
			\newcommand{\ideaBox}[1]{
			    \vspace{2mm}
				\begin{tcolorbox}[enhanced,%
                    title=-,
                    center,
                    fontupper=\small,
                    lifted shadow={1mm}{-2mm}{3mm}{0.1mm}{black!50!white},%
                    boxrule=0.4pt,
                    width=9cm,
                    colback=Thistle!50!white,
                    sharp corners]
					#1
				\end{tcolorbox}
				\vspace{2mm}
			}

		% call-out idea
			\newcommand{\ideaCallout}[1]{\todo[color=Thistle!50!white, size=\small]{#1}}

	% communication: green
		% call for help
			\newcommand{\needhelp}[1]{\todo[color=SpringGreen]{[Need Help]: #1}}

		% comment
			% comment by authors
			\newcommand{\addcomment}[3][\empty]{\todo[color=SkyBlue]{Comment [#2]:\newline#3}\colorbox{SkyBlue}{#1}}

			% usage:
			% \addcomment{auther}{comment text}
			% or
			% \addcomment[highlighted text]{auther}{comment text}
			%
			% e.g.
			% It's a \addcomment[beautiful]{Acer}{need a reference} day

    % backup: 
    \newenvironment{backup}
    {

        \begin{tcolorbox}[enhanced,
            title=-,
            size=small,
            colbacktitle=black!70!white,
            colback=black!10!white,            
            drop fuzzy shadow,
            fontupper=\small,
            boxrule=0.4pt,
            sharp corners]
            Backup
        \end{tcolorbox}
    }
    {
        \begin{tcolorbox}[enhanced,
            halign=flush right,
            halign title=right,
            size=small,
            colbacktitle=black!10!white,
            colback=black!70!white,
            drop fuzzy shadow,
            fontupper=\small,
            boxrule=0.4pt,
            colupper=White,
            sharp corners]
            Backup -
        \end{tcolorbox}    
    }
    % \excludeversion{backup}

% review loop annotation
    \usepackage[xcolor, outerbars]{changebar}
    \cbcolor{red}

    % start anchor: \rlstart
    \newcommand{\rlstart}[1]{  %
        \setlength\changebarwidth{#1pt*2}  %
        \hspace*{-40pt}
        \cbstart{\textcolor{red}{\newline\textbf{iteration #1}}\newline}}

    % end anchor: \rlend
    \newcommand{\rlend}{\cbend}

% quote
\newcommand{\myQuote}[1]{\textit{``#1''}}

% ============================================================================ %
%                                     Title                                    %
% ============================================================================ %
\title{A neural coarse graining theory of consciousness/\newline Non-trivial Informational closure through neural coarse-graining as the Fundamental Informational Correlates of Consciousness }

% ============================================================================ %
%                                    Authors                                   %
% ============================================================================ %
\author[1]{Acer Y.C. Chang\thanks{acercyc@araya.org}}
\author[1]{Martin Biehl\thanks{martin@araya.org}}
\author[1]{Yen Yu\thanks{martin@araya.org}}
\author[1]{Ryota Kanai\thanks{kanair@araya.org }}
\affil[1]{ARAYA, Inc., Tokyo, Japan}

% ============================================================================ %
%                                     Body                                     %
% ============================================================================ %
\begin{document}
	\maketitle
	\tableofcontents

	\begin{abstract}
		Neural systems process information through different levels of organisation in a hierarchical manner. Information at lower levels is finer-grained and can be coarse-grained for higher level computation. However, one is aware of information processed only at specific levels. Theorists have addressed this issue. For example, the intermediate level theory of consciousness suggests that the intermediate level seems to be privileged with respect to consciousness. It is true that we do not experience information processed by individual neurons which is always highly noisy. Besides, we have no conscious experience from interpersonal activities albeit massive interactions among individuals. Instead, neurophysiological evidence has been showing that conscious experience tends to co-vary with information encoded in coarse-grained neural states such as neural population codes. We argue that the neural states within the scope of the informational closure determine the contents of consciousness and brain processes outside apart from the representations of that level remain unconscious. This argument suggests a distinction between conscious and unconscious processing and provides a generic computational framework. Finally, using the deep learning network, we can measure informational closure in deep hidden layers. Our preliminary results show that informational closure representation emerged after learning. We further decoded the information from the representation and compared it with human conscious perception.
	\end{abstract}

	\section*{Keywords:}
	Keywords: theory of Consciousness, informational closure, neural coarse-graining, level of analysis

    \newpage
    \section*{Not decided terminology}
        \begin{ants}
            @ information * in the NTIC process
            @ Full and short name of this theory
            @ core "?" (entity) for conscious content 
            @ our theory? framework? proposal? 
            @ system? process?
            @ variable? node? element? member?
        \end{ants}

	% ============================================================================ %
	%                                     Start                                    %
	% ============================================================================ %

    \newpage
	\section{Introduction}

		%% Story about a cell
		Imagine you are a neuron in Alice's brain. Your daily work is to collect neurotransmitters through dendrites from other neurons, accumulate membrane potential, and finally send signals to other neurons through action potentials along axons. However, you have no idea that you are one of neurons in Alice's supplementary motor area and involved in many motor control processes for Alice's action, for example, grabbing a cup. You are ignorant of intentions, goals, and motor plans that Alice has at every moment even though you are part of the physiological substrate responsible for all those actions.
		A similar story also applies to Alice's conscious mind. To grab a cup, for example, Alice is conscious of her intention and visuosensory experience of this action. However, her conscious experience does not show the dynamic of your membrane potential and about action potentials you send to other neurons every second. That is, information in Alice's conscious experience does not contain information involved in your information processing.

		\toWrite{maybe need a transition sentence here}

		%% scale
		It seems to be true that we are unable to consciously access information processed at every scale in the neural system. Only information at certain levels of coarse-graining can become conscious contents. At microscopic levels of neural systems, information processing in individual neurons is highly noisy and state transitions of neurons are extremely stochastic \citep{Goldwyn2011, White2000}. However, instead of stochastic action potentials and fluctuation of random noise at microscopic levels, what we are aware of in our conscious mind shows astonishing stability and robustness against the ubiquitous noise in the neural system \citep{mathis1995computational}. Likewise, conscious experience does not associate with states of the whole brain level because we have known that some parts of the neural system contribute very little to conscious experience (the cerebellum for example \citep{lemon2010life}). Additionally, we do not  experience "super-consciousness" when we have massive inter-individual interactions with other human-beings. Even though evidence has shown several types of collective information processing at human social groups levels exist \citep{malone2015handbook}, information processed at this level seems to depart from our individual conscious contents.

		%% our argument
		In this article, we propose a new theory of consciousness, called\ac{\tname}. This proposal states that consciousness does not rest on particular neural architectures or locations in the neural systems. Instead, we argue that consciousness correlates with information processing at a certain coarse-grained level where the neural systems create a high degree of non-trivial informational closure (NTIC). We further postulate that the \textit{level} of consciousness corresponds to the degree of NTIC and the \textit{contents} of consciousness corresponds to the state of the NTIC process (for the level versus content of consciousness see \cite{laureys2005neural, overgaard2010neural}).

		% information-based claim 
		Our theory takes a strong assumption that consciousness is information-based, information correlates of consciousness (ICC)\todo{Complete this argument}

		%% About this paper
		Our theory rests on two core concepts: non-trivial informational closure and neural coarse- graining. In this article, we first introduce non-trivial informational closure and its importance to information processing for human scale agents. We next argue that through coarse-graining the human neural system can achieve non-trivial informational closure at a specific coarse-grained level. We then propose that the state of the informational closure correlates with the state of consciousness for both levels and contents which can be explained, quantified, and predicted computationally by this theory. We also address how this theory can concisely explain empirical results from previous studies and reconcile several current major theories of consciousness. Finally, we provide predictions and testable approaches for this theory.

		% TODO: is figure needed?
		\idea{Do I need a figure?, Something like this one?}
		\begin{figure}[H]
			\includegraphicsTodo[width=\textwidth/2]{WritingMaterials/PDFXCview_2018-06-11_13-37-34.png}
			\cite{pennartz2017consciousness}
			\caption{xxxx}
	   	\end{figure}

		%% backup point
		\begin{comment}
			@ consciousness is information

			@ conscious contents
				@@ \toWrite{lower level}
				@@ Information processing of individual neurons are noisy.
				@@ We don't have conscious content changes when individual neurons fire action potentials.
				@@ Don't even mention ion channel dynamic.

				@@ \toWrite{Higher-level dynamic}

			@ For human, physics at our body scale are nearly follow classic physics, which is deterministic.

			@ \toWrite{Human tendency for active prediction }
				@@ \cite{Stahl2015} \rewrite{
					Given the overwhelming quantity of information available from the environment, how do young learners know what to learn about and what to ignore? We found that 11-month-old infants (N = 110) used violations of prior expectations as special opportunities for learning. The infants were shown events that violated expectations about object behavior or events that were nearly identical but did not violate expectations. The sight of an object that violated expectations enhanced learning and promoted information-seeking behaviors; specifically, infants learned more effectively about objects that committed violations, explored those objects more, and engaged in hypothesis-testing behaviors that reflected the particular kind of violation seen. Thus, early in life, expectancy violations offer a wedge into the problem of what to learn.}

			@ Intuitive physics \needref{Intuitive physics}

		\end{comment}

	\section{Non-trivial informational closure}
		\ideaBox{I am still not sure we should go for NTIC without describe my intuition about consciousness and closure? Or we should start with my intuition. Or we should postpone to explain the intuition in Chapter 4?}

		The notion of non-trivial informational closure (NTIC) is introduced by \cite{BERTSCHINGER.2006}. The concept of closure is closely related to system identification in systems theory. One can define a system from its environment by computing the closureness of the system \citep{maturana1991autopoiesis, rosen1991life, pattee2012evolving, luhmann1995probleme}. The closureness can be further quantified by information theory.

		\begin{WritingMaterials}
			@ Consciousness as an intrinsic information. Therefore, information should be self-define. This means the boundary of conscious content should be related to informational closure.

			@ \idea{should we describe the intuition of boundary problem here?}

			@ ============================================================================

			@ \rewrite{
				The notion of closure plays a prominent role in systems theory where it is used to identify or define the system in distinction from its environment} \cite{BERTSCHINGER.2006}

			@ \rewrite{
				Our theoretical interest concerns the type of system that is a unity for and by itself and not only for an external observer distinguishing some entity from the rest of the world. This requires a system that can be described as a whole without reference to its environment. In systems theory, this property is usually referred to as closure.}\citep{BERTSCHINGER.2006}

			@ \rewrite{
				These concepts of closure play an important role in the architecture of systems
				theory, because they are used to
				1. define the system (in distinction to its environment) and to
				2. explain the autonomy of the system.}\citep{BERTSCHINGER.2006}

			@ \rewrite{
				Informational closure: The higher process is informationally closed, i.e., there is no information flow from the lower to the higher level. Knowledge of the microstate will not improve predictions of the macrostate.} \citep[p. 4]{PFANTE.2014}

		\end{WritingMaterials}

		% Definition of informational closure
			\noindent
			Information flow $J_{t}$ from the environment $E$ to a system $Y$ at time $t$ can be defined as the conditional mutual information $I$ between the system future state $Y_{t+1}$ and the current environment current state $E_{t}$ given the current system state $Y_{t}$

				\begin{equation}\label{eq:InformationFlow}
				\left.\begin{array}
				{rl}{J_{t}(E \rightarrow Y )} & {:= I(Y_{t+1};E_{t}|Y_{t})} \\
				%{ } & { \ = H(Y_{t+1}|Y_{t})-H(Y_{t+1}|Y_{t},E_{t})} \\
				%{ } & { \ = H(E_{t}|Y_{t})-H(Y_{t}|Y_{t},Y_{t+1})} \\
				%{ } & { \ = H(E_{t}|Y_{t})-H(E_{t}|Y_{t},Y_{t+1})}\\
				{ } & { \ = I(Y_{t+1};E_{t}) - (I(Y_{t+1};Y_{t})-I(Y_{t+1};Y_{t}|E_{t}))}
				\end{array}\right.
				\end{equation}

				\begin{figure}
					\includegraphics[width=\textwidth]{WritingMaterials/SystemAndEnv.pdf}
					\caption{Figure adapted from \cite{BERTSCHINGER.2006}}
					\label{fig:SystemAndEnv}
				\end{figure}

			\noindent
			\cite{BERTSCHINGER.2006} defines that a system is informational closured when information flow from the environment to the system is close to zero.

				\begin{equation}
				J_{t}(E \rightarrow Y )=0
				\end{equation}

			% ------------------------------- trivial case ------------------------------- %
			\noindent
			Achieving information closure (minimising $J_t$) could be trivial, which means the environment and the system are entirely independent of each other.

				\begin{equation}
				\begin{aligned}
				{I(Y_{t+1};E_{t})=0}&&{\Rightarrow}&&{J_{t}(E \rightarrow Y )=0}
				\end{aligned}
				\end{equation}

			% -------------------------------- non-trivial ------------------------------- %
			\noindent
			However, informational closure can be achieved non-trivially. In the non-trivial case, the system trying to encode information about the environmental dynamics can also be informational closured. This means

				\begin{equation}
				I(Y_{t+1};E_{t}) > 0
				\end{equation}

			\noindent
			This also implies
				\begin{equation}
					I(Y_{t+1};Y_{t})-I(Y_{t+1};Y_{t}|E_{t}) > 0
				\end{equation}

			\noindent
			And, non-trivial informational closure can be defined as
				\begin{equation}
				\left.\begin{array}
				{rl}{NTIC} & {:=I(Y_{t+1};Y_{t})-I(Y_{t+1};Y_{t}|E_{t})}\\
				{ } & {\ =I(Y_{t+1};E_{t})-I(Y_{t+1};E_{t}|Y_{t})}
				\end{array} \right.
				\end{equation}

			\noindent
			And, Maximising NTIC is equivalent to
				\begin{equation}\label{eq:nticObjective}
				\begin{aligned}
				& \text{maximise} & { } & I(Y_{t+1};Y_{t}) & { } & \text{and} \\
				& \text{minimise} & { } & I(Y_{t+1};Y_{t}|E_{t}) & { }
				\end{aligned}
				\end{equation}

			\noindent
			This implies the system contains in itself the information of its own future and the self-predictive information is gained from the information about the environment. Therefore, to achieve NTIC, the system can internalizes and synchronises the dynamics of the environment, i.e. modelling the environment. Furthermore, having high degrees of NTIC entails having high predictive power about the environment. This gives biological agents a great functional and evolutional advantage to achieve NTIC in their information processing systems. Practically, \cite{guttenberg2016neural} proposed that NTIC can be achieved by maximising the predictive power about the environment and the self-predictive information of the system concurrently.

			% Biological evidence of informational closure in the neural system
			Though the significant advantage for biological systems to achieve NTIC, to our knowledge, studies directly examining NTIC in biological systems are limited. However,  recent studies have showed relevant properties in the visual system of salamanders. By examining the salamander retina, in two studies \citep{Palmer2015, sederberg2018learning} the authors found that the a large groups of neural populations of retinal ganglion cells encoded predictive information about external stimuli also had high self-predictive information about their own future states (see Figure~\ref{fig:sederberg2018learning}), therefore, in line with the characteristic of NTIC. Therefore, the self-predictive information of the neural populations can guides prediction about external stimuli without reference to stimulus parameters explicitly. Moreover, the internal predictability can be generalised to different stimulus classes suggesting the tendency to internalise the information of environmental dynamics in the neural populations. \toWrite{Add Some ending sentences}

			\begin{figure}[H]
				\includegraphicsTodo[width=\textwidth]{WritingMaterials/Palmer2015.png}
				\caption{Figure adapted from \cite{sederberg2018learning}}
				\label{fig:sederberg2018learning}
			\end{figure}

			\begin{comment}
				@ ===

				@ \rewrite{
					Internal information reflects the spatial and temporal correlations in the stimulus.}

				@ \rewrite{predictive information is encoded synergistically.}

				@ \rewrite{
					in recordings of populations of RGCs of salamander retina driven by a simple stimulus with partially predictable dynamics, joint activity patterns transmit information that is predictive of future stimuli }

				@ \rewrite{
					We examined whether the temporal correlations within populations of RGCs can be used to guide the search for readouts of predictive information.}

				@ \rewrite{
					We showed that groups of cells with high external, stimulus-predictive information also had high internal predictive information on two classes of stimuli, }

				@ \rewrite{
					Very simple learning rules could find near-optimal readouts of predictive information without any external instructive signal. This suggests that bottom-up prediction may play an important role in sensory processing}

				@ \rewrite{
					Internal predictive information can guide stimulus prediction without explicit reference to stimulus parameters.}

				@ \rewrite{
					Word–word internal predictive information is correlated with word–stimulus predictive information across sets of four cells.}

				@ They also showed generalization of internal predictability across stimulus. This suggests .... what?

				@ \rewrite{
					The generalization of internal predictability across stimulus classes partially reflects the ability of the retina to adapt to the statistics of stimuli}

				@ \cite{Palmer2015}
				@ \rewrite{
					Groups of cells in the retina carry information about the future state of their own activity, and we show that this information can be compressed further and encoded by downstream predictor neurons that exhibit feature selectivity that would support predictive computations.}

				@ \rewrite{
					It seems natural to phrase the problem of prediction in relation to the visual stimulus, as in Fig. 3, but the brain has no direct access to visual stimuli except that provided by the retina. Could the brain learn, in an unsupervised fashion, to predict the future of retinal outputs? More precisely, if we observe that a population of retinal ganglion cells generates the word w t at time t, what can we say about the word that will be generated at time t + Δ t in the future? The answer to this question is contained in the conditional distribution of one word on the other, P ð w t +Δ t j w t Þ } \url{http://tinyurl.com/y9zmhlln}

				@ \rewrite{
					larger groups of cells carry predictive information for hundreds of milliseconds, }

			\end{comment}

			%% backup
			\begin{comment}
				@ Accurately model deterministic environment
				@ \rewrite{
					This demonstrates that a system exhibiting certain internal regularities as measured by $A^* = MI(Sn+1; Sn)$ can achieve informational closure either by gaining information about the environment or by increased autonomy, i.e. by becoming unpredictable or uncontrollable from the (13) environment. Therefore, information about the environment, i.e. modeling, and autonomy can be considered as complementary strategies for achieving informational closure.}

				@ By Action

				@ In the next section, we claim that the neural system achieve NTIC through coarse-graining.
			\end{comment}

		\subsection{Informational closure and level identification \ideaCallout{maybe not necessary}}

		\subsection{Biological Creature may try to achieve closure even the environment is not \ideaCallout{Maybe not necessary}}

	\section{Neural coarse-graining}

		%% stochasticity at microscopic levels
		Nevertheless, to achieve information closure (so as NTIC) in highly stochastic systems (e.g., the neural system) is challenging. The current states of the system have low predictability of its future states due to the stochasticity. Information processing in the neural system is suffered from multiple noise sources throughout, including sensory, cellular, electrical, and synaptic noises. Previous studies have shown that states of neurons have large trial-to-trial variability at the cellular level. That is, the same pattern of activity never occurs twice even when the same stimulus is presented. Neurons are inevitably subject to thermal fluctuations and other physical noises \citep{faisal2008noise}. Furthermore, environmental information is always only partial observable to individual sensors and neurons which only receive little amount of information from the environment. Therefore, self and environmental predictive information is difficult to be represented at the cellular level. It is implausible to construct NTIC processes at microscopic levels.

        %% Our argument
		However, we argue that, by coarse-graining microscopic neural states, the neural system is able to achieve NTIC at certain coarse-grained macroscopic levels. To encode information in coarse-grained variables is a way to encode stable and robust information in neural system and overcome the difficulties to achieve NTIC at microscopic levels. Coarse-graining in this paper is referred to many-to-one functions that map microscopic states to macroscopic states.\needref{Do we need reference?}. In other words, a number of different micro-states realise the same value of the macro-variable \citep{price2007causation}. This is a common strategy that we can see in large number of previous neurophysiological studies. For example, in the temporal domain, neural spikes across time can be coarse-grained as spiking rate variables, known as rate coding \citep{adrian1926impulses, gerstner2002spiking, maass2001pulsed, panzeri2015neural, stein2005neuronal}. Neurons encode stimulus intensity by increasing or decreasing firing rate. \citep{kandel2000principles}. In this coding scheme, individual neural spikes in a transient time span is not meaningful and stochastic \citep{stein2005neuronal}. In contrast, rate codes are relative stable and are highly robust against noise causing variation of inter-spike intervals.

		% population code
		Another example of coding strategy using coarse-graining is population coding. In this coding scheme, information is represented by joint spatiotemporal activities of several neurons. Therefore, the information is encoded in coarse-grained variables whose values are jointly determined by neural activation patterns within a neural population \citep{kristan1997population, pouget2000information, binder2009encyclopedia, QuianQuiroga2009}. In such case, activities of every single neuron is not informative and stochastic. Instead, coarse-grained variables (such as population averaging and population vector) are able to represent information stably. Encoding information at coarse-grained levels allow the neural system ignores certain causal interactions relevant to fine-grained level of description \citep{Woodward2007-WOOCWA}.

		% neural coarse-graining by Nic
		It has been empirically implemented that NTIC can be achieved by coarse-graining snesory inputs in artificial neural networks. \citep{guttenberg2016neural} proposed a "neural coarse-graining (NCG)" architecture (fig.\ref{fig:NCG}) which aims to captures the emergent large-scale dynamics in the environment. The NCG network learns to coarse-grain input signals and extract latent parameters which are both predictive and predictable in the input signal and therefore achieves NTIC by building a higher-level representation of the underlying dynamics in the deep layers. More importantly, using this architecture, agents can process information and act at coarse-grained macroscopic levels.

		\begin{figure}
			\includegraphicsTodo[width=0.8\textwidth]{WritingMaterials/PDFXCview_2018-06-08_14-24-03.png}
			\caption{NCG \idea{I need to simplify this figure}\citep{guttenberg2016neural}}
			\label{fig:NCG}
		\end{figure}

		%% not monotonic
		It is important to note that NTIC should not be a monotonic function of scale of coarse-graining. Overly coarse-graining system states can lead to low degrees of NTIC. For example, in an extreme scenario, when all microscopic states map to a single macroscopic variable, the macroscopic level does not have enough information capacity and thus losses  the self and environmental predictive power. This notion is also supported by empirical evidence. \cite{sederberg2018learning} showed that the efficiency of reading out  self-predictive information of neural population is higher when cell number in populations is 4 than 7 and 10-cell sets. This implies an optimal coarse-graining scale for NTIC processes. % Perhaps the best way to combine more than four cells is to break down the readout into indivisible units of four cells, which are later recombined in subsequent processing.}\citep{sederberg2018learning}

        %% Link to consciousness

        At the physical scale which human being live in, the environmental dynamics is nearly deterministic following the laws of classical physics. It gives agents living at this physical scale great advantages if the agents can build NTIC process internally. Therefore, to coarse-grain microscopic states is necessary

        %This means that it is possible for agents to live at this physical scale to build NTIC process internally.
        % More importantly, the information processing related to consciousness should not be situated at this level. Otherwise our conscious percept should be very noisy and unstable.

		\begin{WritingMaterials}
			@ \rewrite{
				Coarse-graining: a method of reducing the complexity of a system by treating groups of atoms/molecules as single quasi-particles CG: coarse-grained}

			@ neural system use population coding and temporal coding to fight against noise.

			@ Therefore, even though the low level information processing is noisy, it is possible that the neural system achieve NTIC at a coarse-grained level.

			@ This implies that the information about the environmental dynamic should be represented at a certain coarse-grained level rather then other levels.

			%% Macroscale Deterministic
			@ The environment that human scale agents interact with is approximately govern by Newton's law and therefore the state transitions are nearly deterministic.\needhelp{Is there any good ref I can cite?}

			@ \idea{Need something here}

			%% coarse-graining is necessary
			@ Hence, to coarse-grain states of microscopic levels is necessary to represent and model the human-scale environment state and dynamics.

			@ Coarse-graining is necessary to resist noise

			@ \rewrite{ The population will therefore be relatively insensitive to the loss of
				cells or noise in a small number of cells} \cite{eurich2000multidimensional}

		\end{WritingMaterials}

		\begin{WritingMaterials}

			@ Studies have shown that coarse-graining is a common way that the neural system cope with inevitable noise at microscopic levels.

			@ \rewrite{Because the sequence of action potentials generated by a given stimulus varies from trial to trial, neuronal responses are typically treated statistically or probabilistically}

			@ Note that, information processing related to consciousness should not be situated at this level. Otherwise our conscious percept should be very noisy and unstable.

		\end{WritingMaterials}

			\begin{WritingMaterials}
				@ Population coding

					@@ review ref

						@@@ \cite{Stanley2013}

						@@@ \cite{QuianQuiroga2009}

					@@ \rewrite{
						Averaging is used in many neural systems in which information is encoded as patterns of activity across a population of neurons that all subserve a similar function (for example, see REFs 140,141 )}
										140. Georgopoulos, A., Schwartz, A. \& Kettner, R. Neuronal population coding of movement direction. Science 233, 1416–1419 (1986). 141. Lee, C., Rohrer, W. H. \& Sparks, D. L. Population coding of saccadic eye movements by neurons in the superior colliculus. Nature 332, 357–360 (1988).

					@@ \rewrite{
						Electrophysiological studies in the monkey have shown that behaviourally relevant signals are averaged not only across neuronal populations but also over time in the formation of a behavioural decision 156 .} 156. Gold, J. I. \& Shadlen, M. N. Representation of a perceptual decision in developing oculomotor commands. Nature 404, 390–394 (2000).

					@@ \rewrite{A distributed representation of information of this type is more robust to the effects of noise.}

					@@ \rewrite{
						Neural population code: the set of response features of a population of neurons that carry all information about the considered stimuli. These features consist of spatio-temporal sequences of action potentials distributed across neurons and/or time.}

					@@ The diverse response selectivity of sensory neurons

					@@ \rewrite{
						How a neural population represents information is partly determined by the diverse selectivity of individual neurons \cite{Shamir2014}}

				@ sensory hierarchy
					@@ sensory hierarchy also shows characteristic of coarse-graining

					@@ Due to partial information that sensors can receive

					@@ To form complex representation like shape, objects, coarse-graining is necessary.

					@@ Through coarse-graining, \highlightAndComment{higher level}{might be confusing, need to think about the terminology here} cortical areas can integrate those partial information to infer hidden causes.

			\end{WritingMaterials}

			\begin{WritingMaterials}
				@ Achieving NTIC is the key objective to to extract out latent control parameters in the environment.

				@ Through two objectives during training, the model can achieve NTIC.

				@ this can be achieved by maximising the self-predictive power of deep layers and its entropy through all training data.

				@ With the objectives, NCG network learns to coarse-grain input signals and  extract latent parameters which are both predictive and predictable in the input signal and therefore achieves NTIC by building a higher-level representation of the underlying dynamics in the deep layers.

				@ Agents can process information and act at abstract levels
			\end{WritingMaterials}

			\begin{WritingMaterials}
				@ At the physical scale which human being live, the environmental dynamics is nearly deterministic following the laws of classical physics. This means that it is possible for agents living at this physical scale to build NTIC process internally.

				@ When the information in individual sensory channel is noisy and partial, coarse-graining becomes necessary for achieve NTIC.
			\end{WritingMaterials}

	\section{A neural coarse graining theory of consciousness}

\rlstart{5}

        In this section, we propose a new theoretical framework of consciousness \{\tnamefull\} \todo{We need a good name}. This framework proposes that NTIC is the fundamental properties for information processing to be conscious. Additionally, coarse-graining is necessary to achieve NTIC in various of different systems.

        We starts our argument from the first presumptive fact that every human conscious precept is highly informative. Our conscious experience always consists of high multidimensional information and usually involves information from multiple modalities. The notion of information referred to in this article is considered as resolved uncertainty. Being a certain conscious state rules out other enormous possible conscious experience in the state space of conscious experience. Therefore, every conscious percept resolves a huge amount of uncertainty and provides considerable information.

        This notion is in agreement with one of the axiom, \textit{information}, in Integrated Information Theory (IIT 3.0) which claims that \myQuote{...an experience of pure darkness is what it is by differing, in its particular way, from an immense number of other possible experiences...} \citep[p. 2]{oizumi2014phenomenology}.

        Based on this presumptive fact, we postulate that the amount of information possessed of a conscious percept should be equivalent to information involved in a particular event or entity in the physical reality. Strictly speaking, we recognise information is a common language between conscious experience and the physical reality. We further take a radical standpoint and postulate that consciousness is fundamentally associated with information, i.e. information correlates of consciousness (ICC), \cite{chalmers1996conscious, tononi2004information, gamez2011information, Gamez2016}) and discard the notion of neural correlates of consciousness(NCC).

        Next, we next consider the second presumptive fact that the information in consciousness is bound. Even though information involved in every conscious percept is extremely rich, it is still limited and we do not consciously feel everything in this universe. This leads to the boundary problems of consciousness \cite{goff2006experiences}. There should exist information boundaries for every conscious entity. Presuming consciousness is information-based phenomenon, we can identify the boundaries with measures from information theory. Particularly, in this case, boundaries can be defined by information closure. Therefore, information closure should be observed in conscious entities in the physical reality.

        \rewording{informational closure also suggests that there is no information flow from the lower to the higher level. Knowledge of the microscopic levels will not improve predictions of the future states of the macroscopic levels \citep{PFANTE.2014}}. 
        Information closure also implies that the system is ignorant of information outside of the system. Therefore, if a coarse-grained level achieves information closure, it suggests the NTIC process at the coarse-grained level is ignorant of information processing happening at microscopic levels and also higher coarse-grained levels. This virtually makes the informational closed macroscopic levels as a complete reality. 
        \todo{Due to my concern mentioned last week, I think I should also mention the closure is not only to the environment but also to the microscopic levels}

        Finally, our conscious experience always reflects some degree of information about environment and bodily states, i.e. non-trivial information. To account for the information-based considerations, we propose that NTIC is a fundamental informational property associated with consciousness.

        \begin{WritingMaterials}
        For example, considering two physical systems (Alice and Bob) and there is no interaction (or information passing) in between. Assuming that Alice is conscious, the conscious experience that Alice has should not involve any information about Bob.

        \todo{Considering putting this para}
        Similarly, we can apply this scenario to brain processing between two regions. We can consider a thought experiment. 
        Imagining that in the future, one poor subject attend this experiment. We remove the subject's visual cortex from other brain areas. However, we keep all the connection between the two parts of the brain intact by replacing dendrites and axons between the two parts with micro electronic cables. Because these cables are very long, we can move the visual cortex to the surface of Mars. Now the experimenters give visual cortex a input signal. If the signal travels with the speed of light, it still takes three seconds to reach the other part on the earth. We can ask: Between the experimenters send the input signal and the information reach the part on the earth, what visual conscious content does the subject experience in the three seconds? We presume that in this three seconds subject's conscious experience should not contain any information about the visual input. Otherwise, the subject may be able to use the information to perform subsequent actions. This violates physics. This may look like a trivial questions.

        However, in many systems, it is difficult to achieve NTIC at microscopic levels due to stochasticity. Through coarse-graining, NTIC processes become possible at macroscopic levels. Therefore, coarse-graining is necessary for many biological systems to implement NTIC processes, especially for the neural system (Fig. \ref{fig:LevelOfConsciousness}). In the following, we explained this framework and provide mathematical definitions and implications of ICC.  
        \end{WritingMaterials}

		\begin{WritingMaterials}

        @ As we mentioned in Chapter 3, to form non-trivial informational closure has a huge evolutionary advantage for the creatures interacting with the environment at our scale.

        @ The physical environment dynamic at the human scale are nearly deterministic.\needref{Do we need ref here?}

		@ To maximise fitness for individual human-being, neural system should try hard to infer and model the deterministic physical rules.

		@ This drives the neural system to create a non-trivial informational closure.

        @ Therefore, NTIC emerges from evolutionary processes is functionally plausible.

        @ Importantly, at the microscopic level, it is impossible to achieve NTIC as we mentioned in chapter 2.

		@ However, at a macroscopic scale, information processing can achieve non-trivial informational closure (Fig. \ref{fig:LevelOfConsciousness})

        @ Therefore, the NTIC correlating conscious experience must settled at coarse-grained macroscopic levels.

		@ Through coarse-graining, we can define a new set of variables.

        @ information is scale-dependent

		@ If the new set of variables are informational closure, then this creates a new \textit{reality} for all the variables inside.        
		@ \textit{Reality} here means that the all the future states of the system are driven by the current information (include variables and the relationships) within the boundary.

        @

        @ Relationship between coarse-graining, scale and interaction with environment

		@ \rewrite{
			This illustrates how coarse-graining allows the formulation of incomplete generalizations that are relatively invariant, although at the cost of predictive precision regarding fine-grained details.} \cite{price2007causation}

			@@ conscious perception are very stable and time invariant.
			@@ Conscious perception is informative but we loss all the precise information about the states at microscopic level.

        @ To summaries, in our framework, consciousness is 
			    @@ Intrinsic

			    @@ Informative

				@@ scale-dependent

        % our claim   
			@ We claim that the state of a coarse-grained scale which realises non-trivial informational closured correlates the state of consciousness.

			@ We further postulate that level of consciousness corresponds to informational closureness of processes.

			@ The contents of consciousness correspond to the states of the non-trivial informational closure.

		% Following
			@ In the following part, we....\todo{todo}

			@ This is the same as "if a tree falls in a forest" thought experiment.

			@ Therefore, to understand this system, you don't need more information from external environment.

			@ It also means everything in this system is self-defined.

			@ \critical{I need to somehow acknowledge \cite{pennartz2017consciousness}}
				@@ \rewrite{ In conclusion, for a well-behaved representational system, it does not matter whether a neural activation pattern represents an external world feature truthfully or not, as long as the system represents the feature consistently over time and in sensory space.}

				@@ pennartz levels are defined by functional elements call "functional ensembles". \cite{pennartz2017consciousness} \rewrite{This delineation is different from a scale-based distinction of levels, because different levels are distinguished here based on function , i.e., what each level can accomplish in terms of computation and representation, culminating in perception at the highest level.}

			@ \rewrite{
				Multilevel views on consciousness and cognition have been expressed before by many other theorists, such as Oppenheim and Putnam (1958), Attneave (1961), Hofstadter (1979, 1985), Churchland and Sejnowski (1992), Wimsatt (1994), and Lycan (1996).} \cite{pennartz2017consciousness}

				@@ Oppenheim , P. , \& Putnam , H. ( 1958 ). Unity of science as a working hypothesis . In H. Feigl , G. Maxwell , \& M. Scriven (Eds.), Concepts, theories, and the mind – body problem (pp. 3 – 36 ). Minneapolis : University of Minnesota Press .
				@@ Attneave , F. ( 1961 ). In defense of homunculi . In W. A. Rosenblith (Ed.), Sensory communication (pp. 777 – 782 ). Cambridge, MA : MIT Press .
				@@ Hofstadter , D. R. ( 1979 ). Godel, Escher, Bach, an eternal golden braid . New York : Basic Books .
				@@ Churchland , P. S. , \& Sejnowski , T. J. ( 1992 ). The computational brain . Cambridge, MA : MIT Press .
				@@ Wimsatt , W. C. ( 1994 ). The ontology of complex systems: levels of organization, perspectives, and causal thickets. Canadian Journal of Philosophy , 20 , 207 – 274 .
				@@ Lycan ,  W. G.  ( 1996 ).  Consciousness and experience .  Cambridge, MA :  MIT Press
			@ It's important that not the neural states but the coarse-grained state determine contents of consciousness.

		\end{WritingMaterials}

\rlend

\rlstart{3}
		\subsection{Measure of consciousness/information correlate of consciousness}	
		Based on our core assumption that NTIC is the core informational entity correlating conscious experience, we propose conscious levels and contents can be derived by computes the properties of a NTIC process. \newline

		\noindent
		We first hypothesise that, at given time $t$, levels of consciousness $C_{t}^{Level}$ corresponds to the degree of  $NTIC_{t}$ at a coarse-grained level.
			\begin{equation}\label{eq:cLevel}
				C_{t}^{Level} = NTIC_{t}
			\end{equation}
		\newline
		\noindent
		We second hypothesise that, the content of consciousness corresponds to the state of the NTIC process.
			\begin{equation}\label{eq:cContent}
				C_{t}^{Content} = Y_{t}
			\end{equation}

		We discuss the implications of the two hypotheses in the following. 	
	    \subsection{Level of Consciousness correlates degrees of NTIC of a process}

	    Our theory indicates that conscious levels are determined by two key elements based on the definition of NTIC (Equation \ref{eq:nticObjective}). First, to achieve high level of NTIC, one needs to maximise the channel capacity between the current internal state and the future internal state $I(Y_{t+1};Y_{t})$. This indicates that the richer self-predictive information the NTIC process contained the higher level of consciousness the agent has. Considering two hypothetical systems composed of binary nodes, one has only three nodes and the other one has 1 million notes. Even thought the first system can reach the maximal the channel capacity, the maximal level of NTIC is only 3 bits. Comparing the first system, even though the second system does not have full self-predictability about its future state, the level of NTIC of this system can still far higher than the first system. This outcome naturally explains why people intuitively associate levels of consciousness with complexity of systems.\todo{Need to end this part and may need a reference} \toWrite{I want to say something about animal consciousness here}.

	    Second, one can also minimise the conditional mutual information  $I(Y_{t+1};Y_{t}|E_{t})$. This suggests that conscious level positively correlates the level of information about the environment dynamic that the NTIC process encoded. Therefor, this implies that an agent who forms an NTIC process to lives and adapt to a more complex environment has a higher conscious level than an agent who interacts an environment with simpler dynamics. This also implies that agents who can explore, adapt model, and react to diverse environments should have higher level of consciousness.

	    Note that the non-monotonic relationship between levels of NTIC and scale of coarse-graining suggests that there exists a scale of coarse-graining with the maximal level of NTIC. The self-predictive information is the key to achieve high conscious level. If a system dynamics is highly scholastic and unpredictable, the level of consciousness should be low. As a result, information processed at neuronal scales which is heavily noisy and highly scholastic cannot form a high level of consciousness. Similarly, after coarse-graining, macro-variables lose predictive fine-grain information, the predictability become low and also the channel capacity between the current state and future state becomes very small, NTIC would be low as well. Consequently, human consciousness should be maximised at a certain coarse-grained level in the neural system.

	    Note that, the environment of a NTIC process in the nerual system includes not only the\todo{Werite this}

        Finally, which coarse-grained level can achieve high NTIC? 
        agent-scale operation
        At the physical scale which human being live in, the environmental dynamics is nearly deterministic following the laws of classical physics. It gives agents living at this physical scale great advantages if the agents can build NTIC process internally. Therefore, to coarse-grain microscopic states is necessary

		\begin{ants}

			@ \todo{modify this figure}

				\begin{figure}[H]				
				\includegraphics[width=\textwidth]{WritingMaterials/FoxitReader_2019-01-31_19-03-59.png}
				\label{fig:LevelOfConsciousness}
				\caption{Level of coarse-graining and level of consciousness. The degree of NTIC is not a monotonic function of coarse-graining levels, suggesting that high conscious level may exist at a certain coarse-grained level }
				\end{figure}
		\end{ants}

\rlend
\rlstart{3}
		\subsection{Conscious Contents Corresponding to Coarse-grained States}\needfig{maybe I need a figure here}
        As we mentioned above, human conscious contents always consist of rich,  high dimensional, and integrated information. The state space of the correspondent physical system must have the same capacity of containing the same amount of information. We claim that conscious contents correspond to the state of the NTIC process.

        This claim implies that the complexity of conscious contents correlates the amount of information encompassed in the NTIC process. Therefore, a crucial predict from our theory is that the larger state space of the NTIC process has the richer  conscious experience the process can have (e.g., a NTIC process involving a large amount of coarse-grained variables). Crucially, even experience of full darkness contains rich information because it rules out other enormous potential alternative states of conscious contents. Equivalently, in the physical system, to know the state of the NTIC process when there is no sensory input (darkness) also requires the same amount of information from the system.

        Follow the example in the last section\todo{Do I have this example?}, a small creature lives in a simple environment with very limited environment dynamics. It may forms a simple NTIC process. However, in this situation, the self-predictive information is very low and the state space of the NTIC process is small. As the result, the richness of the conscious experience this agent has will be very limited.

        Importantly, because the closure is at a coarse-grained scale one state of the informational closure can be mapped to several states at microscopic scale, our theory supports multiple realisation thesis \needref{multiple realisation} which suggests same conscious experiences can be mapped to different physical implementations.

		\begin{figure}[H]
			\includegraphicsTodo[width=0.8\textwidth]{WritingMaterials/LimitCycle/PhaseCycle.pdf}
			\label{fig:limitCycle}
			\caption{Example of coarse-graining by a limit cycle process}
		\end{figure}

		\begin{equation}\label{eq:LimitCycleExample}
            \begin{array}{l}{\dot{y_1}=y_1-y_2-y_1\left(y_1^{2}+y_2^{2} \right)+\epsilon_{y_1}} \\ {\dot{y_2}=y_1+y_2-y_2\left(y_1^{2}+y_2^{2}\right)+\epsilon_{y_2}}\end{array}
		\end{equation}

		The noise sources, $\epsilon_{y_1}$ and $\epsilon_{y_2}$, are i.i.d with a normal distribution with mean $\mu=0$ a and varance $\sigma^{2}=1$

		\begin{WritingMaterials}
            @ Our theory naturally explains the compositional nature of consciousness because the joint states of entities in the NTIC process determine the contents of consciousness.

		\end{WritingMaterials}

	    \subsection{Reconcile level and content of consciousness}
	    Recently, the segregation of conscious level and conscious contents raise a debate \citep{bayne2016there, Fazekas2016}. Our framework reconciles conscious level and conscious content. When the information encapsulate in the NTIC process is large and reaches a high NTIC, based on our definition, the system has high level of consciousness. Simultaneously, this provides a rich state space which is equivalent to encoding rich predictive environmental dynamic in the system. From this perspective, levels and contents of consciousness are just two different properties of NTIC processes. An important prediction from our theory is that in which the conscious level is determined by the size of the state space of the NTIC process rather the transient state of a system. For example, when we experience monotonous environment (a dark room), this does not degrade the conscious level.

	    Our framework also explains why in normal physiological states level and content are positively correlated \citep{laureys2005neural}\needfig{}. To achieve high NTIC, a system also needs to have high dimensionality and a large state space which guarantees rich and high dimensional information in conscious contents. Therefore, this framework well integrates the two key but debated concepts in consciousness research.

			\begin{WritingMaterials}
    			@ This implies that, based on the Equation \ref{eq:nticObjective}, the self-predictive information about the future states that the current state holds and the information about the environment encoded in the process determine the level of consciousness.

    			@ This also suggests that the richness of the environment being modelled by the	NTIC process has a direct contribution to the level of consciousness.

				@ To have high level non-trivial informational closure, the states of the coarse-grained scale need to

				@ First, maximise the mutual information between environment and the representation.
				This term implies that the agent need to maximise predictive power of environmental state. This also suggest that the environmental complexity is a crucial factor to the level of consciousness. The more rich and complex environment the agent try to predict the higher level of consciousness the agent has.

				@ Consciousness and complexity \cite{Tononi1998}

				@ Second, to minimise the mutual information between environment and the representation conditional on the past state of the representation. This term suggests that the representation is self-predicable and it mimics the environmental transition.

				@ Therefore, this theory predicts that level of consciousness determined by the environment that the agent adapts to. To form a high non-trivial informational closure, the agent will need to live in a complex environment and model the environmental transition precisely.

			\end{WritingMaterials}

\rlend

\rlstart{2}
		\subsection{sensory hierarchy and neural coarse-graining}\label{sec:SensoryHierarchy}

        It's important to note that the coarse-graining direction is not necessary to be align with \critical{Just saying anatomical is not enough. Need better expression} anatomical sensory hierarchy in the neural system. Our theory is different from consciousness theories which focus on the anatomical hierarchy, for example the intermediate Level Theory \citep[see also \ref{IntermediateLevelTheory}]{prinz2007intermediate, jackendoff1987consciousness}. Due to the pervasive noise in the microscopic levels in the neural system reliable information processes need to be built upon the coarse-grained levels. Nevertheless, to exercise causal power in actuators and environments, to read out information from coarse-grained levels is necessary. \needfig{Maybe need a figure discribing brain to hand}. Therefore, the neural system still implement readout decoders for the subsequent signal output. In figure \ref{fig:hierarchy}, the blue arrows indicate the readout mechanisms implemented in the neural system. We argue that previous data suggesting the neural correlates of consciousness between microscopic neural activities and conscious contents may be misled.

			\begin{figure}[H]
				\includegraphics[width=\textwidth]{WritingMaterials/SeperationOfCGandCortHierachy.pdf}
				\label{fig:hierarchy}
			\end{figure}

            \begin{WritingMaterials}
    			@ Of course, from evolutionary perspective, neural system should develop a better hardware to support neural coarse-graining

				@ For example, pooling layers in CNN is an implementation of coarse-graining function. It' is very plausible visual processing hierarchy in the neural system realises pooling layers.

				@ It is possible that the neural system represents higher-level information processing by low level physical subtract. For example, studies have found representation for summery statistics of signal and neural. population.\needref{neural representation for summery statistics}\\
				From this point of view, sensory hierarchy may extend along with levels of coarse-graining.
            \end{WritingMaterials}

\rlend

\rlstart{2}	
        \subsection{Dynamical Boundary}
        Our theory makes strong predicts that the physical boundary of a conscious system is dynamical. The boundary is determined by elements forming high NTIC. This implies that when the structure of interaction between elements changes the physical boundaries support consciousness should also change. If some coarse-grained variables encode environmental information, they may become necessary components to form high NTIC. In such case, these coarse-grained variables are "recruited" inside the boundary of conscious processes. Note that, due to synergetic information, even recruiting some new variables may largely increase the level of NTIC. 
        This may explain why consciousness is tightly associated with binding and integration of information in human perception and cognition. Another crucial implication is that the same neural substrates may not be always involved in conscious processing rather it depends on whether it creates high NTIC with other members in the neural system. \needfig{Maybe I need a figure h  ere as well}

\rlend

	\section{Conscious versus Unconscious Processing}

\rlstart{3}	
		\ideaBox{The goal of this part is to combine empirical study and phenomenology}
	    \ideaBox{I need to expend this section much more and more references}
	    In this section, we suggest that our theory has a strong exploratory and predictive power but with minimal assumptions.  
		Our theory indicates that to make information conscious two necessary conditions need to be satisfied with in any system.

		\begin{enumerate}
		    \item Information is encoded in NTIC process. 
		    \item The system is capable of constructing NTIC processes at coarse-grained levels. 
		\end{enumerate}

		Take the neural system as an example, our theory can well explain previous empirical findings in consciousness science and further make strong and more precise predictions for future studies. In the following, we discussed the implication of the two necessary conditions with respect to the empirical data in the literature of consciousness.

		\subsection{Unconscious Processing}
		As described above, if information processing fails to meet either one of the two necessary conditions, information remains unconscious. First, considering processes which fail to meet the first condition. That is, a information process is not NTIC. We can see many information processing in the neural network system fall in this category.

		\begin{equation}\label{eq:InformationFlow}
		\begin{aligned}
            P(A|S)
        \end{aligned}
		\end{equation}

		When the first condition is not satisfied,

		In this case, the future state of this process is partially or fully determined by environment states. We can see

		\begin{ants}
		    @ Conscious

		    @ Boundary 
    		    @@ binocular rivalry/CFS
    		    @@ Libet's experiment
    		    @@ Priming
    		    @@ Bistable perception
    		    @@ Perceptual overflow
    		    @@ Unconscious determinants of free decisions in the human brain
    		    @@ Threshold of unconscious to consciousness
    		    @@ Probabilistic information is always unconscious

		    @ Unconscious 
                @@ Reflection
        			@@@ Reflexive systems is not informational closured.
        			@@@ Base	d on our theory,
        			@@@ x -> s -> a
        			@@@@ the system state is determined by environmental state, then it is not conscious.
        			@@@ Therefore, in general, a simple policy network is not conscious.

    			@@ Blindsight

    			@ Passive neural activity

		\end{ants}

		\subsection{reflexive behaviours is unconscious (or environment-state dependent processes)}\label{sec:reflexive}
		\subsubsection{Reflection}
		\begin{ants}
			@ Reflexive systems is not informational closured.
			@ Base	d on our theory,
			@ $P(A|S)$ action policy is conditional on the sensory input data.
			@ x -> s -> a
			@@ the system state is determined by environmental state, then it is not conscious.
			@ Therefore, in general, a simple policy network is not conscious.
		\end{ants}

		\subsubsection{Blindsight}
		\begin{ants}
			@ This also blindsight.
			@ Blindsight patients and still make above chance judgement without conscious awareness of visual targets.
			@ The stimulus-reaction policy network still intact, but it cannot form informational closure and therefore, patients has no conscious awareness of visual  targets
			@ Patient B.F. reactions are stimulus driven.
		\end{ants}

		\subsubsection{procedure memory}

		\subsection{Conscious Processing}
		So far, previous consciousness research has identified a set of perceptual and cognitive functions which not exclusively but frequently associate with consciousness.

		\begin{ants}
            @ response inhibition 
            @ goal
            @ planning            
            @ conflict resolution
            @ error detection         
            @ task-switching
            @ working memory
            @ cognitive control 
            @ overriding automatic responses
            @ self-monitoring 
            @ global availability 
            @ integration             
            @ stabilisation
            @ information for off-line processing
            @ flexible routing of information
            @ integrates behaviour across time            
            @ tasks for long duration
            @ flexibility and the strategic use of that information for complex operations and decision-making 
            @ flexible and adjust our behavior to different contexts and goals
            @ complex visuomotor abilities
            @ conscious thought, reflection, reasoning, and temporally extended sense of self. 
            @ multiple alternative possibilities
            @ simulate alternative realities 
            @ imagination
            @ dreaming 
            @ anticipation
            @ intending
            @ replaying
            @ interpreting
            @ reflecting
            @ reasoning
            @ problem solving 
            @ deciding            
		\end{ants}

		To achieve high NTIC has evolutionary advantage. When a process achieves NTIC, the current state of the process contains the information about its future state (Eq. (5)). Therefore, the neural system can build forward models to predict the future state of the environment using the information encoded in the NTIC process. Cognitive functions recruiting forward models built upon it are conscious. (E.g., planning and imagination)

		It is important to note that we do suggest any functionalism of consciousness. Rather, we believe that information is fundamentally linked to consciousness. The reason why consciousness is accompanied with some specific cognitive function is because NTIC is a powerful property that brings creatures a lot of advantage in the evolution \cite{Seth2009Encyclopediaofconsciousness}.

	    \begin{WritingMaterials}
	        @ importantly, evidence suggests that those functions in some conditions do not require the involvement of consciousness. This evidences an important fact that consciousness is not necessay to these functions.

	        @@ Predictive information about the environment.

	        @@ Stability

	        @@ simulation environmental dynamics

	        @ Replaying past events

	        @ \rewrite{However, recent evidence also points out interesting dissociations between conscious and unconscious information processing when it comes to the duration, flexibility and the strategic use of that information for complex operations and decision-making} \cite{van2012role}

	    \end{WritingMaterials}

		\subsection{Unconscious Processing}
		When processes fail to satisfy either of the two conditions, they remain unconscious. First, when processes do not meet the first condition, i.e. the information processed not at the certain coarse-grained level, the information will not be included in conscious contents. For example, we are never conscious of neural spike activities at microscopic levels (e.g. single cell activities) because information passing among individual neurons are not at the certain coarse-grained level. \todo{Rewording}Libet's free will experiment can be also explained by our theory. The random neural fluctuation under Libet's free will experiment happens at the microscopic scale \citep{SchurgerE2904}.

		Second, when processes do not meet the second condition, i.e. processes which do not achieve high NTIC will remain unconscious. This can explain why many "policy-based" processes are not conscious.\todo{Need a better term/way here} Policy-based here features those processes taking sensory information as input and directly outputting actions. Therefore, the future states of policy-based processes largely depend on the environmental states and failed to achieve informational closure. Neural processes are included in this category, e.g. reflexive neural circuit, blindsight, procedure memory.

		To summarise, our theory can well explain the various findings with parsimonious assumptions.

	    \begin{ants}
	        @ \rewrite{the nonsemantic processing of primes is enhanced and priming effects are boosted when the experimental context allows the formation of automatic stimulus–response mappings.}\cite{VandenBussche2009}
	    \end{ants}

\rlend

	\section{Comparison with other theories}
		\ideaBox{Main points should be same/diff, our advantages, and predictions}
		In this section, we will discuss the relationship between our theory and other popular modern theories of consciousness.

\rlstart{2}
		\subsection{Theories about multilevel views on consciousness and cognition}
        Previously, multilevel views on consciousness and cognition have been proposed. We shortly describe two theories which is \todo{XXX and XXX} related to our current proposal.	% We discussed the differences between our theory and other theories about multilevel views.

            \subsubsection{level of Organisation \cite{wimsatt1994ontology}}
                As mentioned previously, the level of coarse-graining is different from the anatomical level.
                Pennartz focus more on multimodal representation as the most important factor (See the discussion in \cite{pennartz2015brain}). Our proposal is inline with Pennartz's Neurorepresentational  theory (Neurorepresentationalism) \cite{pennartz2018consciousness,pennartz2015brain}. However, it’s crucial to note that our theory claims only the level of coarse-graining achieving NTIC matters to consciousness rather than the anatomical level of sensory hierarchy. 
                \ideaBox{Should I also deal with Marr's level of abstraction?}

			\subsubsection{Intermediate Level Theory} \label{IntermediateLevelTheory}
                One important theory linking consciousness to multilevel views is the Intermediate Level Theory (ILT). ILT proposes that conscious experience only correlates specific levels of representations in the sensory processing the hierarchy. This theory claims that consciousness only associates with the representation at intermediate levels rather than the ones at lower-level or higher-level discribed as 2.5D. However, ILT focuses on the levels in terms of anatomical direction. As mentioned previously, a critical difference between ILT and our theory is that our theory doesn't assume the direction of coarse-graining should align with the direction of anatomical processing levels along cortical hierarchies (see fig \ref{fig:hierarchy}).

                Different from ILT which suggests that the neural substrates responsible for the 2.5D computation is conscious, we predict that if information that is carried by v1 neurons are necessary to complete informational closure, the states of V1 neurons should also co-vary with conscious contents.

			\subsubsection{Pennartz's neurorepresentational theory (Neurorepresentationalism)}
			    Our theory shares some similar concepts with Pennartz's Neurorepresentationalism. However, Neurorepresentationalism focuses on multimodal representation \cite{pennartz2018consciousness,pennartz2015brain}. Another focus of neurorepresentationalism is on "making sense" between representations\todo{Need something here}. Different from neurorepresentationalism, conscious contents in our framework are grounded by the informational relations between variables in NTIC because NTIC provides a closed relationship between states in a system.

			    Similar to Neurorepresentationalism, our framwork is more close to Marr ’ s original distinction between the levels of (neural) implementation, algorithms, and computational theory [122], but focuses on how conscious representations correspond to computational operations at levels with lower complexity and representational capacity.\cite{pennartz2018consciousness,pennartz2015brain}

			    Neurorepresentationalism is also a functionalist perspective. However, e don't assume any functional properties as the criteria of consciousness. Instead, we propose information as a more fundamental principle correlates consciousness.

		        \begin{WritingMaterials}
				%% Back up materials

				@ Prinz suggested that \rewrite{as. Cells in V1 are not promising candidates, because they do not reliably respond in ways that are consistent with features that we experience consciously. } \cite{prinz2007inter    mediate}

				@ \rewrite{
					The intermediate level theory originally proposed by Ray Jackendoff and further defended and specified by Jesse Prinz proposes that within the hierarchy of representations that are used to describe the cognitive system, conscious experience occurs only for specific levels of representation. The theory is rooted in Jackendoff ’s analysis of different cognitive systems such as vision, language, and music and the subsequent observation that consciousness does not arise anywhere within these systems. According to Jackendoff, consciousness is not associated with low-level, nor with high-level representations, but rather with those implying intermediate levels of processing. For instance, in the domain of object recognition, it is assumed that the visual system comprises a low level with local computations of visual features, an intermediate level reflecting binding and object recognition, and a higher level computing viewpoint invariance and representing abstract categories. According to Jackendoff and Prinz, conscious experience is not comprised of a disunified picture of visual features, nor is it represented by viewinvariant categories. Rather it is composed of bound and specific instances of objects that are assumed to be computed at the intermediate level of representation. In an analogous manner, speech perception can be decomposed into three levels: an acoustic representation of speech sounds at the lower level, a high level involving abstract lexical and syntactic categories, and in between a word recognition level relying on phonological representations. This theory explains why the conscious experience associated with speech perception mostly involves phonological representations, rather than other levels of representations. In Jackendoff and Prinz’ theory,the privileged role of the intermediate level of processing is based on the need for real-time computational efficiency. Indeed, this level of representation is assumed to be the most relevant one regarding ecological and functional needs. Another important aspect of this theory concerns the central role of attention during conscious experience. Here, attention is defined as a selection process that acts as a gate to working memory mechanisms. It performs the function of selecting the relevant information that is amplified afterward and then becomes conscious. Indeed, Prinz acknowledges that activation of an intermediatelevel representation on its own cannot be a sufficient condition for consciousness, given that those representations can be activated during subliminal perception. However, this theory makes the crucial postulate that the amplification of intermediatelevel representations by attention is a necessary and sufficient condition for consciousness. In sum, for each domain of processing, the content of consciousness at a particular moment is supported by a representational structure of intermediate level for that domain, which is selected to enter short-term memory, and enriched by attentional processing.} \cite{banks2009encyclopedia}

				@ \rewrite{
					In 1987, Ray Jackendoff published Consciousness and the Computational Mind. In it, he posed an important Where question: Where, in the fl ow of information, does consciousness arise? Most cognitive scientists agree that the mind is, in some sense, a computer. It is a device that processes information by transforming representations in accordance with rules. Computational devices decompose into various interconnected subsystems, each of which performs some aspect of a complex task. Given such a decompositional analysis, we can ask: in which subsystems does consciousness arise? If we depict the mind as a vast fl ow chart, and highlight the boxes whose rules and representations are conscious, which boxes should we mark? Jackendoff ’s answer is simple and elegant. He noticed that many of our mental capacities, including our senses and our language systems, are organized hierarchically. In each of these hierarchies, it makes sense to talk about low- , intermediate- , and high- level processing systems. We break down tasks into stages. Appealing to prevailing models of these stages, Jackendoff observed that the intermediate level seems to be privileged with respect to consciousness. Consciousness seems to arise in intermediate- level processing systems and not elsewhere.} \cite{prinz2007intermediate}

				@ \cite{jackendoff1987consciousness}
				@ \cite{prinz2007intermediate}
				@ 2.5D

				@ about why it is this level
				@@ \rewrite{
					Under the computational interpretation, the “why” question means: In what sense are intermediate level representations computationally important or distinctive? Th is is a tractable question, and it may lead to insights into the function of consciousness. Representations at the intermediate level are ideally suited for real- time deliberative behavioral responses. Low- level representations fail to bind features into coherent wholes. If we are going to interact with our environment, the low level is not a good guide. Th e high level is a good deal better for action, but also suboptimal. Th e high level tells us the category of the stimuli we perceive, but from an allocentric point of view. It abstracts away from stimulus features that are crucial for action. If we encounter a predator, the high- level visual representation does not tell us if it is facing toward us or away from us. Without that knowledge, we cannot decide what course of action to take. So, I propose that the intermediate level plays a distinctive role in information processing. It delivers representations that are coherent but viewpoint specifi c. Th ese representations are useful for determining what to do here and now.arg1} \cite{prinz2007intermediate}
				@@ \rewrite{
					I conclude that the intermediate level plays a distinctive and important computational role. Some researchers find this puzzling. In wondering why the intermediate level is privileged, they note the arbitrariness of the fact that perceptual hierarchies have three levels. Could they not have two? Or a hundred? Do the 50 or so areas that contribute to visual processing really divide neatly into three levels? I think these puzzles depend on a particular understanding of what the word “intermediate” amounts to. One might get caught up in the fact that the intermediate level is the second stage in a sequence. Call this the “serial understanding of the intermediate level.” Alternatively, one might think of the intermediate level semantically. On this reading, the intermediate level is one that is not abstract and categorical, but not piecemeal or disunifi ed. Th ese notions are all in need of some refi nement, but, as a fi rst approximation, the idea is that intermediate- level representations are neither too specifi c nor too general.}\cite{prinz2007intermediate}

				%% Our theory
				@ However, as we mentioned in Section \ref{sec:SensoryHierarchy}, \rewrite{The notion of ‘ levels ’ deployed here is functional and very different from that of successive anatomical processing stages along cortical hierarchies [75] or from anatomic scales in the brain. The multi-level concept in [2] is more akin to Marr ’ s original distinction between the levels of (neural) implementation, algorithms, and computational theory [122], but focuses on how conscious representations correspond to computational operations at levels with lower complexity and representational capacity.}\cite{pennartz2018consciousness,pennartz2015brain}
			\end{WritingMaterials}

\rlend

\rlstart{2}	
		\subsection{First-order theories}
            The first-order theories suggest that consciousness is determined by early sensory information or neural activities\needref{First-order theories}. The first-orde view maintains that conscious awareness is determined by early sensory activity alone, independently of higher-order representations. \rewrite{According to first-order views, phenomenal consciousness consists in analog or fine-grained contents that are available to the first-order processes that guide thought and action. So a phenomenally-conscious percept of red, for example, consists in a state with the analog content red which is tokened in such a way as to feed into thoughts about red, or into actions that are in one way or another guided by redness.}

            We predict that, if early sensory information or neural activities after coarse-graining take parts in the NTIC process, early sensory information or neural activities also contribute consciousness. However, due to coarse-graining, changes of early sensory information or neural activities do not necessarily accompany with changes of conscious contents. \todo{Need more here, espectially more counterintuitive predictions}

			\begin{WritingMaterials}
				@ \rewrite{
					The ﬁrst-order view maintains that conscious awareness is determined by early sensory activity alone, independently of higher-order representations. Thus the crucial difference between the ﬁrst-order and higher-order views is that the latter but not the former predict that conscious awareness is determined at least in part by prefrontal and parietal activity. Therefore, in the group of ﬁrst-order theorists we include here not only those commonly labeled as such in the philosophical literature [11] but also theorists, such as Ned Block [12,13], who hold that the phenomenal qualities of awareness depend on the biological substrate rather than merely the content of the ﬁrst-order representations, as well as scientists who hold that visual awareness depends on activity in content-speciﬁc regions of the extrastriate cortex [24,25] or on feedback from these regions to the primary visual cortex [26]. Most ﬁrst-order theories explain the difference between awareness and unawareness by positing that the latter is associated with weak information [29] or with representations in alternative (e.g. subcortical) sensory pathways. Thus this view suggests that conscious and unconscious processing will have different functional consequences. Whereas some ﬁrst-order theorists hold that some higher cognitive functions can be performed without conscious awareness [30–32], most ﬁrst-order theorists take a difference in perceptual task performance (e.g. ‘hits’ vs ‘misses’ in a detection task) as evidence for a difference in conscious awareness [12,13,25,26,33]. In other words, they typically associate task performance with awareness..} \cite{lau2011empirical}

				@ Among those are first-order theories, on which a mental state is conscious if being in that state results in one's being conscious of something;

				@  According to first-order views, phenomenal consciousness consists in analog or fine-grained contents that are available to the first-order processes that guide thought and action. So a phenomenally-conscious percept of red, for example, consists in a state with the analog content red which is tokened in such a way as to feed into thoughts about red, or into actions that are in one way or another guided by redness.

			\end{WritingMaterials}

\rlend

\rlstart{1}
		\subsection{Higher Order Thought theory of consciousness}
		    In contrast to first-order theories, higher-order thought theories suggest that consciousness depends on higher-order representations representing agents as being in particular internal states. Meta-cognition is also associated with many conscious cognitive function. However, we propose a new perspective and indicate that HOT may be a misunderstanding \critical{Very bad writing. I need to rewrite this part}. This may be the result of neural coarse-graining. Because contents in informational closure look like watching fine-grained information, people may have an wrong impression about it. Coarse-grained information can be summary statistics which may be misunderstood as higher-order representation. It is true that the neural system does create  meta-representation to represent xxx\needref{Maybe come studies about confidence represenatation}. The higher-order representation may resemble coarse-grained variables. This may cause misidentify the entity which correlates conscious experience.

		    Moreover, the predictive information in NTIC is critical for other systems to build forward models for a wild range of tasks. Therefore, most of the high level cognition can utilise the state of informational closure. For example, mental planning needs a precise forward model to infer the environmental dynamics.

			\begin{WritingMaterials}
		    @ In contrast to first-order theories, higher-order thought theories suggest that consciousness depends on higher-order representations representing agents as being in particular internal states.

		    @ Coarse-grained information can be summary statistics which may be misunderstood as higher-order representation.

		    @ It is true that the neural system does create  meta-representation to represent xxx.\needref{Maybe come studies about confidence represenatation}

		    @ The higher-order representation may resemble coarse-grained variables.

		    @ This may cause misidentify the entity which correlates conscious experience.

		    @ ----------------------------------------------------------------------------

			@ Information closure directly is critical for other systems to construct forward models.

			@ Therefore, most of the high level cognition can utilise the state of informational closure.

			@ For example, mental planning needs a precise forward model to infer the environmental dynamics.

			@ \idea{This is way HOT always involve consciousness }

			@ \cite{rosenthal2005consciousness}

            @ ============================================================================
			@ \rewrite{
				Higher-order theories of consciousness argue that conscious awareness crucially depends on higher-order mental representations that represent oneself as being in particular mental states.} \cite{lau2011empirical}

			@ \rewrite{
				According to this view, humans not only have first-order non-conceptual and/or analog perceptions of states of their environments and bodies, they also have second-order non-conceptual and/or analog perceptions of their first-order states of perception. And the most popular version of higher-order perception theory holds, in addition, that humans (and perhaps other animals) not only have sense-organs that scan the environment/body to produce fine-grained representations that can then serve to ground thoughts and action-planning, but they also have inner senses, charged with scanning the outputs of the first-order senses (i.e. perceptual experiences) to produce equally fine-grained, but higher-order, representations of those outputs (i.e. to produce higher-order experiences). A version of this view was first proposed by the British Empiricist philosopher John Locke (1690). In our own time it has been defended especially by Armstrong (1968, 1984) and by Lycan (1996).} \url{https://plato.stanford.edu/entries/consciousness-higher/#SelRepHigOrdThe}

			@ \rewrite{
				neutral about whether conscious awareness adds signiﬁcant utility or immediate impact on behavior and task performance [1,27]. This is because the view assumes that task performance in most perceptual and cognitive tasks depends mainly on ﬁrst-order rather than higher-order representations. Because conscious awareness can differ even if all ﬁrst-order representations remain completely unchanged, such awareness itself might serve little function [1,27].}\cite{lau2011empirical}
				\ideaCallout{
					My theory would have similar prediction. Because conscious contents are coarse-grained results from low-level information. It is possible that more than two low-level neural states all coarse-grained to a high-level state.  }

			@ \rewrite{
					Metacognition: cognition that is about another cognitive process as opposed to about objects in the world. In this article we use it mainly to refer to sensory metacognition: a cognitive process that concerns the quality or efﬁcacy of a perceptual process. The capacity of sensory metacognition is sometimes empirically assessed by the correspondence between subjective report and task performance: how closely are they associated with each other on a trial-by-trial basis}\cite{lau2011empirical}

			\end{WritingMaterials}

\rlend

\rlstart{2}
		\subsection{Global workspace theory}
		Global workspace theory (GWT)\cite{baars1988cognitive, baars1997theatre, baars2002conscious} or Global Neuronal Workspace theory (GNWT)\cite{dehaene1998neuronal, dehaene2001towards, dehaene2011experimental} states that the neural system consists of many separate specialised modules and a central global workspace (GW) which integrates and passes information amount the modules. Only the information that is accessed by the global workspace can be conscious aware of. The modules competes with each other to gain the access to the global workspace and the information from the winner can trigger an all-or-none "ignition" in the global workspace and be globally broadcasted to other modules. Conscious contents then associates information which gains access to the internal global workspace \cite{Dehaene2017}. Our framework can well accommodate and interpret these claims by GWT.

		Stability: Conscious perception necessitates representational stability. Our theory rests upon self-predictability which formally encompasses stability.

		Broadcasting: When new sensory information from a modality is involved in NTIC, the information can be preserved in the following dynamic of NTIC. The neural system can extract the information for specific task goals. This is equivalent to the function of broadcasting.

		Non-linear ignition: Because mapping microscopic to macroscopic states is many-to-one, it commonly shows a nonlinear relationship between microstates and macrostates. In our theory, new information presents in conscious perception corresponds to a transition in the state space of the NTIC process. This can cause a significant change of the brain states and resembles non-linear ignition of brain activities. Conscious access as an accumulation of evidence leading to an all-or-none ignition What, if anything, remains unique to conscious processing? Although many cognitive operations can be partially launched non-consciously, these operations rarely if ever run to completion in the absence of consciousness. A subliminal stimulus may induce above-chance performance, behavioural priming, and a small amount of brain activity in narrowly deﬁned brain networks, but these measures often increase dramatically as soon as the subject reports seeing the stimulus, especially in high-level areas [46 60,61  ]. Accumulation of evidence has been demonstrated with non-conscious stimuli [59], but only conscious stimuli cross the threshold beyond which an overt strategy can be ﬂexibly deployed. \todo{Cite similar opinion from other theories}

		A difference between our theory and GWT is that our theory does not suggest a neuronal core anatomical area for consciousness. \todo{Link to Section 4}. Coarse-grained information in NTIC is more crucial for consciousness rather than neural substrates supporting the global workspace.

		\begin{WritingMaterials}
			%% Introduction
			@ Global workspace theory (GWT)\cite{baars1988cognitive, baars1997theatre, baars2002conscious} or Global Neuronal Workspace theory (GNWT)\cite{dehaene1998neuronal, dehaene2001towards, dehaene2011experimental} states that the neural system consists of many separate specialised modules and a central global workspace (GW) which integrates and passes information amount the modules. Only the information that is accessed by the global workspace can be conscious aware of. The modules competes with each other to gain the access to the global workspace and the information from the winner can trigger an all-or-none "ignition" in the global workspace and be globally broadcasted to other modules. Conscious contents then associates information which gains access to the internal global workspace \cite{Dehaene2017}.

			@ Submodule access and NTIC

			%% Our theory

			@ Our theory can well accommodate several claims by GWT.

			@ Conscious perception necessitates representational stability: Our theory rests upon self-predictability which formally encompasses stability.

			@ Broadcasting: When new sensory information from a modality is involved in NTIC, the information can be preserved in the following dynamic of NTIC. The neural system can extract the information for specific task goals. This is equivalent to the function of broadcasting.

			@ Non-linear ignition: Because mapping microscopic to macroscopic states is many-to-one, it commonly shows a nonlinear relationship between microstates and macrostates. In our theory, new information presents in conscious perception corresponds to a transition in the state space of the NTIC process. This can cause a significant change of the brain states and resembles non-linear ignition of brain activities.

			@ our theory re-explains the critical xxx from GWT.

			@ The critical difference is that our theory does not suggest a neuronal core anatomical area for consciousness. We suggest coarse-grained information form NTIC is crucial for consciousness.

			@ In sum, our theory is compatible with previous physiological evidence supporting GWT.

		\end{WritingMaterials}

% 			\subsubsection{Global availability and Broadcasting}
% 			\subsubsection{Stability}
				\begin{WritingMaterials}
					@ the presence of contexts as stable coalitions shaping access to the workspace.

					@ e ‘all-or-none’ behavior, whereby the incoming evidence either quickly dies out (corresponding to subliminal processing) or is accumulated and ampliﬁed non-linearly into a full-blown state of high-level activity. This global ‘ignition’ has been proposed as a marker of conscious perception [70]. Indeed, empirically, when stimulus strength is varied, the early stages of non-conscious processing typically show a linear variation in activation, whereas conscious access is often characterized by a late non-linear ampliﬁcation of activation which invades a distributed set of parietal, prefrontal and cingulate areas
				\end{WritingMaterials}

% 			\subsubsection{Broadcasting}

			\subsubsection{Ignition}
				\begin{WritingMaterials}
					@ Conscious access as an accumulation of evidence leading to an all-or-none ignition What, if anything, remains unique to conscious processing? Although many cognitive operations can be partially launched non-consciously, these operations rarely if ever run to completion in the absence of consciousness. A subliminal stimulus may induce above-chance performance, behavioural priming, and a small amount of brain activity in narrowly deﬁned brain networks, but these measures often increase dramatically as soon as the subject reports seeing the stimulus, especially in high-level areas [46 60,61  ]. Accumulation of evidence has been demonstrated with non-conscious stimuli [59], but only conscious stimuli cross the threshold beyond which an overt strategy can be ﬂexibly deployed. 
				\end{WritingMaterials}

			\begin{WritingMaterials}
				@ GWT is one of the current popular consciousness theories.

				@ \rewrite{AI system and corresponds to our first functional definition of consciousness: global availability} \cite{Dehaene2017}

				@ C1: Global availability of relevant information The need for integration and coordination \cite{Dehaene2017}

				@ Evidence for integration and broadcasting

				@ Stability as a feature of consciousness \rewrite{“ meta-stability ” seems to be necessary for the nervous system to integrate information from a variety of modules and then broadcast it back to them, achieving flexible cross-module routing.}

				@ \rewrite{integration of computational resources in a large-scale coordination and for the exchange of information among processors}

				@ \rewrite{Grounded on the distinction between conscious and unconscious processes, Bernard Baars’ global workspace theory is one of the most influential cognitive theories of consciousness. This theory relies on the metaphor of a theater. In this theater, unconscious specialized processors (equivalent to modules) are assumed to be the actors and the audience. While the audience represents the set of passive processors, actors represents active processors playing on the stage of the theater (i.e., the workspace). These actors are engaged in a competition for being seen by the audience: by broadcasting their information they actually compete for more broadcasting. Active processors with the highest coherent activity can form local coalitions that strengthen them in this competition process. The strongest coalition in this competition dominates the workspace, in a winner-take-all fashion, and corresponds to the content of consciousness. The workspace is equated by Baars to working-memory, in which only the most active content becomes conscious. Additionally, the dominant coalition benefits from global broadcasting, which allows it to recruit new processors from the audience in order to form a global coalition. Here, consciousness allows for the integration of computational resources in a large-scale coordination and for the exchange of information among processors that would otherwise remain separated. In this theory, each processor can operate in the conscious mode if it benefits from global broadcasting through the workspace, or it can operate in the unconscious mode when disconnected from the workspace. An important feature of the global workspace theory is the presence of contexts as stable coalitions shaping access to the workspace. Contexts are constituted of unconscious processors reflecting, in a hierarchical manner, our expectations, our beliefs, our goals, and ultimately our self. In particular, attention is implemented as a goal context in this theory. It is described as a mechanism that controls access to the workspace, acting as a filter and biasing the competition process toward a particular set of actors. At any given moment, the dominant coalition is under the spotlight of attention, and its informational content becomes the content of conscious experience. A crucial aspect of Baars’ theory is that it avoids the problem of the homunculus by reducing it to an audience of multiple unconscious processors. Here, there is no need for a hypothetical single conscious observer in the system, and thus there is no issue of infinite regression with a homunculus inside another homunculus. Instead, consciousness is considered to reflect the global broadcasting of information to an audience of unconscious processors. As the audience is unconscious, unsupervised, and receptive rather than attending to the information, it does not constitute an internal homunculus.}

			\end{WritingMaterials}
\rlend

		\subsection{Sensorimotor contingency}
		Sensorimotor contingency (SMC) theory of consciousness is proposed to account of conscious perception. It suggests that different types of SMCs give rise to different characteristics of conscious perception \cite{o2001sensorimotor}. The theory radically rejects the view that conscious contents is associated with information encoded in internal representations in the neural system. Rather, the quality of conscious perception depends on agents' mastery of SMCs. It emphasises the interactions between a system (the neural system) and its environment are crucial to form conscious perception

			\begin{ants}
				%% SMC

				@ Sensorimotor contingency (SMC) theory of consciousness is proposed to account of conscious perception. It suggests that different types of SMCs give rise to different characteristics of conscious perception \cite{o2001sensorimotor}.

				@ The theory radically rejects the view that conscious contents is associated with information encoded in internal representations in the neural system.

				@ Rather, the quality of conscious perception depends on agents' mastery of SMCs.

				@ It emphasizes the importance of the interactions between a system (the neural system) and its.

				@ Counter-intuitively, because consciousness inhabits in interactions between agents and environments, this theory suggests that consciousness is not driven by brain activities. Instead, consciousness should be shaped by the way of interaction, i.e. SMCs, between agents and environments.

				%% Our theory

				@ Similar to the SMC theory, our theory predicts that the interaction between the neural system and the environment shapes the quality of conscious perception.

				@ This is because to achieve NTIC the neural system should maximise the conditional mutual information between the future state of the NTIC process and the environment given the agent's current action (see equation XXX \critical{I NEED A EQUATION!}).

				@ This suggests the to maximise NTIC the NTIC process needs to involve the information about the environmental transition and dynamic after agent preforms an action.

				@ Therefore, as a consequence of maximising NTIC, the representation forming NTIC implicitly encodes information about SMCs.

				@ In the long-term, once NTIC neural dynamic interoperates the environmental state transition given actions via maximising NTIC, the state space of XXX then is shaped by the new learned SMC

				@ Accordingly, the way how the agent interacts with the environment influences the structure of the NTIC representation.

				@ \todo{Need to involve some sentence from  }

				@ \idea{Do I need a figure here?}

				@ However, in contrast to the SMC theory, our theory suggests the state of NTIC process correlate conscious contents. Therefore, if the NTIC process is formed inside the neural system, we should have correspondent conscious contents in our conscious experience without interacting with the environment.

				@ \idea{Not sure here} This can easily explain that the conscious experience of dream is just induced by self-evolved state changes of the NTIC process.

				@ Further more the SMC and our theories make complete different prediction about the relationship between SMC and consciousness.

				@ Contrary to the SMC theory which suggests that consciousness resides on SMCs, our theory predicts that pure S-R contingency between the neural system and the environment can not achieve informational closure within the neural system and therefore is not conscious (please see section \ref{sec:reflexive})

			\end{ants}

			\begin{WritingMaterials} % materials

				%% Intro about this theory
				@ O’Regan and Noë

				@ \rewrite{According to Noë, perceptual presence is explained by a “ sensorimotor theory ” on which perception depends on a practical mastery of sensorimotor dependencies or “ sensorimotor contingencies ” (SMCs) (O ’ Regan \& Noë, 2001). The theory inherits from Gibsonian notions of “ affordances ” (Gibson, 1979) and from enactive cognitive science (Thompson \& Varela, 2001) which stress the importance of brain-body-world interactions in cognitive processes. On sensorimotor theory, the perception of a tomato as a (perceptually present, real, subjectively veridical) tomato is given by practical mastery of the SMCs governing how the sensory responses elicited by the tomato will behave in a variety of situations. A strong point of this theory is that it suggests why there are differences in qualitative character between modalities, the reason being that different modalities instantiate different SMCs (O ’ Regan \& Noë, 2001). }

				@ In their seminal article O’Regan and Noe¨ (2001) introduce sensorimotor contingencies (SMCs) as the basis of a sensorimotor account of conscious perception.

				@ In short, different types of SMCs give rise to different qualities of sensory experience

				@  Second, vision, audition, touch, etc., correspond to domains of knowledge of the respective SMCs that are exercised by an agent as part of its habitual behavior.This ‘‘mastery of SMCs’’ is what lets an agent perceive its environment and adapt its behavior accordingly

				@ And third, sensory awareness arises when SMCs are integrated with planning, reasoning, and generation of behavior

				@ The theory is a radical departure from the classical view that the brain constructs an internal representation of the outside world on which higher cognitive processes such as memorizing, reasoning, and planning operat

				@ perception depends on a practical mastery of sensorimotor dependencies or “sensorimotor contingencies” (SMCs)

				@ s the importance of brain-body-world interactions in cognitive processes. On sensorimotor theory, the perception of a tomato as a (perceptually present, real, subjectively veridical) tomato is given by practical mastery of the SMCs governing how the sensory responses elicited by the tomato will behave in a variety of situations.

				@ ways of acting or as something we do, rather than an internal phenomenal experience or an internal representation of the world (O’Regan \& Noë, 2001)

				@ \rewrite{I advance this truly astonishing hypothesis: To understand consciousness in humans and animals, we must look not inward, into the recesses of our insides; rather, we need to look to the ways in which each of us, as a whole animal, carries on the processes of living in and with and in response to the world around us . . . You are not your brain . . . Meaningful thought arises only for the whole animal dynamically engaged with its environment . . . And indeed the same is true for the quality of our conscious episodes . . . The taste of licorice is not something that happens in our brains.} (Noë, 2009, pp. 7–8)

				@ Because consciousness resides in our behavioural interactions with the world rather than in our brain, the theory postulates that consciousness does not derive from brain activity at all. Consequently, there is no need to explain how brain activity causes or constitutes consciousness, because it does not.

				@ O ’ Regan, J.K. and Noë, A. (2001) A sensorimotor account of vision and visual consciousness. Behav. Brain Sci. 24, 939 – 973

				@ SMC theory argues that consciousness arises from the execution of SMCs, resulting in brain – environmental interactions.

				@ The second variant of SMC theory postulates that ‘ it is not movement as such, but the consequences of potential movement that play a role ’ (in perceptual experience) ([5], p. 1015; see also [9,10,19,20]). This ‘ non-acute ’ or dispositional variant marks a signi ﬁ cant shift in position because it de-emphasizes actual movement. \cite{pennartz2017consciousness}

				@ It stipulates that for us to be conscious of something in the environment (or of our way of interacting with the environment)

			\end{WritingMaterials}

		\subsection{Predictive Processing}
			\begin{ants}
				%% Introduce PP
				@ The predictive processing is a powerful framework (PP) which integrates several influential ideas in the history of neuroscience including "perception as unconscious inference" from Helmholtz \citet{helmholtz1866concerning}, "analysis by synthesis", “predictive coding”, "Bayesian brain hypothesis"

				@ is a powerful framework

				@ a recent emerged theoretical framework of perception and brain function, which suggests that the brain continuously generates and updates predictions about incoming sensory signals, represents a general principle of neural functioning.

				@ According to predictive processing (PP) account of perception, the neural system constantly performs unconscious statistical inference about hidden causes in the external environment. The perceptual contents are the "best guess" about the environment 	\cite{clark_2013}			\cite{Hohwy2013}

				@ Bperceptual content is the result of probabilistic inference on the hidden causes of sensory signals.

				@ Because it is well integrated with Bayesian brain hypothesis, the PP framework has been used to interpret conscious perception in many perceptual domain. \cite{Hohwy2013} \cite{SethPP2014}

				%% The gaps between pp and consciousness
				@ However, to link PP to consciousness, there are still two major gaps.

					@@ First, previous studies have demonstrated many brain processes following the principle of Bayesian inference and Bayesian integration. But not all these processes are conscious. This indicates that PP is not a sufficient mechanism for conscious perception. Some other factors may be involved to determine which PPs can be conscious or not.

					@@ Second, it has been emphasized that only the results of the inference or prediction can be consciously accessed. The process of inference in completely unconscious. So WHY?

				@ Even though PP has been acquiring attention in different discipline in neuroscience, So far, to our knowledge, no detailed explanation has been given to account for the two questions.

				%% Our theory

				% 2018/06/15 15:10
				@ We first hypothesize that predictive processing stays unconscious is because it is not able to achieve NTIC.

					@@ \idea{Example from PID controller?}

				@ Second, according to our theory, it is obvious that the computation of predictive processing is unconscious and only the result is conscious. Because the computational details is not at the coarse-grained level which achieves NTIC.

					@@ So far, many neuronal models and coding schema have been proposed to explain how to implement Bayesian inference and prediction at the neuronal level.

					@@ However?

				@ We hypothesize that the distinction between conscious and unconscious predictive mechanisms is whether they build up on the information from the NTIC process.

			\end{ants}

			\begin{WritingMaterials}

				%% About the unconscious Bayesian processing
				@ \cite{lamme2015predictive}
					@@ To my knowledge, this is the first time this has been so explicitly laid out—writers on predictive coding thus far have always stayed a little vague on where exactly consciousness sits in the Bayesian framework.

					@@ Yet the two points seem contradictory. In the Bayesian predictive coding framework, consciousness is the result of the unconscious inferential processes.

					@@ However, these authors have so far been very reticent about how exactly consciousness ﬁts into the PC framework. For now, there is an emerging idea that understands consciousness as the ﬁnal result of unconsciousness processing. According to Hohwy (2013), perceptual consciousness ﬁts in the PC theory as the ‘upshot’ or ‘conclusion’ of unconscious perceptual inferences. Melloni (2014) also expects that inferential processes are conducted behind the curtain of consciousness and what we experience are the ‘outcomes’ or ‘results’ of an unconsciou inferential process. Lamme (2015) agrees with the idea that consciousness is based on the relation or more precisely conjunction of current inputs and priors, which together produce posterior beliefs. Karl Friston agrees to a certain extent with this interpretation of consciousness. According to Hobson and Friston (2016), consciousness is not a phenomenon but a process, a process of optimizing beliefs through inference (consciousness, dreams, and inference; the Cartesian theater revisited; a response to our theater critics).

				@ Link PP and c
					@@ \cite{hobson2016response}
					@@ \cite{Melloni2015}

				%% ----------------------------------------------------------------------------
				@ \cite{SethPP2014}

				@ When uncertainty is high, we should expect an increase in the ability of ever higher-level prior beliefs to determine conscious experience. I

				@ determine conscious experience.

				@ PP combines and builds upon previous ideas about the role of “unconscious inference” in perception (Helmholtz, 1925; Barlow, 1961; Gregory, 1970), the process of “analysis by synthesis” in psychology (Neisser, 1967), the “predictive coding” approach in neuroscience (Srinivasan et al., 1982; Rao and Ballard, 1999; Huang and Rao, 2011) and “generative models” and related probabilistic computational principles (MacKay, 1956; Mumford, 1992; Dayan et al., 1995; Hinton, 2007a,b; Tenenbaum et al., 2011).

				@ \rewrite{The brain is constantly confronted with a wealth of sensory information that must be processed efficiently to facilitate appropriate reactions. One way of optimizing this processing effort is to predict incoming sensory information based on previous experience so that expected information is processed efficiently and resources can be allocated to novel or surprising information. Theoretical and computational studies led to the formulation of the predictive coding framework (Friston 2005, Hawkins and Blakeslee 2004, Mumford 1992, Rao and Ballard 1999). Predictive coding states that the brain continually generates models of the world based on context and information from memory to predict sensory input. In terms of brain processing, a predictive model is created in higher cortical areas and communicated through feedback connections to lower sensory areas. In contrast, feedforward connections process and project an error signal, i.e. the mismatch between the predicted information and the actual sensory input (Rao \& Ballard, 1999). The predictive model is constantly updated according to this error signal. }

				@ \rewrite{Predictive inference and perception The concept of PC overturns classical notions of perception as a largely ‘bottom-up’ process of evidence accumulation or feature detection, proposing instead that perceptual content is speciﬁed by top-down predictive signals that emerge from hierarchically organized generative models of the causes of sensory signals. According to PC, the brain is continuously attempting to minimize the discrepancy or ‘prediction error’ between its inputs and its emerging models of the causes of these inputs via neural computations approximating Bayesian inference (Figure 1 and Box 1). Importantly, prediction errors can be minimized either by updating generative models (perceptual inference and learning; changing the model to ﬁt the world) or by performing actions to bring about sensory states in line with predictions (active inference; changing the world to ﬁt the model).}

				@ \rewrite{In terms of brain function, Hermann von Helmholtz’s 19th Century notion of perception as unconscious inference has found new momentum in modern formulations of ‘predictive processing’, the Bayesian brain, and the ‘free energy principle’ (Clark, 2013; Friston, 2010; Hohwy, 2013). On these formulations, which can all be subsumed under the general term ‘prediction error minimization’ (PEM, (Hohwy, 2013)) perceptual content is the result of probabilistic inference on the hidden causes of sensory signals. }

				@ \rewrite{Generative models encoded by brain structure and dynamics make predictions about sensory inputs, based on prior expectations. Action (e.g., body movements) and perception conspire to reduce sensory prediction errors, giving rise to perceptual content and}

				@ \rewrite{More informally, what we perceive is the brain’s ‘best guess’ of what’s out there (or ‘in here’, for perceptions of body and self).}

				@ \rewrite{“ predictive processing ” (PP) 1 or the “ Bayesian brain ” this holds that perceptual content is determined by hierarchically organized generative (i.e., predictive) models (HGMs) of the external causes of sensory signals, induced by a process approximating Bayesian inference (Friston, 2009).}

				@ Not all predictive mechanism are conscious.

				@ We hypothesize that the distinction between conscious and unconscious predictive mechanisms is whether they build up on the information from the NTIC process.

				@ we can also explain why only the result (posterior) of predictive processing is conscious.

				@ Because of this XXXX, the representation has the maximal \ac{ntic} also has the maximal predictive power of the external environment. \todo[inline]{I need math here!!}

				@ Therefore, it's reasonably assume that if evolution wants to build predictive mechanisms, the mechanisms should be settled on the information at the \ac{cged} level.

				@ More specifically, a forward model, which received state and action as input and compute transition and then output next states, should be build on the representation that forms the \acl{ic}.

				@ Therefore, the state of predictive model can be conscious while it is linked to \acl{ic} representation.

				@ Note that, a system showing some predictive power is not sufficient to be conscious.

				@ For example, the proportional–integral–derivative controller (PID) controller shows predictive behaviours due to its derivative which computes and predict error value in the future. Derivative action predicts system behaviour and thus improves settling time and stability of the system.

				@ However, the state of the whole PID system still be determined by the inputs, i.e. the states of the controlled process, thus cannot complete \acl{ic}.

				. It can compute position, velocity, and acceleration of objects, and output control signals (action). However, the state of the PID controller is not information-closed. The state still fully determined by the input signals. Therefore, it fails to reach \ac{ic}. Hence, according to our theory, the PID system is not conscious.

				@ Similarly, the neural system also has many circuits that show predictive power but do not have \ac{ic}.

			\end{WritingMaterials}

			\subsubsection{statistical learning/prediction is not conscious}
				\begin{ants}
					@ considers the brain as a predictive machine
					@ According to predictive processing account, conscious contents are the inference results (posterior from Bayesian inference framework) of predictive mechanism.

					@ However, we can see that not all predictive mechanisms in the neural system can be consciously aware of.

					@ So what's the critical difference between them in terms of consciousness?

					@ We argue that when predictive mechanisms utilise the information in the informational closure, the predictive result is conscious.

					@ Because the forward model build on the informational closure representation can be seen as part of the closure. \critical{IS THIS TRUE? NEED DISCUSSION}

					@ we can consider two scenarios

						@@ Predictive information is encoded in neuron populations but there is high entropy of conditional probability which means it's not closure. Therefore, the conscious level could be very low even though the it still has some degree of predictability.

						@@ Another scenario is a forward model but its state fully depends on external sensory input. This system is not informational closured and therefore is not conscious.

						@@ Based on this point of view, predictive power for a system does not guarantee consciousness.

						@@ For example, in active inference \needref{active inference}, action is guided by prediction error so the state of the system is non-closured.

				\end{ants}

\rlstart{1}
		\subsection{Integrated information theory\needhelp{Help from Jun?}}
			\begin{ants}

			@ One common principle between our theory and IIT is that instead of NCC, both theories suggest information is the fundamental entity which correlates consciousness. \needref{cite David Chalmers}

			@ Our theory is different from IIT which proposes that consciousness is information integration in a system.

			@ For level of consciousness, IIT predicts a system with higher level of integration produces a higher level of consciousness. In our theory, the level of consciousness corresponds to the level of NTIC, which suggests that level of consciousness is determined by self-predictive information and the information about the environment encoded in the process.

			@ In terms of conscious content, IIT suggests that the causal structure of a system determines the quality of conscious contents. In the current version of our theory, how the state of NTIC process maps to conscious content has not been sophisticatedly specified. More work is needed to understand the relationship between the state of NTIC process and conscious contents.

		    @ --------------------------------------------------------------------
			@ \toWrite{Information integration without awareness}\cite{Mudrik_Faivre_Koch}
			@ \rewrite{consciousness is necessary for high-level but not low-level semantic integration}\cite{Mudrik_Faivre_Koch} we would argue an inverse relationship:"High-level information processing is necessary for consciousness." This is because higher-level information processing is more likely to create an informational closure representation.

			@ Similarly, it is not \rewrite{consciousness is necessary for multisensory integration}. It should be multisensory integration is more likely to create an informational closure representation. Because in most situations, multisensory signals are generated from hidden causes which may have deterministic dynamic and relation with each other. Therefore, to infer the hidden causes and represent the deterministic relations can form informational closure representation which is conscious.

			\end{ants}

			\subsubsection{Hoel's theory\needhelp{Help from Martin?}}
				\ideaBox{This is very important. Need to be careful here.}

				\begin{ants}

				    @ Our theory is closely related to causal emergence described by Hoel et al. (2013) which was examined by a following work using integrated information theory (Hoel et al. 2016). More research on the precise mathematical relationship between causal emergence and our theory is needed

					@ \cite{hoel2016can}
					@ causal emergence
					@ \cite{hoel2013quantifying} examined causal power at different coarse-grained scale and show that causal power can be stronger at macro rather than micro levels.

					@ To answer the question about what is the best scale to compute Phi, \cite{hoel2016can} examined causal power at different coarse-grained scale.

					@ Further instigation is needed to elucidate the relationship between our theory and causal emergence

				\end{ants}

\rlend

		\subsection{Internal simulation and self-modelling theory}

    \section{Limitation}

    \subsection{Finding potential coarse-graining functions}
    To empirically verify the current theory, it is important to know what coarse-graining functions which maps microscopic variables to macroscopic variables in the neural system. So far, in this article, we have not speculated potential candidates of the coarse-graining function (or functions) that creates NTIC in the neural system.

    \cite{Gamez2016} has systematically describe a similar issue in terms of finding data correlates of consciousness amount different 
    level of abstraction.

        \begin{ants}
            @ Our theory does not intent to solve the Hard problems. 
            @ Inverted spectrum Inverted Qualia \citep{Shoemaker1982-SHOTIS, Block1990-BLOIE, Locke1979-LOCTCE-2}

            @ Considering that a system has only two possible physical states $X$ and $Y$ mapping to three different qualia (we can label them as $"red"$ and $"blue"$ respectively). A system cannot rest on two states at any moment, therefore, knowing the system state at $X$ excludes the the other possible state $Y$ and receives 1 bit information. Similarly, if conscious percept is $"red"$, it rules out the $"blue"$. Therefore, information provides by the conscious percept is also 1 bit.

            @ However, our theory cannot tell why $X$ and $Y$ map to $red$ and $blue$ ,respectively, rather than the other way around.

            @

            @ Our theory does not explain the mapping
        \end{ants}

	\section{Future works}
		\begin{ants}

			@ Lack of direct evidence because no one focus on informational closure.

			@ Physiological location of NTIC

			@ Practical measure of NTIC.

		\end{ants}

		\subsection{Finding coarse-grain function}
			\begin{ants}
				@ It's not clear what the coarse-graining function is.\critical{this should be explained by environmental deterministic}

				@ \rewrite{
					not all causal relationships (or relationships of nomological dependency) among micro-events aggregate up to causal relationships among coarse-grained macro-events that are constituted by those micro-events. Instead, whether one gets causation at the macroscopic level will depend (among other things) on the particular coarse-graining that is chosen.} \cite{price2007causation}

				@ \rewrite{
					It may seem surprising, even counterintuitive, that causal and statistical dependence relationships involving fine grained microscopic variables do not automatically show up in causal and dependence relationships among the macroscopic variables that are realized by the fine grained variables.} \cite{price2007causation}

				@ \cite{jonas2017could} well demonstrated that it is difficult to understand higher-level information processing by the current neuroscience methods.

			\end{ants}

%	\section{Evolution of conscious mind (not sure but if I have time)}
%		\cite{dennett2008kinds}

	\section{Conclusion}
		\begin{ants}
			@ Why is this theory better than other theories of consciousness
			@ NCC: To find NCC, it's not about where and when, it's about scale and level of description
		\end{ants}

	% ============================================================================ %
	%                                      End                                     %
	% ============================================================================ %

	\section*{Funding}

	\section*{Acknowledgements}

	\section*{Supplemental Data}

	\bibliographystyle{authordate1}
	\bibliography{ref}

\newpage
\begin{backup}
\part*{Backup}
\addcontentsline{toc}{part}{Backup}
\setcounter{section}{0}
	\section*{Biological evidence of informational closure in neural system}
		\begin{ants}
			% ============================================================================ %
			%                             sederberg2018learning                            %
			% ============================================================================ %

			@ So far, not so much research on non-trivial informational closure in biological neural systems.

			@ However, \rewording{XXX}

			% Internal self-predictive mechanism
			@ Recent biological evidence suggests that low-level neurons encodes predictive information about external  and

			@ \toWrite{
				need to say this is exactly the non-trivial informational closure, and refer to equation XXX}

			@ \cite{sederberg2018learning}
			@ \rewrite{
				in recordings of populations of RGCs of salamander retina driven by a simple stimulus with partially predictable dynamics, joint activity patterns transmit information that is predictive of future stimuli }

			@ \rewrite{
				We examined whether the temporal correlations within populations of RGCs can be used to guide the search for readouts of predictive information.}

			@ \rewrite{
				We showed that groups of cells with high external, stimulus-predictive information also had high internal predictive information on two classes of stimuli, }

			@ \rewrite{
				Very simple learning rules could find near-optimal readouts of predictive information without any external instructive signal. This suggests that bottom-up prediction may play an important role in sensory processing}

			@ \rewrite{
				Internal predictive information can guide stimulus prediction without explicit reference to stimulus parameters.}

			@ \rewrite{
				Word–word internal predictive information is correlated with word–stimulus predictive information across sets of four cells.}

			@ They also showed generalization of internal predictability across stimulus. This suggests .... what?

			@ \rewrite{
				The generalization of internal predictability across stimulus classes partially reflects the ability of the retina to adapt to the statistics of stimuli}

			@ \cite{Palmer2015}
			@ \rewrite{
				Groups of cells in the retina carry information about the future state of their own activity, and we show that this information can be compressed further and encoded by downstream predictor neurons that exhibit feature selectivity that would support predictive computations.}

			@ \rewrite{
				It seems natural to phrase the problem of prediction in relation to the visual stimulus, as in Fig. 3, but the brain has no direct access to visual stimuli except that provided by the retina. Could the brain learn, in an unsupervised fashion, to predict the future of retinal outputs? More precisely, if we observe that a population of retinal ganglion cells generates the word w t at time t, what can we say about the word that will be generated at time t + Δ t in the future? The answer to this question is contained in the conditional distribution of one word on the other, P ð w t +Δ t j w t Þ } \url{http://tinyurl.com/y9zmhlln}

			@ \rewrite{
				larger groups of cells carry predictive information for hundreds of milliseconds, }

		\end{ants}

	\section*{Relation to empirical findings in neuroscience and studies of consciousness}

		\subsection{Unconscious Processing}
		\begin{ants}
			@ According the theory, there are two factor that renders neural processes unconscious.

			@ First, processes are reflexive. This causes non-closured

			@ Second, the abstraction level of the information is below the non-trivial informational closure scale.
		\end{ants}

		\subsection{reflexive behaviours is unconscious (or environment-state dependent processes)}\label{sec:reflexive}
		\subsubsection{Reflection}
		\begin{ants}
			@ Reflexive systems is not informational closured.
			@ Base	d on our theory,
			@ x -> s -> a
			@@ the system state is determined by environmental state, then it is not conscious.
			@ Therefore, in general, a simple policy network is not conscious.
		\end{ants}

		\subsubsection{Blindsight}
		\begin{ants}
			@ This also blindsight.
			@ Blindsight patients and still make above chance judgement without conscious awareness of visual targets.
			@ The stimulus-reaction policy network still intact, but it cannot form informational closure and therefore, patients has no conscious awareness of visual  targets
			@ Patient B.F. reactions are stimulus driven.
		\end{ants}

		\subsubsection{procedure memory}

		\subsubsection{cerebellum}
		\begin{ants}
			@ cerebellum feed-forward connections, maybe just a policy network.\needref{cerebellum}
		\end{ants}

		\subsection{Under the level of informational closure}
		\subsubsection{statistical inference}
		\begin{ants}
			@ The computation of Bayesian brain is unconscious.
		\end{ants}

		\subsubsection{subliminal perception}
		\begin{ants}
			@ Above chance performance can be performed through non-closure pathway (reflexive behaviours)

			@ Due to coarse-graining, mapping between changes of microstate
		\end{ants}
		\subsubsection{Libet Experiments}

		\subsection{Deterministic vs probabilistic}
		\cite{dehaene2017consciousness}
		\cite{vul2008temporal, moreno2011bayesian, asplund2014attentional, vul2009attention}

	\section*{About Phenomenology (conscious processing)}
\subsection{Perceptual overflow}
\subsection{Volition and freewill}
\begin{ants}
	@ Volition is a result of coarse-graining

	@ Lebel's experiment can be well explained by the experiment.
\end{ants}

\subsection{Planning}
\subsection{Imagination}
\subsection{Dream vs non-dream sleep}
\subsection{Binocular rivalry}
\subsection{Hallucinations}
\subsection{Synaesthesia}

	\section*{Theory predictions (Counter-intuitive prediction)}

\subsection{informational closure}
\begin{ants}
	@ We predict that through coarse-graining, conscious agents create
\end{ants}

\subsection{Prediction on split-brain (vs IIT)}
* IIT suggests that cutting, two subparts may both still have MIP, therefore, have two conscious mind.

* However, our theory suggests that if the cut largely destroy the \ac{ic}, then both part may not be conscious.

\end{backup}

\end{document}

### 2019-04-25 Paper_neural_coarse_graining_of_consciousness.tex
Updates from Overleaf

@@
 		\subsection{Unconscious Processing}
-		As described above, if information processing fails to meet either one of the two necessary conditions, information remains unconscious.
-First, considering processes which fail to meet the first condition.
-That is, a information process is not NTIC.
-We can see many information processing in the neural network system fall in this category.
+		\begin{ants}
+		    @ As described above, if information processing fails to meet either one of the two necessary conditions, information remains unconscious.
+
+		    @ First, considering processes which fail to meet the first condition. That is, a information process is not NTIC. We can see many processes in the neural network system fall in this category.
+
+		    @ In this category, processes cannot form NTIC.
+The internal states of the processes are partially or fully determined by environment states, i.e.
+information is not closed.
+Reflective behaviours are one of the main subcategory.
+
+		    @Reflective behaviours usually are considered as automatic and non-conscious behavioural controls. \citep{casali2013theoretically}\needref{More referene}.
+
+		    @ In modern reinforcement learning framework, this usually is referred to policy-based agents.
+The agents constructs a policy function that maps sensory inputs to the action space \citep{sutton2018reinforcement}.
+
+		    @  Roughly speaking, a policy is a mapping from perceived states of the environment to actions to be taken when in those states.
+It corresponds to what in psychology would be called a set of stimulus–response rules or associations
+
+		    @ The same principle can be applied to blindsight and procedure memory which are often considered as the classical cases of unconscious processing
+
+		    @ This classic patient study of D.F.
+who has apperceptive agnosia \citep{10.3389/fneur.2014.00255} also falls in this category.
+With online sensory inputs, the neural system can create functional processes without forming NTIC.
+
+		    @ Note that, when we prolong the temporal interval between stimulus and action, usually consciousness is necessary for learning associations. \needref{time}
+
+		    @ Anoher case is that, processes are information closed but it is trivial.
+
+		\end{ants}
+
+		----------------------------------------------------------------------------
+		=== -
+
+		--- 
+		procedure memory
+		Reflective reaction, blindsight,
 
@@
 		\begin{aligned}
-            P(A|S)
+            \pi(A|S)\\
+            {J_{t}(E \rightarrow Y )} & {:= I(Y_{t+1};E_{t}|Y_{t})} > 0
         \end{aligned}
 		\end{equation}
+		\needhelp{Math here}
+
+		\begin{figure}
+			\includegraphicsTodo[width=0.8\textwidth]{WritingMaterials/S_Y_A/S_Y_A_01.png}
+			\caption{Policy network}
+			\label{fig:s2a}
+		\end{figure}
 

### 2019-04-27 Paper_neural_coarse_graining_of_consciousness.tex
Updates from Overleaf

@@
 
-		    @ Anoher case is that, processes are information closed but it is trivial.
+		    @ Another case is that, processes are information closed but it is trivial.
+
+		    @ ============================================================================
+
+		    @ Even though the system can form NTIC processes in some certain coarse-grained levels, information processing outside these levels remains unconscious.
+
+		    @ microscopic neural activities fall in this category.
+
+		    @ When processes at macroscopic levels becomes informational closed, information from other levels is redundant.
+
+		    @ Therefore, information from other levels does not influence the dynamic of this level.
 

### 2019-05-01 Paper_neural_coarse_graining_of_consciousness.tex
Update from local

@@
 Could the brain learn, in an unsupervised fashion, to predict the future of retinal outputs?
-More precisely, if we observe that a population of retinal ganglion cells generates the word w t at time t, what can we say about the word that will be generated at time t + Δ t in the future?
-The answer to this question is contained in the conditional distribution of one word on the other, P ð w t +Δ t j w t Þ } \url{http://tinyurl.com/y9zmhlln}
+More precisely, if we observe that a population of retinal ganglion cells generates the word w t at time t, what can we say about the word that will be generated at time t + delta t in the future?
+The answer to this question is contained in the conditional distribution of one word on the other, P ð w t +delta t j w t Þ } \url{http://tinyurl.com/y9zmhlln}
 
@@
 
-		\subsection{Informational closure and level identification \ideaCallout{maybe not necessary}}
-
-		\subsection{Biological Creature may try to achieve closure even the environment is not \ideaCallout{Maybe not necessary}}
+		\subsection{Informational closure and level identification}
+
+		\subsection{Biological Creature may try to achieve closure even the environment is not}
 
@@
 	    In this section, we suggest that our theory has a strong exploratory and predictive power but with minimal assumptions.  
-		Our theory indicates that to make information conscious two necessary conditions need to be satisfied with in any system.
+		Our theory indicates that, to make information conscious, a sufficient and a necessary conditions need to be satisfied.
 
 		\begin{enumerate}
-		    \item Information is encoded in NTIC process. 
-		    \item The system is capable of constructing NTIC processes at coarse-grained levels. 
+		    \item Sufficient condition: Information is encoded in NTIC process. 
+		    \item Necessary condition: The system is capable of constructing NTIC processes at coarse-grained levels. 
 		\end{enumerate}
@@
     		    @@ Libet's experiment
+    		    @@ Unconscious determinants of free decisions in the human brain    		    
     		    @@ Priming
@@
     		    @@ Perceptual overflow
-    		    @@ Unconscious determinants of free decisions in the human brain
     		    @@ Threshold of unconscious to consciousness
@@
 				@ \rewrite{
-					The ﬁrst-order view maintains that conscious awareness is determined by early sensory activity alone, independently of higher-order representations.
-Thus the crucial difference between the ﬁrst-order and higher-order views is that the latter but not the former predict that conscious awareness is determined at least in part by prefrontal and parietal activity.
-Therefore, in the group of ﬁrst-order theorists we include here not only those commonly labeled as such in the philosophical literature [11] but also theorists, such as Ned Block [12,13], who hold that the phenomenal qualities of awareness depend on the biological substrate rather than merely the content of the ﬁrst-order representations, as well as scientists who hold that visual awareness depends on activity in content-speciﬁc regions of the extrastriate cortex [24,25] or on feedback from these regions to the primary visual cortex [26].
-Most ﬁrst-order theories explain the difference between awareness and unawareness by positing that the latter is associated with weak information [29] or with representations in alternative (e.g.
+					The first-order view maintains that conscious awareness is determined by early sensory activity alone, independently of higher-order representations.
+Thus the crucial difference between the first-order and higher-order views is that the latter but not the former predict that conscious awareness is determined at least in part by prefrontal and parietal activity.
+Therefore, in the group of first-order theorists we include here not only those commonly labeled as such in the philosophical literature [11] but also theorists, such as Ned Block [12,13], who hold that the phenomenal qualities of awareness depend on the biological substrate rather than merely the content of the first-order representations, as well as scientists who hold that visual awareness depends on activity in content-specific regions of the extrastriate cortex [24,25] or on feedback from these regions to the primary visual cortex [26].
+Most first-order theories explain the difference between awareness and unawareness by positing that the latter is associated with weak information [29] or with representations in alternative (e.g.
 subcortical) sensory pathways.
 Thus this view suggests that conscious and unconscious processing will have different functional consequences.
-Whereas some ﬁrst-order theorists hold that some higher cognitive functions can be performed without conscious awareness [30–32], most ﬁrst-order theorists take a difference in perceptual task performance (e.g.
+Whereas some first-order theorists hold that some higher cognitive functions can be performed without conscious awareness [30–32], most first-order theorists take a difference in perceptual task performance (e.g.
 ‘hits’ vs ‘misses’ in a detection task) as evidence for a difference in conscious awareness [12,13,25,26,33].
@@
 			@ \rewrite{
-				neutral about whether conscious awareness adds signiﬁcant utility or immediate impact on behavior and task performance [1,27].
-This is because the view assumes that task performance in most perceptual and cognitive tasks depends mainly on ﬁrst-order rather than higher-order representations.
-Because conscious awareness can differ even if all ﬁrst-order representations remain completely unchanged, such awareness itself might serve little function [1,27].}\cite{lau2011empirical}
+				neutral about whether conscious awareness adds significant utility or immediate impact on behavior and task performance [1,27].
+This is because the view assumes that task performance in most perceptual and cognitive tasks depends mainly on first-order rather than higher-order representations.
+Because conscious awareness can differ even if all first-order representations remain completely unchanged, such awareness itself might serve little function [1,27].}\cite{lau2011empirical}
 				\ideaCallout{
@@
 					Metacognition: cognition that is about another cognitive process as opposed to about objects in the world.
-In this article we use it mainly to refer to sensory metacognition: a cognitive process that concerns the quality or efﬁcacy of a perceptual process.
+In this article we use it mainly to refer to sensory metacognition: a cognitive process that concerns the quality or efficacy of a perceptual process.
 The capacity of sensory metacognition is sometimes empirically assessed by the correspondence between subjective report and task performance: how closely are they associated with each other on a trial-by-trial basis}\cite{lau2011empirical}
@@
 Although many cognitive operations can be partially launched non-consciously, these operations rarely if ever run to completion in the absence of consciousness.
-A subliminal stimulus may induce above-chance performance, behavioural priming, and a small amount of brain activity in narrowly deﬁned brain networks, but these measures often increase dramatically as soon as the subject reports seeing the stimulus, especially in high-level areas [46 60,61  ].
-Accumulation of evidence has been demonstrated with non-conscious stimuli [59], but only conscious stimuli cross the threshold beyond which an overt strategy can be ﬂexibly deployed.
+A subliminal stimulus may induce above-chance performance, behavioural priming, and a small amount of brain activity in narrowly defined brain networks, but these measures often increase dramatically as soon as the subject reports seeing the stimulus, especially in high-level areas [46 60,61  ].
+Accumulation of evidence has been demonstrated with non-conscious stimuli [59], but only conscious stimuli cross the threshold beyond which an overt strategy can be fiexibly deployed.
 \todo{Cite similar opinion from other theories}
@@
 
-					@ e ‘all-or-none’ behavior, whereby the incoming evidence either quickly dies out (corresponding to subliminal processing) or is accumulated and ampliﬁed non-linearly into a full-blown state of high-level activity.
+					@ e ‘all-or-none’ behavior, whereby the incoming evidence either quickly dies out (corresponding to subliminal processing) or is accumulated and amplified non-linearly into a full-blown state of high-level activity.
 This global ‘ignition’ has been proposed as a marker of conscious perception [70].
-Indeed, empirically, when stimulus strength is varied, the early stages of non-conscious processing typically show a linear variation in activation, whereas conscious access is often characterized by a late non-linear ampliﬁcation of activation which invades a distributed set of parietal, prefrontal and cingulate areas
+Indeed, empirically, when stimulus strength is varied, the early stages of non-conscious processing typically show a linear variation in activation, whereas conscious access is often characterized by a late non-linear amplification of activation which invades a distributed set of parietal, prefrontal and cingulate areas
 				\end{WritingMaterials}
@@
 Although many cognitive operations can be partially launched non-consciously, these operations rarely if ever run to completion in the absence of consciousness.
-A subliminal stimulus may induce above-chance performance, behavioural priming, and a small amount of brain activity in narrowly deﬁned brain networks, but these measures often increase dramatically as soon as the subject reports seeing the stimulus, especially in high-level areas [46 60,61  ].
-Accumulation of evidence has been demonstrated with non-conscious stimuli [59], but only conscious stimuli cross the threshold beyond which an overt strategy can be ﬂexibly deployed.
+A subliminal stimulus may induce above-chance performance, behavioural priming, and a small amount of brain activity in narrowly defined brain networks, but these measures often increase dramatically as soon as the subject reports seeing the stimulus, especially in high-level areas [46 60,61  ].
+Accumulation of evidence has been demonstrated with non-conscious stimuli [59], but only conscious stimuli cross the threshold beyond which an overt strategy can be fiexibly deployed.
 				\end{WritingMaterials}
@@
 
-				@ In their seminal article O’Regan and Noe¨ (2001) introduce sensorimotor contingencies (SMCs) as the basis of a sensorimotor account of conscious perception.
+				@ In their seminal article O’Regan and Noë (2001) introduce sensorimotor contingencies (SMCs) as the basis of a sensorimotor account of conscious perception.
 
@@
 1015; see also [9,10,19,20]).
-This ‘ non-acute ’ or dispositional variant marks a signi ﬁ cant shift in position because it de-emphasizes actual movement.
+This ‘ non-acute ’ or dispositional variant marks a signi fi cant shift in position because it de-emphasizes actual movement.
 \cite{pennartz2017consciousness}
@@
 
-					@@ However, these authors have so far been very reticent about how exactly consciousness ﬁts into the PC framework.
-For now, there is an emerging idea that understands consciousness as the ﬁnal result of unconsciousness processing.
-According to Hohwy (2013), perceptual consciousness ﬁts in the PC theory as the ‘upshot’ or ‘conclusion’ of unconscious perceptual inferences.
+					@@ However, these authors have so far been very reticent about how exactly consciousness fits into the PC framework.
+For now, there is an emerging idea that understands consciousness as the final result of unconsciousness processing.
+According to Hohwy (2013), perceptual consciousness fits in the PC theory as the ‘upshot’ or ‘conclusion’ of unconscious perceptual inferences.
 Melloni (2014) also expects that inferential processes are conducted behind the curtain of consciousness and what we experience are the ‘outcomes’ or ‘results’ of an unconsciou inferential process.
@@
 
-				@ \rewrite{Predictive inference and perception The concept of PC overturns classical notions of perception as a largely ‘bottom-up’ process of evidence accumulation or feature detection, proposing instead that perceptual content is speciﬁed by top-down predictive signals that emerge from hierarchically organized generative models of the causes of sensory signals.
+				@ \rewrite{Predictive inference and perception The concept of PC overturns classical notions of perception as a largely ‘bottom-up’ process of evidence accumulation or feature detection, proposing instead that perceptual content is specified by top-down predictive signals that emerge from hierarchically organized generative models of the causes of sensory signals.
 According to PC, the brain is continuously attempting to minimize the discrepancy or ‘prediction error’ between its inputs and its emerging models of the causes of these inputs via neural computations approximating Bayesian inference (Figure 1 and Box 1).
-Importantly, prediction errors can be minimized either by updating generative models (perceptual inference and learning; changing the model to ﬁt the world) or by performing actions to bring about sensory states in line with predictions (active inference; changing the world to ﬁt the model).}
+Importantly, prediction errors can be minimized either by updating generative models (perceptual inference and learning; changing the model to fit the world) or by performing actions to bring about sensory states in line with predictions (active inference; changing the world to fit the model).}
 
@@
 \rlstart{1}
-		\subsection{Integrated information theory\needhelp{Help from Jun?}}
+		\subsection{Integrated information theory}
 			\begin{ants}

### 2019-05-06 Paper_neural_coarse_graining_of_consciousness.tex
Updates from Overleaf

@@
 \usepackage{graphicx}
+\usepackage{svg}
 \usepackage[colorlinks=true, allcolors=blue]{hyperref}
@@
 	\section{Conscious versus Unconscious Processing}
-
-\rlstart{3}	
 		\ideaBox{The goal of this part is to combine empirical study and phenomenology}
@@
 		\subsection{Unconscious Processing}
-		\begin{ants}
-		    @ As described above, if information processing fails to meet either one of the two necessary conditions, information remains unconscious.
-
-		    @ First, considering processes which fail to meet the first condition. That is, a information process is not NTIC. We can see many processes in the neural network system fall in this category.
-
-		    @ In this category, processes cannot form NTIC.
-The internal states of the processes are partially or fully determined by environment states, i.e.
-information is not closed.
-Reflective behaviours are one of the main subcategory.
-
-		    @Reflective behaviours usually are considered as automatic and non-conscious behavioural controls. \citep{casali2013theoretically}\needref{More referene}.
+\rlstart{3}			
+		    \subsubsection{\sim 1}
+		    % reflexive behaviour
+    		\begin{figure}[H]
+    			\includegraphics[width=0.8\textwidth]{WritingMaterials/Fig_Reflexive/Reflexive.pdf}
+    			\caption{Reflexive Behaviours}
+    			\label{fig:reflexive}
+    		\end{figure}
+
+    		\begin{ants}
+    		    @ As described above, if a process fails to meet either one of the two necessary conditions, information remains unconscious.
+
+    		    @ We first consider the first condition: A process fails to achieve NTIC.
+
+    		    @ Many processes in the neural network system fall in this category.
+
+    		    @ When a process is not information closed the internal state of the process is largely determined by the environmental state.
+
+    		    @ In terms of perception, this indicates that the process only passively reacts.
+
+    		    @ In terms of action, this implies reflective behaviours.
+
+    		    @ Reflective behaviours usually are considered as automatic and non-conscious behavioural controls. \citep{casali2013theoretically}\needref{More referene}.
+
+    		    @
 
@@
     		\end{ants}
+\rlend
 
@@
 
-\rlend
-
 	\section{Comparison with other theories}

### 2019-05-10 Paper_neural_coarse_graining_of_consciousness.tex
Updates from Overleaf

@@
 
-				\begin{equation}\label{eq:InformationFlow}
+				\begin{equation}
+    				\label{eq:InformationFlow}
     				\left.\begin{array}
@@
 				\begin{equation}
+				\label{eq:NTIC}
     				\left.\begin{array}
@@
 			And, Maximising NTIC is equivalent to
-				\begin{equation}\label{eq:nticObjective}
+				\begin{equation}
+    				\label{eq:nticObjective}
     				\begin{aligned}
@@
 		\subsection{Unconscious Processing}
-\rlstart{3}			
-		    \subsubsection{\sim 1}
+
+        \subsubsection{Fail to meet 1\lowercase{st} condition}
+\rlstart{4}        	As described above, if a process fails to fulfil either of the two conditions, information remains unconscious.
+First, We consider that a process fails to satisfy the first condition, i.e.
+the process fails to achieve NTIC.
+Many processes in the neural system fall into this category.
+
+        	Considering the objectives of achieving NTIC (Equation \ref{eq:nticObjective}), if a process fails to maximise $I(Y_{t+1};Y_{t})$ or minimise $I(Y_{t+1};Y_{t}|E_{t})$, this results in low NTIC.
+The failure to maximise $I(Y_{t+1};Y_{t})$ implies the past states has small influence on its future states.
+In the meantime, if the process still receives environmental information and produces outputs, the future state of the process is largely determined by the past environmental states (fig.\ref{Fig:reflexive}), i.e.
+the process is not informational closed (${J_{t}(E \rightarrow Y )} \not\approx 0$).
+
+            % If the future states of the system have strong mutual information with the current environmental states ($I(Y_{t+1};E_{t})$) but have weak mutual information with the current system states ($I(Y_{t+1};Y_{t})$), the informational closeness will be small.
+
     	    % reflexive behaviour
@@
 
-    		\begin{ants}
-    		    @ As described above, if a process fails to meet either one of the two necessary conditions, information remains unconscious.
-
-    		    @ We first consider the first condition: A process fails to achieve NTIC.
-
-    		    @ Many processes in the neural network system fall in this category.
-
-    		    @ When a process is not information closed the internal state of the process is largely determined by the environmental state.
-
-    		    @ In terms of perception, this indicates that the process only passively reacts.
-
-    		    @ In terms of action, this implies reflective behaviours.
-
-    		    @ Reflective behaviours usually are considered as automatic and non-conscious behavioural controls. \citep{casali2013theoretically}\needref{More referene}.
-
-    		    @
-
-    		    @ In modern reinforcement learning framework, this usually is referred to policy-based agents.
-The agents constructs a policy function that maps sensory inputs to the action space \citep{sutton2018reinforcement}.
-
-    		    @  Roughly speaking, a policy is a mapping from perceived states of the environment to actions to be taken when in those states.
-It corresponds to what in psychology would be called a set of stimulus–response rules or associations
-
-    		    @ The same principle can be applied to blindsight and procedure memory which are often considered as the classical cases of unconscious processing
-
-    		    @ This classic patient study of D.F.
-who has apperceptive agnosia \citep{10.3389/fneur.2014.00255} also falls in this category.
-With online sensory inputs, the neural system can create functional processes without forming NTIC.
-
-    		    @ Note that, when we prolong the temporal interval between stimulus and action, usually consciousness is necessary for learning associations. \needref{time}
-
-    		    @ Another case is that, processes are information closed but it is trivial.
-
-    		    @ ============================================================================
-
-    		    @ Even though the system can form NTIC processes in some certain coarse-grained levels, information processing outside these levels remains unconscious.
-
-    		    @ microscopic neural activities fall in this category.
-
-    		    @ When processes at macroscopic levels becomes informational closed, information from other levels is redundant.
-
-    		    @ Therefore, information from other levels does not influence the dynamic of this level.
-
-    		\end{ants}
-\rlend
-
-		----------------------------------------------------------------------------
-		=== -
-
-		--- 
-		procedure memory
-		Reflective reaction, blindsight,
-
-		\begin{equation}\label{eq:InformationFlow}
+            In the context of information processing in the neural system, regarding to perception, this indicates that the perceptual processes only passively responds to the sensory inputs.
+Regarding to action, this indicates that the process only produces reflective-like behaviour.
+Reflexive behaviours are commonly considered as automatic and non-conscious behavioural controls.
+\citep{casali2013theoretically}\needref{More referene}.
+We hypothesise that this is a natural consequence when a process fails to meet the first condition.
+
+            The same notion can be applied to blindsight and procedure memory \needref{blindsight}.
+Blindsight patients are able to track objects and avoid obstacles within the visual field without having any visual conscious experience.
+The direct stimulus-response mapping ($S\rightarrowR$) makes the internal neural circuit a non-NTIC process and results in unconscious processing.
+In the case of procedure memory, processes often relies on both the current environmental and system states to determine the next state of the processes\needref{Do I need ref??}.
+Therefore, they also fail to achieve high NTIC as well.
+
+             This is similar to the model-free policy-based agents in the reinforcement learning framework.
+The process of a system only maps the input state space to the action state space \needref{11}.
+The agent learns a policy $\pi$ which directly maps sensor values $S$ to output action $A$.
+            % @ $\pi : S \times A$\\
+    		\begin{equation}
+    			\label{eq:PolicyBasedAgent}
     			\begin{aligned}
-            \pi(A|S)\\
-            {J_{t}(E \rightarrow Y )} & {:= I(Y_{t+1};E_{t}|Y_{t})} > 0
+    			    \pi(A | S)=\operatorname{Pr}\left(A_{t}=a | S_{t}=s\right)
     			\end{aligned}
     		\end{equation}
-		\needhelp{Math here}
-
-		\begin{figure}
-			\includegraphicsTodo[width=0.8\textwidth]{WritingMaterials/S_Y_A/S_Y_A_01.png}
-			\caption{Policy network}
-			\label{fig:s2a}
-		\end{figure}
+
+    		This can explain why the patient D.F., who has apperceptive agnosia, can perform online motor controls without visual awareness of the action targets  \citep{10.3389/fneur.2014.00255}.
+    		Finally, an interesting implication from our theory is that a pure feedforward neural network cannot be conscious because there is no way to maintain any form of memory of a system and such that there is zero influence from the system past states to its future state.
+On the contrary, with recurrent loops, a neural network can create information channels from its past to its future and becomes capable of achieving NTIC.
+This result coincide with some theories of consciousness which hypothesise the recurrent neural circuits as the NCC \needref{recurrent and NCC}.
+However, we derive this conclusion from a more fundamental informational-related hypothesis showing that our theory has a stronger explanatory power.
+\rlend
+
+        \subsubsection{Fail to meet 2\lowercase{ed} condition}
+\rlstart{3}        
+            \begin{ants}
+                @ Due to the coarse-grained level-dependence of information processing, if a process is not at levels achieving NTIC, the information remains unconscious.
+
+        	    @ Even though a system can form NTIC processes at some certain coarse-grained levels, information processing outside these levels remains unconscious.
+
+        	    @ The first implication from this scenario is that processes at levels with high stochasticity are unable to achieve high NTIC and hence unconscious.
+High stochasticity corrupts informational channel capacity and leads to low mutual information between past and future states of a process.
+
+        	    @ In the neural system, the cellular level activities are highly noisy.
+
+        	    @ This prevents information from cellular activities from forming high NTIC processes.
+
+        	    @ Therefore, we never can be aware of detail activities at microscopic in the neural system.
+
+        	    @ Some may argue that empirical evidence suggests single cell level correlation of conscious experience, the Jennifer Aniston cell for example.
+
+        	    @ However, to note that, the correlation is always not the microscopic state changes of the cells, e.g.
+the action potentials.
+Instead, the correlated variables are always coarse-grained, for example the firing rate which is temporal coarse-grained variables.
+
+        	    @ Second, it has been well established that heterogeneous nonlinearity is crucial for neural populations to encode rich and high dimensional information.
+\citep{Chelaru2008, Rigotti2010Oct, Shamir2004Jun}.
+Finding a single neuron whose activities align with a subspace representing a single object within the state space of a population code.
+\ideaCallout{Not sure if I want to add this point}
+
+        	    @ This also explains why we are not aware of probabilistic inference performed by the neural system.
+
+        	    @ Previous studies have showed that the neural system can encode probability distribution and perform probabilistic inference in a near optimal way.
+
+        	    @ However, in
+
+            \end{ants}
+
+            \begin{WritingMaterials}
+
+                @ \rewrite{Such unconscious systems compute with probability distributions, but only a single sample, drawn from this probabilistic distribution, becomes conscious at a given time ( 27 , 28 ).
+We may become aware of several alternative interpretations, but only by sampling their unconscious distributions over time ( 29 , 30 ).}
+
+            \end{WritingMaterials}
+
+\rlend
+
+% 		\begin{figure}
+% 			\includegraphicsTodo[width=0.8\textwidth]{WritingMaterials/S_Y_A/S_Y_A_01.png}
+% 			\caption{Policy network}
+% 			\label{fig:s2a}
+% 		\end{figure}
 

### 2019-05-15 Paper_neural_coarse_graining_of_consciousness.tex
Updates from Overleaf

@@
 		% Highlight only
-		\newcommand{\highlight}[2][Yellow!75!white]{\colorbox{#1}{#2}}
+		\newcommand{\highlight}[2][Yellow]{\sethlcolor{#1}\hl{#2}}
 
@@
 
-	\section{Non-trivial informational closure}
+	\section{Non-trivial informational closure} \label{sec:Non-trivial informational closure}
 		\ideaBox{I am still not sure we should go for NTIC without describe my intuition about consciousness and closure?
@@
         \subsubsection{Fail to meet 1\lowercase{st} condition}
-\rlstart{4}        	As described above, if a process fails to fulfil either of the two conditions, information remains unconscious.
+\rlstart{4}        	
+            As described above, if a process fails to fulfil either of the two conditions, information remains unconscious.
 First, We consider that a process fails to satisfy the first condition, i.e.
@@
             The same notion can be applied to blindsight and procedure memory \needref{blindsight}.
-Blindsight patients are able to track objects and avoid obstacles within the visual field without having any visual conscious experience.
-The direct stimulus-response mapping ($S\rightarrowR$) makes the internal neural circuit a non-NTIC process and results in unconscious processing.
+            Blindsight patients are able to track objects, avoid obstacles,and make above chance level judgements without conscious awareness of visual targets within the visual field without having any visual conscious experience.
+The direct stimulus-response mapping ($S\rightarrow{}R$) makes the internal neural circuit a non-NTIC process and results in unconscious processing.
 In the case of procedure memory, processes often relies on both the current environmental and system states to determine the next state of the processes\needref{Do I need ref??}.
@@
             % @ $\pi : S \times A$\\
+            % Policy
     		\begin{equation}
@@
     		This can explain why the patient D.F., who has apperceptive agnosia, can perform online motor controls without visual awareness of the action targets  \citep{10.3389/fneur.2014.00255}.
+    		Our theory also explains why the unconscious processing in this category often fail when long delay periods are introduced in the tasks.
+Because without self-predicitve information in NTIC, the policies of motor outputs largely depends on the present sensory states implying that this type of processes can only perform online.
+With certain delays, sensory information is unable to guide the delayed motor outputs and leads to failure consequences.
+
     		Finally, an interesting implication from our theory is that a pure feedforward neural network cannot be conscious because there is no way to maintain any form of memory of a system and such that there is zero influence from the system past states to its future state.
@@
         \subsubsection{Fail to meet 2\lowercase{ed} condition}
+
+		\begin{figure}[H]
+			\includegraphics[width=1.3\textwidth]{WritingMaterials/Fig_Temperature_Example/ExampleOfCG.pdf}
+			\centering
+			\caption{An Example of ...}
+			\label{fig:TemperatureExample}
+		\end{figure}   
 \rlstart{3}        
@@
 
-        	    @ This also explains why we are not aware of probabilistic inference performed by the neural system.
-
-        	    @ Previous studies have showed that the neural system can encode probability distribution and perform probabilistic inference in a near optimal way.
-
-        	    @ However, in
+        	    @ This also explains why we are not aware of probabilistic inference performed by the neural system but only a "sample" of W
+
+        	    @ Previous studies have showed that the neural system is able to encode probability distribution and perform probabilistic inference in a near optimal way.
+
+        	    @ However, we are ignorant nearly all the computation when the neural system performs probabilistic inference.
+
+        	    @ Fig.
+\ref{fig:TemperatureExample} showed that because the computation is performed at microscopic levels, only the macroscopic variables, e.g.
+the summary statistics, are at the level with NTIC and become conscious.
+
+        	    % Libet's experient
+
+        	    @ The same scenario can also explain the results of Libet's experiment.
+In this experiment, in this experiment, Libet found that the neural activities (indicated by event-related potential) start earlier than the feeling of intention to perform an self-determined action.
+
+        	    @ \citeauthor{schurger2012accumulat}
+
+        	    @ The movement preparation initiates at the microscopic level.
+
+        	    @ However, coarse-graining always maps a larger state space at microscopic levels to a equal or smaller state space at macroscopic levels (i.e.
+a surjective function).
+As the result, the state transitions at microscopic levels do not always lead to state transitions at macroscopic levels.
+
+        	    @ Therefore, the initiative neural correlates of the free motor actions remained unconscious until the macroscopic state transition at the NTIC level.
+
+        	    % multistable perception
+        	    In the case of multistable perception, at every moment, only a single macroscopic state is mapped from the microscopic levels, we can only be aware of one interpretation at every moment.
+
+        	    % Priming
+        	    @ The same mechanism can also applied to unconscious priming effects.
+\highlight{Making state transitions at microscopic levels does not guarantee transitions at macroscopic levels.}\ideaCallout{this is the key sentence}
+
+        	    @ Of course, this is related to what kind of coarse-grain function which can form a NTIC process at macroscopic scales. We will discuss this issue in the later section.
+
+        	   @  === boundary conditions  ===
+        	   @ The third category is the boundary conditions.
+
+        	   % Binocular rivalry
+        	   @ In binocular rivalry, either eye provides information to form a NTIC process.
+Once the process is NTIC, the process continue the trajectory in the state space and close system.
+Information from the other eye is unable to enter the process, thus it remains unconscious.
+
+        	   @ Including information from either of objects information can achieve NTIC.
+
+        	   @ For example, when the information of the visual stimuli both can form the NTIC.
+
+        	   @ Our theory also explains why the conscious percepts show some kind of inertia (stably remain conscious for a period of time).
+
+        	   @ Once the NTIC process is formed, the closureness guarantees the stability of the state transitions of the process.
 
@@
 
-\rlend
-
-% 		\begin{figure}
-% 			\includegraphicsTodo[width=0.8\textwidth]{WritingMaterials/S_Y_A/S_Y_A_01.png}
-% 			\caption{Policy network}
-% 			\label{fig:s2a}
-% 		\end{figure}
-
-		When the first condition is not satisfied,
-
-		In this case, the future state of this process is partially or fully determined by environment states. We can see
-
-		\begin{ants}
-		    @ Conscious
-
-		    @ Boundary 
-    		    @@ binocular rivalry/CFS
-    		    @@ Libet's experiment
-    		    @@ Unconscious determinants of free decisions in the human brain    		    
-    		    @@ Priming
-    		    @@ Bistable perception
-    		    @@ Perceptual overflow
-    		    @@ Threshold of unconscious to consciousness
-    		    @@ Probabilistic information is always unconscious
-
-		    @ Unconscious 
-                @@ Reflection
-        			@@@ Reflexive systems is not informational closured.
-        			@@@ Base	d on our theory,
-        			@@@ x -> s -> a
-        			@@@@ the system state is determined by environmental state, then it is not conscious.
-        			@@@ Therefore, in general, a simple policy network is not conscious.
-
-    			@@ Blindsight
-
-	    			@ Passive neural activity
-
-		\end{ants}
-
-		\subsection{reflexive behaviours is unconscious (or environment-state dependent processes)}\label{sec:reflexive}
-		\subsubsection{Reflection}
-		\begin{ants}
-			@ Reflexive systems is not informational closured.
-			@ Base	d on our theory,
-			@ $P(A|S)$ action policy is conditional on the sensory input data.
-			@ x -> s -> a
-			@@ the system state is determined by environmental state, then it is not conscious.
-			@ Therefore, in general, a simple policy network is not conscious.
-		\end{ants}
-
-		\subsubsection{Blindsight}
-		\begin{ants}
-			@ This also blindsight.
-			@ Blindsight patients and still make above chance judgement without conscious awareness of visual targets.
-			@ The stimulus-reaction policy network still intact, but it cannot form informational closure and therefore, patients has no conscious awareness of visual  targets
-			@ Patient B.F. reactions are stimulus driven.
-		\end{ants}
-
-		\subsubsection{procedure memory}
+\rlends
 
 		\subsection{Conscious Processing}
-		So far, previous consciousness research has identified a set of perceptual and cognitive functions which not exclusively but frequently associate with consciousness.
-
-		\begin{ants}
-            @ response inhibition 
-            @ goal
-            @ planning            
-            @ conflict resolution
-            @ error detection         
-            @ task-switching
-            @ working memory
-            @ cognitive control 
-            @ overriding automatic responses
-            @ self-monitoring 
-            @ global availability 
-            @ integration             
-            @ stabilisation
-            @ information for off-line processing
-            @ flexible routing of information
-            @ integrates behaviour across time            
-            @ tasks for long duration
-            @ flexibility and the strategic use of that information for complex operations and decision-making 
-            @ flexible and adjust our behavior to different contexts and goals
-            @ complex visuomotor abilities
-            @ conscious thought, reflection, reasoning, and temporally extended sense of self. 
-            @ multiple alternative possibilities
-            @ simulate alternative realities 
-            @ imagination
-            @ dreaming 
-            @ anticipation
-            @ intending
-            @ replaying
-            @ interpreting
-            @ reflecting
-            @ reasoning
-            @ problem solving 
-            @ deciding            
-		\end{ants}
 
@@
 The reason why consciousness is accompanied with some specific cognitive function is because NTIC is a powerful property that brings creatures a lot of advantage in the evolution \cite{Seth2009Encyclopediaofconsciousness}.
+
+		\begin{ants}
+		    @ If both conditions are satisfied, information within the NTIC process becomes conscious. 
+		    @ Our theory suggests that conscious processing should be linked to cognitive functions that require forward models and predictive information \critical{Need to list items vary carefully here.}
+
+		    @ Previous research has identified a set of perceptual and cognitive functions which not exclusively but frequently associate with consciousness.
+
+    		    @@ Planning, achieving long term goals
+
+    		        @@@ simulate alternative realities 
+    		        @@@ multiple alternative possibilities
+    		        @@@ imagination
+    		        @@@ information for off-line processing
+
+    		    @@ Cognitive control, response inhibition, flexible routing of information, overriding automatic responses
+
+    		        @@@ flexibility and the strategic use of that information for complex operations and decision-making 
+    		        @@@ flexible and adjust our behavior to different contexts and goals
+
+    		    @@ integration,
+
+    		    @@ integrates behaviour across time
+
+    		        @@@ tasks for long duration
+
+    		    @@ stabilisation
+
+    		    @@ conscious thought, reflection, reasoning, and temporally extended sense of self.
+
+    		    @@ complex visuomotor abilities
+
+    		    @@ intending deciding
+
+    		    @@ dreaming
+
+    		    @@ reasoning interpreting
+
+    		    @@ self
+
+    		        @@@ reflecting
+    		        @@@ self-monitoring 
+            @ As mentioned in \ref{sec:Non-trivial informational closure}, achieving NTIC has a large evolutionary advantage.
+
+                @@ Because NTIC processes encode information about environmental transition, it becomes a perfect computational core for constructing forward models for the environment, simulating the dynamics of self-environment interaction, and generating predictions.
+
+            @ Therefore, if an agent equips a NTIC process, the process can be used to integrate information from different sources.
+
+		\end{ants}
 
@@
 
-            @
+            % about the coarse-graining function (aggregation function) 
+            @ \cite{PFANTE.2014}, the authors discuss the the implications of the types of aggregation function (deterministic or probabilistic) and its relationship with macroscopic processes.
+If the macroscopic process: \rewrite{Furthermore, we could prove that observational commutativity forces the aggregation to be deterministic if the upper process is invertible, i.e., ψ is invertible, and in the case of a soft (i.e., probabilistic) aggregation the third idea of commutativity really differs from the one of observational commutativity.
+}
 

### 2019-06-04 Chaper_Limitation.tex
Updates from Overleaf

--- 2019-05-06 Paper_neural_coarse_graining_of_consciousness.tex
@@
-\documentclass[utf8]{article}
-
-%% Language and font encoding
-\usepackage[english]{babel}
-%\usepackage[utf8]{inputenc}
-\usepackage[T1]{fontenc}
-
-%% Sets page size and margins
-%\usepackage[a4paper, top=3cm,bottom=2cm,left=3cm,right=3cm,marginparwidth=4cm]{geometry}
-\usepackage[papersize={10in, 12in}, top=3cm,bottom=2cm,left=2in,right=2in,marginparwidth=1.8in]{geometry}
-
-%% Title style
-\usepackage{stringstrings}
-\usepackage[explicit]{titlesec}
-\usepackage{sectsty}
-
-%% ============================== Useful packages ============================= %
-\usepackage[dvipsnames,table,xcdraw]{xcolor}
-\usepackage[round]{natbib}
-\usepackage{amsmath}
-\usepackage{graphicx}
-\usepackage{svg}
-\usepackage[colorlinks=true, allcolors=blue]{hyperref}
-\usepackage{authblk}
-\usepackage{float}
-\usepackage{tikz}
-
-%% ================================== acronym ================================= %
-\usepackage{acronym}
-\newacro{ntic}{non-trivial informational closure}
-\newacro{ic}{informational closure}
-\newacro{cg}{coarse-grain}
-\newacro{cging}{coarse-graining}
-\newacro{cged}{coarse-grained}
-\newacro{ncg}{neural coarse-graining}
-
-% The name of our theory
-% ----------------------------------------------------------------------------
-\newcommand{\tnamefull}{The Neural Coarse-graining Theory of Consciousness}
-\newcommand{\tname}{NCGT} 	% TheoryNameShort
-\newacro{\tname}{\tnamefull}
-%\newacro{NCGT}{the neural coarse-graining theory of consciousness}
-
-% =================================== Macro ================================== %
-\usepackage[colorinlistoftodos]{todonotes}
-\usepackage[at]{easylist}
-\usepackage{tcolorbox}
-\tcbuselibrary{skins}
-\usepackage{comment}
-\usepackage[framemethod=tikz]{mdframed}
-\usetikzlibrary{shadows}
-\usepackage{soul}
-\usepackage{version}
-
-% Meaning of colours --------------------------------------------------------- %
-%	Red: Important and Critical
-%	Orange: Todo
-%	Blue: Topic and Guideline
-%	Purple: Murmur
-%	Green: Question, Call for help, Open for opinions and comments
-%	Brown: Need Wording
-% ---------------------------------------------------------------------------- %
-
-% Real content
-	% Outline items that can be integrated into main text
-		\newenvironment{ants}
-			{
-			 \begin{easylist}[itemize]
-		 	}
-			{
-			\end{easylist}
-			} %
-
-	% Writing Materials
-    \newenvironment{WritingMaterials} %
-    	{
-            \begin{tcolorbox}[enhanced,
-                title=-,
-                size=small,
-                colbacktitle=Aquamarine,
-                drop fuzzy shadow,
-                fontupper=\small,
-                boxrule=0.4pt,
-                colback=Aquamarine!10!white,
-                sharp corners]
-                Writing Materials
-            \end{tcolorbox}
-            \begin{easylist}[itemize]
-    	}
-    	{
-            \end{easylist}  
-            \begin{tcolorbox}[enhanced,
-                halign=flush right,
-                halign title=right,
-                size=small,
-                colbacktitle=Aquamarine,
-                drop fuzzy shadow,
-                fontupper=\small,
-                boxrule=0.4pt,
-                colback=Aquamarine,
-                colupper=White,
-                sharp corners]
-                Writing Materials -
-            \end{tcolorbox}        
-    	}
-
-    % \excludeversion{WritingMaterials}
-
-% Functional content
-	% Quotes: green
-		\newcommand{\rewrite}[1]{\textcolor{ForestGreen}{\textit{"#1"}}\newline}
-
-	% todo: orange
-		% text todo
-		\newcommand{\toWrite}[1]{\noindent
-			\textcolor{Orange}{\textbf{[[ #1 ]]}}}
-
-	% figure todo
-        \newcommand{\includegraphicsTodo}[2][]{%
-            \tcbox[enhanced,
-                center,
-            	adjusted title=\large To Be Modified ...,
-            	halign title=center,
-            	attach boxed title to top left={yshift=-3mm, xshift=1cm,yshifttext=-1mm}, boxed title style={drop fuzzy shadow},
-            	colbacktitle=RedOrange!70!black,
-            	coltitle=white,
-            	colframe=RedOrange!50!black,
-            	colback=white
-        	]{\includegraphics[#1]{#2}}}
-
-		% figure todo callout
-        \newcommand{\needfig}[1]{%
-			\ifthenelse{\equal{#1}{}}{%
-				\todo[color=White, linecolor=Orange, bordercolor=RedOrange]{\textcolor{RedOrange}{Fig}}}{%
-				\todo[color=White, linecolor=Orange, bordercolor=RedOrange]{\textcolor{RedOrange}{Fig: #1}}%
-			}%
-		}
-
-		% rewording
-		\newcommand{\rewording}[1]{\textcolor{RawSienna}{[[ REWORDING | #1 ]]}}
-
-		% Need reference
-		\newcommand{\needref}[1]{%
-			\ifthenelse{\equal{#1}{}}{%
-				\todo[color=White, linecolor=Orange, bordercolor=Orange]{\textcolor{Orange}{Ref}}}{%
-				\todo[color=White, linecolor=Orange, bordercolor=Orange]{\textcolor{Orange}{Ref: #1}}%
-			}%
-		}
-
-	% Highlight: Yellow or Red
-		% Highlight only
-		\newcommand{\highlight}[2][Yellow!75!white]{\colorbox{#1}{#2}}
-
-		% Highlight and comment
-        \newcommand{\highlightAndComment}[3][Yellow]{\sethlcolor{#1}\hl{#2}\todo[color=#1, linecolor=Yellow]{#3}}
-
-		% Critical point
-		\newcommand{\critical}[1]{%
-			\todo[color=OrangeRed!80!white]{#1}
-		}
-
-	% idea: Purple
-		% text idea
-			\newcommand{\idea}[2][Plum]{\noindent
-				\textcolor{#1}{[[ #2 ]]}}
-
-		% box idea
-			\newcommand{\ideaBox}[1]{
-			    \vspace{2mm}
-				\begin{tcolorbox}[enhanced,%
-                    title=-,
-                    center,
-                    fontupper=\small,
-                    lifted shadow={1mm}{-2mm}{3mm}{0.1mm}{black!50!white},%
-                    boxrule=0.4pt,
-                    width=9cm,
-                    colback=Thistle!50!white,
-                    sharp corners]
-					#1
-				\end{tcolorbox}
-				\vspace{2mm}
-			}
-
-		% call-out idea
-			\newcommand{\ideaCallout}[1]{\todo[color=Thistle!50!white, size=\small]{#1}}
-
-	% communication: green
-		% call for help
-			\newcommand{\needhelp}[1]{\todo[color=SpringGreen]{[Need Help]: #1}}
-
-		% comment
-			% comment by authors
-			\newcommand{\addcomment}[3][\empty]{\todo[color=SkyBlue]{Comment [#2]:\newline#3}\colorbox{SkyBlue}{#1}}
-
-			% usage:
-			% \addcomment{auther}{comment text}
-			% or
-			% \addcomment[highlighted text]{auther}{comment text}
-			%
-			% e.g.
-			% It's a \addcomment[beautiful]{Acer}{need a reference} day
-
-    % backup: 
-    \newenvironment{backup}
-    {
-
-        \begin{tcolorbox}[enhanced,
-            title=-,
-            size=small,
-            colbacktitle=black!70!white,
-            colback=black!10!white,            
-            drop fuzzy shadow,
-            fontupper=\small,
-            boxrule=0.4pt,
-            sharp corners]
-            Backup
-        \end{tcolorbox}
-    }
-    {
-        \begin{tcolorbox}[enhanced,
-            halign=flush right,
-            halign title=right,
-            size=small,
-            colbacktitle=black!10!white,
-            colback=black!70!white,
-            drop fuzzy shadow,
-            fontupper=\small,
-            boxrule=0.4pt,
-            colupper=White,
-            sharp corners]
-            Backup -
-        \end{tcolorbox}    
-    }
-    % \excludeversion{backup}
-
-% review loop annotation
-    \usepackage[xcolor, outerbars]{changebar}
-    \cbcolor{red}
-
-    % start anchor: \rlstart
-    \newcommand{\rlstart}[1]{  %
-        \setlength\changebarwidth{#1pt*2}  %
-        \hspace*{-40pt}
-        \cbstart{\textcolor{red}{\newline\textbf{iteration #1}}\newline}}
-
-    % end anchor: \rlend
-    \newcommand{\rlend}{\cbend}
-
-% quote
-\newcommand{\myQuote}[1]{\textit{``#1''}}
-
-% ============================================================================ %
-%                                     Title                                    %
-% ============================================================================ %
-\title{A neural coarse graining theory of consciousness/\newline Non-trivial Informational closure through neural coarse-graining as the Fundamental Informational Correlates of Consciousness }
-
-% ============================================================================ %
-%                                    Authors                                   %
-% ============================================================================ %
-\author[1]{Acer Y.C. Chang\thanks{acercyc@araya.org}}
-\author[1]{Martin Biehl\thanks{martin@araya.org}}
-\author[1]{Yen Yu\thanks{martin@araya.org}}
-\author[1]{Ryota Kanai\thanks{kanair@araya.org }}
-\affil[1]{ARAYA, Inc., Tokyo, Japan}
-
-% ============================================================================ %
-%                                     Body                                     %
-% ============================================================================ %
-\begin{document}
-	\maketitle
-	\tableofcontents
-
-	\begin{abstract}
-		Neural systems process information through different levels of organisation in a hierarchical manner.
-Information at lower levels is finer-grained and can be coarse-grained for higher level computation.
-However, one is aware of information processed only at specific levels.
-Theorists have addressed this issue.
-For example, the intermediate level theory of consciousness suggests that the intermediate level seems to be privileged with respect to consciousness.
-It is true that we do not experience information processed by individual neurons which is always highly noisy.
-Besides, we have no conscious experience from interpersonal activities albeit massive interactions among individuals.
-Instead, neurophysiological evidence has been showing that conscious experience tends to co-vary with information encoded in coarse-grained neural states such as neural population codes.
-We argue that the neural states within the scope of the informational closure determine the contents of consciousness and brain processes outside apart from the representations of that level remain unconscious.
-This argument suggests a distinction between conscious and unconscious processing and provides a generic computational framework.
-Finally, using the deep learning network, we can measure informational closure in deep hidden layers.
-Our preliminary results show that informational closure representation emerged after learning.
-We further decoded the information from the representation and compared it with human conscious perception.
-	\end{abstract}
-
-	\section*{Keywords:}
-	Keywords: theory of Consciousness, informational closure, neural coarse-graining, level of analysis
-
-    \newpage
-    \section*{Not decided terminology}
-        \begin{ants}
-            @ information * in the NTIC process
-            @ Full and short name of this theory
-            @ core "?" (entity) for conscious content 
-            @ our theory? framework? proposal? 
-            @ system? process?
-            @ variable? node? element? member?
-        \end{ants}
-
-	% ============================================================================ %
-	%                                     Start                                    %
-	% ============================================================================ %
-
-    \newpage
-	\section{Introduction}
-
-		%% Story about a cell
-		Imagine you are a neuron in Alice's brain.
-Your daily work is to collect neurotransmitters through dendrites from other neurons, accumulate membrane potential, and finally send signals to other neurons through action potentials along axons.
-However, you have no idea that you are one of neurons in Alice's supplementary motor area and involved in many motor control processes for Alice's action, for example, grabbing a cup.
-You are ignorant of intentions, goals, and motor plans that Alice has at every moment even though you are part of the physiological substrate responsible for all those actions.
-		A similar story also applies to Alice's conscious mind.
-To grab a cup, for example, Alice is conscious of her intention and visuosensory experience of this action.
-However, her conscious experience does not show the dynamic of your membrane potential and about action potentials you send to other neurons every second.
-That is, information in Alice's conscious experience does not contain information involved in your information processing.
-
-		\toWrite{maybe need a transition sentence here}
-
-		%% scale
-		It seems to be true that we are unable to consciously access information processed at every scale in the neural system.
-Only information at certain levels of coarse-graining can become conscious contents.
-At microscopic levels of neural systems, information processing in individual neurons is highly noisy and state transitions of neurons are extremely stochastic \citep{Goldwyn2011, White2000}.
-However, instead of stochastic action potentials and fluctuation of random noise at microscopic levels, what we are aware of in our conscious mind shows astonishing stability and robustness against the ubiquitous noise in the neural system \citep{mathis1995computational}.
-Likewise, conscious experience does not associate with states of the whole brain level because we have known that some parts of the neural system contribute very little to conscious experience (the cerebellum for example \citep{lemon2010life}).
-Additionally, we do not  experience "super-consciousness" when we have massive inter-individual interactions with other human-beings.
-Even though evidence has shown several types of collective information processing at human social groups levels exist \citep{malone2015handbook}, information processed at this level seems to depart from our individual conscious contents.
-
-		%% our argument
-		In this article, we propose a new theory of consciousness, called\ac{\tname}.
-This proposal states that consciousness does not rest on particular neural architectures or locations in the neural systems.
-Instead, we argue that consciousness correlates with information processing at a certain coarse-grained level where the neural systems create a high degree of non-trivial informational closure (NTIC).
-We further postulate that the \textit{level} of consciousness corresponds to the degree of NTIC and the \textit{contents} of consciousness corresponds to the state of the NTIC process (for the level versus content of consciousness see \cite{laureys2005neural, overgaard2010neural}).
-
-		% information-based claim 
-		Our theory takes a strong assumption that consciousness is information-based, information correlates of consciousness (ICC)\todo{Complete this argument}
-
-		%% About this paper
-		Our theory rests on two core concepts: non-trivial informational closure and neural coarse- graining.
-In this article, we first introduce non-trivial informational closure and its importance to information processing for human scale agents.
-We next argue that through coarse-graining the human neural system can achieve non-trivial informational closure at a specific coarse-grained level.
-We then propose that the state of the informational closure correlates with the state of consciousness for both levels and contents which can be explained, quantified, and predicted computationally by this theory.
-We also address how this theory can concisely explain empirical results from previous studies and reconcile several current major theories of consciousness.
-Finally, we provide predictions and testable approaches for this theory.
-
-		% TODO: is figure needed?
-		\idea{Do I need a figure?, Something like this one?}
-		\begin{figure}[H]
-			\includegraphicsTodo[width=\textwidth/2]{WritingMaterials/PDFXCview_2018-06-11_13-37-34.png}
-			\cite{pennartz2017consciousness}
-			\caption{xxxx}
-	   	\end{figure}
-
-		%% backup point
-		\begin{comment}
-			@ consciousness is information
-
-			@ conscious contents
-				@@ \toWrite{lower level}
-				@@ Information processing of individual neurons are noisy.
-				@@ We don't have conscious content changes when individual neurons fire action potentials.
-				@@ Don't even mention ion channel dynamic.
-
-				@@ \toWrite{Higher-level dynamic}
-
-			@ For human, physics at our body scale are nearly follow classic physics, which is deterministic.
-
-			@ \toWrite{Human tendency for active prediction }
-				@@ \cite{Stahl2015} \rewrite{
-					Given the overwhelming quantity of information available from the environment, how do young learners know what to learn about and what to ignore?
-We found that 11-month-old infants (N = 110) used violations of prior expectations as special opportunities for learning.
-The infants were shown events that violated expectations about object behavior or events that were nearly identical but did not violate expectations.
-The sight of an object that violated expectations enhanced learning and promoted information-seeking behaviors; specifically, infants learned more effectively about objects that committed violations, explored those objects more, and engaged in hypothesis-testing behaviors that reflected the particular kind of violation seen.
-Thus, early in life, expectancy violations offer a wedge into the problem of what to learn.}
-
-			@ Intuitive physics \needref{Intuitive physics}
-
-		\end{comment}
-
-	\section{Non-trivial informational closure}
-		\ideaBox{I am still not sure we should go for NTIC without describe my intuition about consciousness and closure?
-Or we should start with my intuition.
-Or we should postpone to explain the intuition in Chapter 4?}
-
-		The notion of non-trivial informational closure (NTIC) is introduced by \cite{BERTSCHINGER.2006}.
-The concept of closure is closely related to system identification in systems theory.
-One can define a system from its environment by computing the closureness of the system \citep{maturana1991autopoiesis, rosen1991life, pattee2012evolving, luhmann1995probleme}.
-The closureness can be further quantified by information theory.
-
-		\begin{WritingMaterials}
-			@ Consciousness as an intrinsic information. Therefore, information should be self-define. This means the boundary of conscious content should be related to informational closure.
-
-			@ \idea{should we describe the intuition of boundary problem here?}
-
-			@ ============================================================================
-
-			@ \rewrite{
-				The notion of closure plays a prominent role in systems theory where it is used to identify or define the system in distinction from its environment} \cite{BERTSCHINGER.2006}
-
-			@ \rewrite{
-				Our theoretical interest concerns the type of system that is a unity for and by itself and not only for an external observer distinguishing some entity from the rest of the world.
-This requires a system that can be described as a whole without reference to its environment.
-In systems theory, this property is usually referred to as closure.}\citep{BERTSCHINGER.2006}
-
-			@ \rewrite{
-				These concepts of closure play an important role in the architecture of systems
-				theory, because they are used to
-				1. define the system (in distinction to its environment) and to
-				2. explain the autonomy of the system.}\citep{BERTSCHINGER.2006}
-
-			@ \rewrite{
-				Informational closure: The higher process is informationally closed, i.e., there is no information flow from the lower to the higher level.
-Knowledge of the microstate will not improve predictions of the macrostate.} \citep[p.
-4]{PFANTE.2014}
-
-		\end{WritingMaterials}
-
-		% Definition of informational closure
-			\noindent
-			Information flow $J_{t}$ from the environment $E$ to a system $Y$ at time $t$ can be defined as the conditional mutual information $I$ between the system future state $Y_{t+1}$ and the current environment current state $E_{t}$ given the current system state $Y_{t}$
-
-				\begin{equation}\label{eq:InformationFlow}
-				\left.\begin{array}
-				{rl}{J_{t}(E \rightarrow Y )} & {:= I(Y_{t+1};E_{t}|Y_{t})} \\
-				%{ } & { \ = H(Y_{t+1}|Y_{t})-H(Y_{t+1}|Y_{t},E_{t})} \\
-				%{ } & { \ = H(E_{t}|Y_{t})-H(Y_{t}|Y_{t},Y_{t+1})} \\
-				%{ } & { \ = H(E_{t}|Y_{t})-H(E_{t}|Y_{t},Y_{t+1})}\\
-				{ } & { \ = I(Y_{t+1};E_{t}) - (I(Y_{t+1};Y_{t})-I(Y_{t+1};Y_{t}|E_{t}))}
-				\end{array}\right.
-				\end{equation}
-
-				\begin{figure}
-					\includegraphics[width=\textwidth]{WritingMaterials/SystemAndEnv.pdf}
-					\caption{Figure adapted from \cite{BERTSCHINGER.2006}}
-					\label{fig:SystemAndEnv}
-				\end{figure}
-
-			\noindent
-			\cite{BERTSCHINGER.2006} defines that a system is informational closured when information flow from the environment to the system is close to zero.
-
-				\begin{equation}
-				J_{t}(E \rightarrow Y )=0
-				\end{equation}
-
-			% ------------------------------- trivial case ------------------------------- %
-			\noindent
-			Achieving information closure (minimising $J_t$) could be trivial, which means the environment and the system are entirely independent of each other.
-
-				\begin{equation}
-				\begin{aligned}
-				{I(Y_{t+1};E_{t})=0}&&{\Rightarrow}&&{J_{t}(E \rightarrow Y )=0}
-				\end{aligned}
-				\end{equation}
-
-			% -------------------------------- non-trivial ------------------------------- %
-			\noindent
-			However, informational closure can be achieved non-trivially.
-In the non-trivial case, the system trying to encode information about the environmental dynamics can also be informational closured.
-This means
-
-				\begin{equation}
-				I(Y_{t+1};E_{t}) > 0
-				\end{equation}
-
-			\noindent
-			This also implies
-				\begin{equation}
-					I(Y_{t+1};Y_{t})-I(Y_{t+1};Y_{t}|E_{t}) > 0
-				\end{equation}
-
-			\noindent
-			And, non-trivial informational closure can be defined as
-				\begin{equation}
-				\left.\begin{array}
-				{rl}{NTIC} & {:=I(Y_{t+1};Y_{t})-I(Y_{t+1};Y_{t}|E_{t})}\\
-				{ } & {\ =I(Y_{t+1};E_{t})-I(Y_{t+1};E_{t}|Y_{t})}
-				\end{array} \right.
-				\end{equation}
-
-			\noindent
-			And, Maximising NTIC is equivalent to
-				\begin{equation}\label{eq:nticObjective}
-				\begin{aligned}
-				& \text{maximise} & { } & I(Y_{t+1};Y_{t}) & { } & \text{and} \\
-				& \text{minimise} & { } & I(Y_{t+1};Y_{t}|E_{t}) & { }
-				\end{aligned}
-				\end{equation}
-
-			\noindent
-			This implies the system contains in itself the information of its own future and the self-predictive information is gained from the information about the environment.
-Therefore, to achieve NTIC, the system can internalizes and synchronises the dynamics of the environment, i.e.
-modelling the environment.
-Furthermore, having high degrees of NTIC entails having high predictive power about the environment.
-This gives biological agents a great functional and evolutional advantage to achieve NTIC in their information processing systems.
-Practically, \cite{guttenberg2016neural} proposed that NTIC can be achieved by maximising the predictive power about the environment and the self-predictive information of the system concurrently.
-
-			% Biological evidence of informational closure in the neural system
-			Though the significant advantage for biological systems to achieve NTIC, to our knowledge, studies directly examining NTIC in biological systems are limited.
-However,  recent studies have showed relevant properties in the visual system of salamanders.
-By examining the salamander retina, in two studies \citep{Palmer2015, sederberg2018learning} the authors found that the a large groups of neural populations of retinal ganglion cells encoded predictive information about external stimuli also had high self-predictive information about their own future states (see Figure~\ref{fig:sederberg2018learning}), therefore, in line with the characteristic of NTIC.
-Therefore, the self-predictive information of the neural populations can guides prediction about external stimuli without reference to stimulus parameters explicitly.
-Moreover, the internal predictability can be generalised to different stimulus classes suggesting the tendency to internalise the information of environmental dynamics in the neural populations.
-\toWrite{Add Some ending sentences}
-
-			\begin{figure}[H]
-				\includegraphicsTodo[width=\textwidth]{WritingMaterials/Palmer2015.png}
-				\caption{Figure adapted from \cite{sederberg2018learning}}
-				\label{fig:sederberg2018learning}
-			\end{figure}
-
-			\begin{comment}
-				@ ===
-
-				@ \rewrite{
-					Internal information reflects the spatial and temporal correlations in the stimulus.}
-
-				@ \rewrite{predictive information is encoded synergistically.}
-
-				@ \rewrite{
-					in recordings of populations of RGCs of salamander retina driven by a simple stimulus with partially predictable dynamics, joint activity patterns transmit information that is predictive of future stimuli }
-
-				@ \rewrite{
-					We examined whether the temporal correlations within populations of RGCs can be used to guide the search for readouts of predictive information.}
-
-				@ \rewrite{
-					We showed that groups of cells with high external, stimulus-predictive information also had high internal predictive information on two classes of stimuli, }
-
-				@ \rewrite{
-					Very simple learning rules could find near-optimal readouts of predictive information without any external instructive signal.
-This suggests that bottom-up prediction may play an important role in sensory processing}
-
-				@ \rewrite{
-					Internal predictive information can guide stimulus prediction without explicit reference to stimulus parameters.}
-
-				@ \rewrite{
-					Word–word internal predictive information is correlated with word–stimulus predictive information across sets of four cells.}
-
-				@ They also showed generalization of internal predictability across stimulus. This suggests .... what?
-
-				@ \rewrite{
-					The generalization of internal predictability across stimulus classes partially reflects the ability of the retina to adapt to the statistics of stimuli}
-
-				@ \cite{Palmer2015}
-				@ \rewrite{
-					Groups of cells in the retina carry information about the future state of their own activity, and we show that this information can be compressed further and encoded by downstream predictor neurons that exhibit feature selectivity that would support predictive computations.}
-
-				@ \rewrite{
-					It seems natural to phrase the problem of prediction in relation to the visual stimulus, as in Fig.
-3, but the brain has no direct access to visual stimuli except that provided by the retina.
-Could the brain learn, in an unsupervised fashion, to predict the future of retinal outputs?
-More precisely, if we observe that a population of retinal ganglion cells generates the word w t at time t, what can we say about the word that will be generated at time t + delta t in the future?
-The answer to this question is contained in the conditional distribution of one word on the other, P ð w t +delta t j w t Þ } \url{http://tinyurl.com/y9zmhlln}
-
-				@ \rewrite{
-					larger groups of cells carry predictive information for hundreds of milliseconds, }
-
-			\end{comment}
-
-			%% backup
-			\begin{comment}
-				@ Accurately model deterministic environment
-				@ \rewrite{
-					This demonstrates that a system exhibiting certain internal regularities as measured by $A^* = MI(Sn+1; Sn)$ can achieve informational closure either by gaining information about the environment or by increased autonomy, i.e.
-by becoming unpredictable or uncontrollable from the (13) environment.
-Therefore, information about the environment, i.e.
-modeling, and autonomy can be considered as complementary strategies for achieving informational closure.}
-
-				@ By Action
-
-				@ In the next section, we claim that the neural system achieve NTIC through coarse-graining.
-			\end{comment}
-
-		\subsection{Informational closure and level identification}
-
-		\subsection{Biological Creature may try to achieve closure even the environment is not}
-
-	\section{Neural coarse-graining}
-
-		%% stochasticity at microscopic levels
-		Nevertheless, to achieve information closure (so as NTIC) in highly stochastic systems (e.g., the neural system) is challenging.
-The current states of the system have low predictability of its future states due to the stochasticity.
-Information processing in the neural system is suffered from multiple noise sources throughout, including sensory, cellular, electrical, and synaptic noises.
-Previous studies have shown that states of neurons have large trial-to-trial variability at the cellular level.
-That is, the same pattern of activity never occurs twice even when the same stimulus is presented.
-Neurons are inevitably subject to thermal fluctuations and other physical noises \citep{faisal2008noise}.
-Furthermore, environmental information is always only partial observable to individual sensors and neurons which only receive little amount of information from the environment.
-Therefore, self and environmental predictive information is difficult to be represented at the cellular level.
-It is implausible to construct NTIC processes at microscopic levels.
-
-        %% Our argument
-		However, we argue that, by coarse-graining microscopic neural states, the neural system is able to achieve NTIC at certain coarse-grained macroscopic levels.
-To encode information in coarse-grained variables is a way to encode stable and robust information in neural system and overcome the difficulties to achieve NTIC at microscopic levels.
-Coarse-graining in this paper is referred to many-to-one functions that map microscopic states to macroscopic states.\needref{Do we need reference?}.
-In other words, a number of different micro-states realise the same value of the macro-variable \citep{price2007causation}.
-This is a common strategy that we can see in large number of previous neurophysiological studies.
-For example, in the temporal domain, neural spikes across time can be coarse-grained as spiking rate variables, known as rate coding \citep{adrian1926impulses, gerstner2002spiking, maass2001pulsed, panzeri2015neural, stein2005neuronal}.
-Neurons encode stimulus intensity by increasing or decreasing firing rate.
-\citep{kandel2000principles}.
-In this coding scheme, individual neural spikes in a transient time span is not meaningful and stochastic \citep{stein2005neuronal}.
-In contrast, rate codes are relative stable and are highly robust against noise causing variation of inter-spike intervals.
-
-		% population code
-		Another example of coding strategy using coarse-graining is population coding.
-In this coding scheme, information is represented by joint spatiotemporal activities of several neurons.
-Therefore, the information is encoded in coarse-grained variables whose values are jointly determined by neural activation patterns within a neural population \citep{kristan1997population, pouget2000information, binder2009encyclopedia, QuianQuiroga2009}.
-In such case, activities of every single neuron is not informative and stochastic.
-Instead, coarse-grained variables (such as population averaging and population vector) are able to represent information stably.
-Encoding information at coarse-grained levels allow the neural system ignores certain causal interactions relevant to fine-grained level of description \citep{Woodward2007-WOOCWA}.
-
-		% neural coarse-graining by Nic
-		It has been empirically implemented that NTIC can be achieved by coarse-graining snesory inputs in artificial neural networks.
-\citep{guttenberg2016neural} proposed a "neural coarse-graining (NCG)" architecture (fig.\ref{fig:NCG}) which aims to captures the emergent large-scale dynamics in the environment.
-The NCG network learns to coarse-grain input signals and extract latent parameters which are both predictive and predictable in the input signal and therefore achieves NTIC by building a higher-level representation of the underlying dynamics in the deep layers.
-More importantly, using this architecture, agents can process information and act at coarse-grained macroscopic levels.
-
-		\begin{figure}
-			\includegraphicsTodo[width=0.8\textwidth]{WritingMaterials/PDFXCview_2018-06-08_14-24-03.png}
-			\caption{NCG \idea{I need to simplify this figure}\citep{guttenberg2016neural}}
-			\label{fig:NCG}
-		\end{figure}
-
-		%% not monotonic
-		It is important to note that NTIC should not be a monotonic function of scale of coarse-graining.
-Overly coarse-graining system states can lead to low degrees of NTIC.
-For example, in an extreme scenario, when all microscopic states map to a single macroscopic variable, the macroscopic level does not have enough information capacity and thus losses  the self and environmental predictive power.
-This notion is also supported by empirical evidence.
-\cite{sederberg2018learning} showed that the efficiency of reading out  self-predictive information of neural population is higher when cell number in populations is 4 than 7 and 10-cell sets.
-This implies an optimal coarse-graining scale for NTIC processes.
-% Perhaps the best way to combine more than four cells is to break down the readout into indivisible units of four cells, which are later recombined in subsequent processing.}\citep{sederberg2018learning}
-
-        %% Link to consciousness
-
-        At the physical scale which human being live in, the environmental dynamics is nearly deterministic following the laws of classical physics.
-It gives agents living at this physical scale great advantages if the agents can build NTIC process internally.
-Therefore, to coarse-grain microscopic states is necessary
-
-        %This means that it is possible for agents to live at this physical scale to build NTIC process internally.
-        % More importantly, the information processing related to consciousness should not be situated at this level. Otherwise our conscious percept should be very noisy and unstable.
-
-		\begin{WritingMaterials}
-			@ \rewrite{
-				Coarse-graining: a method of reducing the complexity of a system by treating groups of atoms/molecules as single quasi-particles CG: coarse-grained}
-
-			@ neural system use population coding and temporal coding to fight against noise.
-
-			@ Therefore, even though the low level information processing is noisy, it is possible that the neural system achieve NTIC at a coarse-grained level.
-
-			@ This implies that the information about the environmental dynamic should be represented at a certain coarse-grained level rather then other levels.
-
-			%% Macroscale Deterministic
-			@ The environment that human scale agents interact with is approximately govern by Newton's law and therefore the state transitions are nearly deterministic.\needhelp{Is there any good ref I can cite?}
-
-			@ \idea{Need something here}
-
-			%% coarse-graining is necessary
-			@ Hence, to coarse-grain states of microscopic levels is necessary to represent and model the human-scale environment state and dynamics.
-
-			@ Coarse-graining is necessary to resist noise
-
-			@ \rewrite{ The population will therefore be relatively insensitive to the loss of
-				cells or noise in a small number of cells} \cite{eurich2000multidimensional}
-
-		\end{WritingMaterials}
-
-		\begin{WritingMaterials}
-
-			@ Studies have shown that coarse-graining is a common way that the neural system cope with inevitable noise at microscopic levels.
-
-			@ \rewrite{Because the sequence of action potentials generated by a given stimulus varies from trial to trial, neuronal responses are typically treated statistically or probabilistically}
-
-			@ Note that, information processing related to consciousness should not be situated at this level. Otherwise our conscious percept should be very noisy and unstable.
-
-		\end{WritingMaterials}
-
-			\begin{WritingMaterials}
-				@ Population coding
-
-					@@ review ref
-
-						@@@ \cite{Stanley2013}
-
-						@@@ \cite{QuianQuiroga2009}
-
-					@@ \rewrite{
-						Averaging is used in many neural systems in which information is encoded as patterns of activity across a population of neurons that all subserve a similar function (for example, see REFs 140,141 )}
-										140.
-Georgopoulos, A., Schwartz, A.
-\& Kettner, R.
-Neuronal population coding of movement direction.
-Science 233, 1416–1419 (1986).
-141.
-Lee, C., Rohrer, W.
-H.
-\& Sparks, D.
-L.
-Population coding of saccadic eye movements by neurons in the superior colliculus.
-Nature 332, 357–360 (1988).
-
-					@@ \rewrite{
-						Electrophysiological studies in the monkey have shown that behaviourally relevant signals are averaged not only across neuronal populations but also over time in the formation of a behavioural decision 156 .} 156.
-Gold, J.
-I.
-\& Shadlen, M.
-N.
-Representation of a perceptual decision in developing oculomotor commands.
-Nature 404, 390–394 (2000).
-
-					@@ \rewrite{A distributed representation of information of this type is more robust to the effects of noise.}
-
-					@@ \rewrite{
-						Neural population code: the set of response features of a population of neurons that carry all information about the considered stimuli.
-These features consist of spatio-temporal sequences of action potentials distributed across neurons and/or time.}
-
-					@@ The diverse response selectivity of sensory neurons
-
-					@@ \rewrite{
-						How a neural population represents information is partly determined by the diverse selectivity of individual neurons \cite{Shamir2014}}
-
-				@ sensory hierarchy
-					@@ sensory hierarchy also shows characteristic of coarse-graining
-
-					@@ Due to partial information that sensors can receive
-
-					@@ To form complex representation like shape, objects, coarse-graining is necessary.
-
-					@@ Through coarse-graining, \highlightAndComment{higher level}{might be confusing, need to think about the terminology here} cortical areas can integrate those partial information to infer hidden causes.
-
-			\end{WritingMaterials}
-
-			\begin{WritingMaterials}
-				@ Achieving NTIC is the key objective to to extract out latent control parameters in the environment.
-
-				@ Through two objectives during training, the model can achieve NTIC.
-
-				@ this can be achieved by maximising the self-predictive power of deep layers and its entropy through all training data.
-
-				@ With the objectives, NCG network learns to coarse-grain input signals and  extract latent parameters which are both predictive and predictable in the input signal and therefore achieves NTIC by building a higher-level representation of the underlying dynamics in the deep layers.
-
-				@ Agents can process information and act at abstract levels
-			\end{WritingMaterials}
-
-			\begin{WritingMaterials}
-				@ At the physical scale which human being live, the environmental dynamics is nearly deterministic following the laws of classical physics.
-This means that it is possible for agents living at this physical scale to build NTIC process internally.
-
-				@ When the information in individual sensory channel is noisy and partial, coarse-graining becomes necessary for achieve NTIC.
-			\end{WritingMaterials}
-
-	\section{A neural coarse graining theory of consciousness}
-
-\rlstart{5}
-
-        In this section, we propose a new theoretical framework of consciousness \{\tnamefull\} \todo{We need a good name}.
-This framework proposes that NTIC is the fundamental properties for information processing to be conscious.
-Additionally, coarse-graining is necessary to achieve NTIC in various of different systems.
-
-        We starts our argument from the first presumptive fact that every human conscious precept is highly informative.
-Our conscious experience always consists of high multidimensional information and usually involves information from multiple modalities.
-The notion of information referred to in this article is considered as resolved uncertainty.
-Being a certain conscious state rules out other enormous possible conscious experience in the state space of conscious experience.
-Therefore, every conscious percept resolves a huge amount of uncertainty and provides considerable information.
-
-        This notion is in agreement with one of the axiom, \textit{information}, in Integrated Information Theory (IIT 3.0) which claims that \myQuote{...an experience of pure darkness is what it is by differing, in its particular way, from an immense number of other possible experiences...} \citep[p.
-2]{oizumi2014phenomenology}.
-
-        Based on this presumptive fact, we postulate that the amount of information possessed of a conscious percept should be equivalent to information involved in a particular event or entity in the physical reality.
-Strictly speaking, we recognise information is a common language between conscious experience and the physical reality.
-We further take a radical standpoint and postulate that consciousness is fundamentally associated with information, i.e.
-information correlates of consciousness (ICC), \cite{chalmers1996conscious, tononi2004information, gamez2011information, Gamez2016}) and discard the notion of neural correlates of consciousness(NCC).
-
-        Next, we next consider the second presumptive fact that the information in consciousness is bound.
-Even though information involved in every conscious percept is extremely rich, it is still limited and we do not consciously feel everything in this universe.
-This leads to the boundary problems of consciousness \cite{goff2006experiences}.
-There should exist information boundaries for every conscious entity.
-Presuming consciousness is information-based phenomenon, we can identify the boundaries with measures from information theory.
-Particularly, in this case, boundaries can be defined by information closure.
-Therefore, information closure should be observed in conscious entities in the physical reality.
-
-        \rewording{informational closure also suggests that there is no information flow from the lower to the higher level.
-Knowledge of the microscopic levels will not improve predictions of the future states of the macroscopic levels \citep{PFANTE.2014}}.
-        Information closure also implies that the system is ignorant of information outside of the system.
-Therefore, if a coarse-grained level achieves information closure, it suggests the NTIC process at the coarse-grained level is ignorant of information processing happening at microscopic levels and also higher coarse-grained levels.
-This virtually makes the informational closed macroscopic levels as a complete reality.
-        \todo{Due to my concern mentioned last week, I think I should also mention the closure is not only to the environment but also to the microscopic levels}
-
-        Finally, our conscious experience always reflects some degree of information about environment and bodily states, i.e.
-non-trivial information.
-To account for the information-based considerations, we propose that NTIC is a fundamental informational property associated with consciousness.
-
-        \begin{WritingMaterials}
-        For example, considering two physical systems (Alice and Bob) and there is no interaction (or information passing) in between.
-Assuming that Alice is conscious, the conscious experience that Alice has should not involve any information about Bob.
-
-        \todo{Considering putting this para}
-        Similarly, we can apply this scenario to brain processing between two regions. We can consider a thought experiment. 
-        Imagining that in the future, one poor subject attend this experiment.
-We remove the subject's visual cortex from other brain areas.
-However, we keep all the connection between the two parts of the brain intact by replacing dendrites and axons between the two parts with micro electronic cables.
-Because these cables are very long, we can move the visual cortex to the surface of Mars.
-Now the experimenters give visual cortex a input signal.
-If the signal travels with the speed of light, it still takes three seconds to reach the other part on the earth.
-We can ask: Between the experimenters send the input signal and the information reach the part on the earth, what visual conscious content does the subject experience in the three seconds?
-We presume that in this three seconds subject's conscious experience should not contain any information about the visual input.
-Otherwise, the subject may be able to use the information to perform subsequent actions.
-This violates physics.
-This may look like a trivial questions.
-
-        However, in many systems, it is difficult to achieve NTIC at microscopic levels due to stochasticity.
-Through coarse-graining, NTIC processes become possible at macroscopic levels.
-Therefore, coarse-graining is necessary for many biological systems to implement NTIC processes, especially for the neural system (Fig.
-\ref{fig:LevelOfConsciousness}).
-In the following, we explained this framework and provide mathematical definitions and implications of ICC.
-        \end{WritingMaterials}
-
-		\begin{WritingMaterials}
-
-        @ As we mentioned in Chapter 3, to form non-trivial informational closure has a huge evolutionary advantage for the creatures interacting with the environment at our scale.
-
-        @ The physical environment dynamic at the human scale are nearly deterministic.\needref{Do we need ref here?}
-
-		@ To maximise fitness for individual human-being, neural system should try hard to infer and model the deterministic physical rules.
-
-		@ This drives the neural system to create a non-trivial informational closure.
-
-        @ Therefore, NTIC emerges from evolutionary processes is functionally plausible.
-
-        @ Importantly, at the microscopic level, it is impossible to achieve NTIC as we mentioned in chapter 2.
-
-		@ However, at a macroscopic scale, information processing can achieve non-trivial informational closure (Fig. \ref{fig:LevelOfConsciousness})
-
-        @ Therefore, the NTIC correlating conscious experience must settled at coarse-grained macroscopic levels.
-
-		@ Through coarse-graining, we can define a new set of variables.
-
-        @ information is scale-dependent
-
-		@ If the new set of variables are informational closure, then this creates a new \textit{reality} for all the variables inside.        
-		@ \textit{Reality} here means that the all the future states of the system are driven by the current information (include variables and the relationships) within the boundary.
-
-        @
-
-        @ Relationship between coarse-graining, scale and interaction with environment
-
-		@ \rewrite{
-			This illustrates how coarse-graining allows the formulation of incomplete generalizations that are relatively invariant, although at the cost of predictive precision regarding fine-grained details.} \cite{price2007causation}
-
-			@@ conscious perception are very stable and time invariant.
-			@@ Conscious perception is informative but we loss all the precise information about the states at microscopic level.
-
-        @ To summaries, in our framework, consciousness is 
-			    @@ Intrinsic
-
-			    @@ Informative
-
-				@@ scale-dependent
-
-        % our claim   
-			@ We claim that the state of a coarse-grained scale which realises non-trivial informational closured correlates the state of consciousness.
-
-			@ We further postulate that level of consciousness corresponds to informational closureness of processes.
-
-			@ The contents of consciousness correspond to the states of the non-trivial informational closure.
-
-		% Following
-			@ In the following part, we....\todo{todo}
-
-			@ This is the same as "if a tree falls in a forest" thought experiment.
-
-			@ Therefore, to understand this system, you don't need more information from external environment.
-
-			@ It also means everything in this system is self-defined.
-
-			@ \critical{I need to somehow acknowledge \cite{pennartz2017consciousness}}
-				@@ \rewrite{ In conclusion, for a well-behaved representational system, it does not matter whether a neural activation pattern represents an external world feature truthfully or not, as long as the system represents the feature consistently over time and in sensory space.}
-
-				@@ pennartz levels are defined by functional elements call "functional ensembles".
-\cite{pennartz2017consciousness} \rewrite{This delineation is different from a scale-based distinction of levels, because different levels are distinguished here based on function , i.e., what each level can accomplish in terms of computation and representation, culminating in perception at the highest level.}
-
-			@ \rewrite{
-				Multilevel views on consciousness and cognition have been expressed before by many other theorists, such as Oppenheim and Putnam (1958), Attneave (1961), Hofstadter (1979, 1985), Churchland and Sejnowski (1992), Wimsatt (1994), and Lycan (1996).} \cite{pennartz2017consciousness}
-
-				@@ Oppenheim , P.
-, \& Putnam , H.
-( 1958 ).
-Unity of science as a working hypothesis .
-In H.
-Feigl , G.
-Maxwell , \& M.
-Scriven (Eds.), Concepts, theories, and the mind – body problem (pp.
-3 – 36 ).
-Minneapolis : University of Minnesota Press .
-				@@ Attneave , F. ( 1961 ). In defense of homunculi . In W. A. Rosenblith (Ed.), Sensory communication (pp. 777 – 782 ). Cambridge, MA : MIT Press .
-				@@ Hofstadter , D. R. ( 1979 ). Godel, Escher, Bach, an eternal golden braid . New York : Basic Books .
-				@@ Churchland , P. S. , \& Sejnowski , T. J. ( 1992 ). The computational brain . Cambridge, MA : MIT Press .
-				@@ Wimsatt , W. C. ( 1994 ). The ontology of complex systems: levels of organization, perspectives, and causal thickets. Canadian Journal of Philosophy , 20 , 207 – 274 .
-				@@ Lycan ,  W. G.  ( 1996 ).  Consciousness and experience .  Cambridge, MA :  MIT Press
-			@ It's important that not the neural states but the coarse-grained state determine contents of consciousness.
-
-		\end{WritingMaterials}
-
-\rlend
-
-\rlstart{3}
-		\subsection{Measure of consciousness/information correlate of consciousness}	
-		Based on our core assumption that NTIC is the core informational entity correlating conscious experience, we propose conscious levels and contents can be derived by computes the properties of a NTIC process.
-\newline
-
-		\noindent
-		We first hypothesise that, at given time $t$, levels of consciousness $C_{t}^{Level}$ corresponds to the degree of  $NTIC_{t}$ at a coarse-grained level.
-			\begin{equation}\label{eq:cLevel}
-				C_{t}^{Level} = NTIC_{t}
-			\end{equation}
-		\newline
-		\noindent
-		We second hypothesise that, the content of consciousness corresponds to the state of the NTIC process.
-			\begin{equation}\label{eq:cContent}
-				C_{t}^{Content} = Y_{t}
-			\end{equation}
-
-		We discuss the implications of the two hypotheses in the following. 	
-	    \subsection{Level of Consciousness correlates degrees of NTIC of a process}
-
-	    Our theory indicates that conscious levels are determined by two key elements based on the definition of NTIC (Equation \ref{eq:nticObjective}).
-First, to achieve high level of NTIC, one needs to maximise the channel capacity between the current internal state and the future internal state $I(Y_{t+1};Y_{t})$.
-This indicates that the richer self-predictive information the NTIC process contained the higher level of consciousness the agent has.
-Considering two hypothetical systems composed of binary nodes, one has only three nodes and the other one has 1 million notes.
-Even thought the first system can reach the maximal the channel capacity, the maximal level of NTIC is only 3 bits.
-Comparing the first system, even though the second system does not have full self-predictability about its future state, the level of NTIC of this system can still far higher than the first system.
-This outcome naturally explains why people intuitively associate levels of consciousness with complexity of systems.\todo{Need to end this part and may need a reference} \toWrite{I want to say something about animal consciousness here}.
-
-	    Second, one can also minimise the conditional mutual information  $I(Y_{t+1};Y_{t}|E_{t})$.
-This suggests that conscious level positively correlates the level of information about the environment dynamic that the NTIC process encoded.
-Therefor, this implies that an agent who forms an NTIC process to lives and adapt to a more complex environment has a higher conscious level than an agent who interacts an environment with simpler dynamics.
-This also implies that agents who can explore, adapt model, and react to diverse environments should have higher level of consciousness.
-
-	    Note that the non-monotonic relationship between levels of NTIC and scale of coarse-graining suggests that there exists a scale of coarse-graining with the maximal level of NTIC.
-The self-predictive information is the key to achieve high conscious level.
-If a system dynamics is highly scholastic and unpredictable, the level of consciousness should be low.
-As a result, information processed at neuronal scales which is heavily noisy and highly scholastic cannot form a high level of consciousness.
-Similarly, after coarse-graining, macro-variables lose predictive fine-grain information, the predictability become low and also the channel capacity between the current state and future state becomes very small, NTIC would be low as well.
-Consequently, human consciousness should be maximised at a certain coarse-grained level in the neural system.
-
-	    Note that, the environment of a NTIC process in the nerual system includes not only the\todo{Werite this}
-
-        Finally, which coarse-grained level can achieve high NTIC? 
-        agent-scale operation
-        At the physical scale which human being live in, the environmental dynamics is nearly deterministic following the laws of classical physics.
-It gives agents living at this physical scale great advantages if the agents can build NTIC process internally.
-Therefore, to coarse-grain microscopic states is necessary
-
-		\begin{ants}
-
-			@ \todo{modify this figure}
-
-				\begin{figure}[H]				
-				\includegraphics[width=\textwidth]{WritingMaterials/FoxitReader_2019-01-31_19-03-59.png}
-				\label{fig:LevelOfConsciousness}
-				\caption{Level of coarse-graining and level of consciousness.
-The degree of NTIC is not a monotonic function of coarse-graining levels, suggesting that high conscious level may exist at a certain coarse-grained level }
-				\end{figure}
-		\end{ants}
-
-\rlend
-\rlstart{3}
-		\subsection{Conscious Contents Corresponding to Coarse-grained States}\needfig{maybe I need a figure here}
-        As we mentioned above, human conscious contents always consist of rich,  high dimensional, and integrated information.
-The state space of the correspondent physical system must have the same capacity of containing the same amount of information.
-We claim that conscious contents correspond to the state of the NTIC process.
-
-        This claim implies that the complexity of conscious contents correlates the amount of information encompassed in the NTIC process.
-Therefore, a crucial predict from our theory is that the larger state space of the NTIC process has the richer  conscious experience the process can have (e.g., a NTIC process involving a large amount of coarse-grained variables).
-Crucially, even experience of full darkness contains rich information because it rules out other enormous potential alternative states of conscious contents.
-Equivalently, in the physical system, to know the state of the NTIC process when there is no sensory input (darkness) also requires the same amount of information from the system.
-
-        Follow the example in the last section\todo{Do I have this example?}, a small creature lives in a simple environment with very limited environment dynamics.
-It may forms a simple NTIC process.
-However, in this situation, the self-predictive information is very low and the state space of the NTIC process is small.
-As the result, the richness of the conscious experience this agent has will be very limited.
-
-        Importantly, because the closure is at a coarse-grained scale one state of the informational closure can be mapped to several states at microscopic scale, our theory supports multiple realisation thesis \needref{multiple realisation} which suggests same conscious experiences can be mapped to different physical implementations.
-
-		\begin{figure}[H]
-			\includegraphicsTodo[width=0.8\textwidth]{WritingMaterials/LimitCycle/PhaseCycle.pdf}
-			\label{fig:limitCycle}
-			\caption{Example of coarse-graining by a limit cycle process}
-		\end{figure}
-
-		\begin{equation}\label{eq:LimitCycleExample}
-            \begin{array}{l}{\dot{y_1}=y_1-y_2-y_1\left(y_1^{2}+y_2^{2} \right)+\epsilon_{y_1}} \\ {\dot{y_2}=y_1+y_2-y_2\left(y_1^{2}+y_2^{2}\right)+\epsilon_{y_2}}\end{array}
-		\end{equation}
-
-		The noise sources, $\epsilon_{y_1}$ and $\epsilon_{y_2}$, are i.i.d with a normal distribution with mean $\mu=0$ a and varance $\sigma^{2}=1$
-
-		\begin{WritingMaterials}
-            @ Our theory naturally explains the compositional nature of consciousness because the joint states of entities in the NTIC process determine the contents of consciousness.
-
-		\end{WritingMaterials}
-
-	    \subsection{Reconcile level and content of consciousness}
-	    Recently, the segregation of conscious level and conscious contents raise a debate \citep{bayne2016there, Fazekas2016}.
-Our framework reconciles conscious level and conscious content.
-When the information encapsulate in the NTIC process is large and reaches a high NTIC, based on our definition, the system has high level of consciousness.
-Simultaneously, this provides a rich state space which is equivalent to encoding rich predictive environmental dynamic in the system.
-From this perspective, levels and contents of consciousness are just two different properties of NTIC processes.
-An important prediction from our theory is that in which the conscious level is determined by the size of the state space of the NTIC process rather the transient state of a system.
-For example, when we experience monotonous environment (a dark room), this does not degrade the conscious level.
-
-	    Our framework also explains why in normal physiological states level and content are positively correlated \citep{laureys2005neural}\needfig{}.
-To achieve high NTIC, a system also needs to have high dimensionality and a large state space which guarantees rich and high dimensional information in conscious contents.
-Therefore, this framework well integrates the two key but debated concepts in consciousness research.
-
-			\begin{WritingMaterials}
-    			@ This implies that, based on the Equation \ref{eq:nticObjective}, the self-predictive information about the future states that the current state holds and the information about the environment encoded in the process determine the level of consciousness.
-
-    			@ This also suggests that the richness of the environment being modelled by the	NTIC process has a direct contribution to the level of consciousness.
-
-				@ To have high level non-trivial informational closure, the states of the coarse-grained scale need to
-
-				@ First, maximise the mutual information between environment and the representation.
-				This term implies that the agent need to maximise predictive power of environmental state.
-This also suggest that the environmental complexity is a crucial factor to the level of consciousness.
-The more rich and complex environment the agent try to predict the higher level of consciousness the agent has.
-
-				@ Consciousness and complexity \cite{Tononi1998}
-
-				@ Second, to minimise the mutual information between environment and the representation conditional on the past state of the representation.
-This term suggests that the representation is self-predicable and it mimics the environmental transition.
-
-				@ Therefore, this theory predicts that level of consciousness determined by the environment that the agent adapts to.
-To form a high non-trivial informational closure, the agent will need to live in a complex environment and model the environmental transition precisely.
-
-			\end{WritingMaterials}
-
-\rlend
-
-\rlstart{2}
-		\subsection{sensory hierarchy and neural coarse-graining}\label{sec:SensoryHierarchy}
-
-        It's important to note that the coarse-graining direction is not necessary to be align with \critical{Just saying anatomical is not enough.
-Need better expression} anatomical sensory hierarchy in the neural system.
-Our theory is different from consciousness theories which focus on the anatomical hierarchy, for example the intermediate Level Theory \citep[see also \ref{IntermediateLevelTheory}]{prinz2007intermediate, jackendoff1987consciousness}.
-Due to the pervasive noise in the microscopic levels in the neural system reliable information processes need to be built upon the coarse-grained levels.
-Nevertheless, to exercise causal power in actuators and environments, to read out information from coarse-grained levels is necessary.
-\needfig{Maybe need a figure discribing brain to hand}.
-Therefore, the neural system still implement readout decoders for the subsequent signal output.
-In figure \ref{fig:hierarchy}, the blue arrows indicate the readout mechanisms implemented in the neural system.
-We argue that previous data suggesting the neural correlates of consciousness between microscopic neural activities and conscious contents may be misled.
-
-			\begin{figure}[H]
-				\includegraphics[width=\textwidth]{WritingMaterials/SeperationOfCGandCortHierachy.pdf}
-				\label{fig:hierarchy}
-			\end{figure}
-
-            \begin{WritingMaterials}
-    			@ Of course, from evolutionary perspective, neural system should develop a better hardware to support neural coarse-graining
-
-				@ For example, pooling layers in CNN is an implementation of coarse-graining function. It' is very plausible visual processing hierarchy in the neural system realises pooling layers.
-
-				@ It is possible that the neural system represents higher-level information processing by low level physical subtract.
-For example, studies have found representation for summery statistics of signal and neural.
-population.\needref{neural representation for summery statistics}\\
-				From this point of view, sensory hierarchy may extend along with levels of coarse-graining.
-            \end{WritingMaterials}
-
-\rlend
-
-\rlstart{2}	
-        \subsection{Dynamical Boundary}
-        Our theory makes strong predicts that the physical boundary of a conscious system is dynamical.
-The boundary is determined by elements forming high NTIC.
-This implies that when the structure of interaction between elements changes the physical boundaries support consciousness should also change.
-If some coarse-grained variables encode environmental information, they may become necessary components to form high NTIC.
-In such case, these coarse-grained variables are "recruited" inside the boundary of conscious processes.
-Note that, due to synergetic information, even recruiting some new variables may largely increase the level of NTIC.
-        This may explain why consciousness is tightly associated with binding and integration of information in human perception and cognition.
-Another crucial implication is that the same neural substrates may not be always involved in conscious processing rather it depends on whether it creates high NTIC with other members in the neural system.
-\needfig{Maybe I need a figure h  ere as well}
-
-\rlend
-
-	\section{Conscious versus Unconscious Processing}
-		\ideaBox{The goal of this part is to combine empirical study and phenomenology}
-	    \ideaBox{I need to expend this section much more and more references}
-	    In this section, we suggest that our theory has a strong exploratory and predictive power but with minimal assumptions.  
-		Our theory indicates that, to make information conscious, a sufficient and a necessary conditions need to be satisfied.
-
-		\begin{enumerate}
-		    \item Sufficient condition: Information is encoded in NTIC process. 
-		    \item Necessary condition: The system is capable of constructing NTIC processes at coarse-grained levels. 
-		\end{enumerate}
-
-		Take the neural system as an example, our theory can well explain previous empirical findings in consciousness science and further make strong and more precise predictions for future studies.
-In the following, we discussed the implication of the two necessary conditions with respect to the empirical data in the literature of consciousness.
-
-		\subsection{Unconscious Processing}
-\rlstart{3}			
-		    \subsubsection{\sim 1}
-		    % reflexive behaviour
-    		\begin{figure}[H]
-    			\includegraphics[width=0.8\textwidth]{WritingMaterials/Fig_Reflexive/Reflexive.pdf}
-    			\caption{Reflexive Behaviours}
-    			\label{fig:reflexive}
-    		\end{figure}
-
-    		\begin{ants}
-    		    @ As described above, if a process fails to meet either one of the two necessary conditions, information remains unconscious.
-
-    		    @ We first consider the first condition: A process fails to achieve NTIC.
-
-    		    @ Many processes in the neural network system fall in this category.
-
-    		    @ When a process is not information closed the internal state of the process is largely determined by the environmental state.
-
-    		    @ In terms of perception, this indicates that the process only passively reacts.
-
-    		    @ In terms of action, this implies reflective behaviours.
-
-    		    @ Reflective behaviours usually are considered as automatic and non-conscious behavioural controls. \citep{casali2013theoretically}\needref{More referene}.
-
-    		    @
-
-    		    @ In modern reinforcement learning framework, this usually is referred to policy-based agents.
-The agents constructs a policy function that maps sensory inputs to the action space \citep{sutton2018reinforcement}.
-
-    		    @  Roughly speaking, a policy is a mapping from perceived states of the environment to actions to be taken when in those states.
-It corresponds to what in psychology would be called a set of stimulus–response rules or associations
-
-    		    @ The same principle can be applied to blindsight and procedure memory which are often considered as the classical cases of unconscious processing
-
-    		    @ This classic patient study of D.F.
-who has apperceptive agnosia \citep{10.3389/fneur.2014.00255} also falls in this category.
-With online sensory inputs, the neural system can create functional processes without forming NTIC.
-
-    		    @ Note that, when we prolong the temporal interval between stimulus and action, usually consciousness is necessary for learning associations. \needref{time}
-
-    		    @ Another case is that, processes are information closed but it is trivial.
-
-    		    @ ============================================================================
-
-    		    @ Even though the system can form NTIC processes in some certain coarse-grained levels, information processing outside these levels remains unconscious.
-
-    		    @ microscopic neural activities fall in this category.
-
-    		    @ When processes at macroscopic levels becomes informational closed, information from other levels is redundant.
-
-    		    @ Therefore, information from other levels does not influence the dynamic of this level.
-
-    		\end{ants}
-\rlend
-
-		----------------------------------------------------------------------------
-		=== -
-
-		--- 
-		procedure memory
-		Reflective reaction, blindsight,
-
-		\begin{equation}\label{eq:InformationFlow}
-		\begin{aligned}
-            \pi(A|S)\\
-            {J_{t}(E \rightarrow Y )} & {:= I(Y_{t+1};E_{t}|Y_{t})} > 0
-        \end{aligned}
-		\end{equation}
-		\needhelp{Math here}
-
-		\begin{figure}
-			\includegraphicsTodo[width=0.8\textwidth]{WritingMaterials/S_Y_A/S_Y_A_01.png}
-			\caption{Policy network}
-			\label{fig:s2a}
-		\end{figure}
-
-		When the first condition is not satisfied,
-
-		In this case, the future state of this process is partially or fully determined by environment states. We can see
-
-		\begin{ants}
-		    @ Conscious
-
-		    @ Boundary 
-    		    @@ binocular rivalry/CFS
-    		    @@ Libet's experiment
-    		    @@ Unconscious determinants of free decisions in the human brain    		    
-    		    @@ Priming
-    		    @@ Bistable perception
-    		    @@ Perceptual overflow
-    		    @@ Threshold of unconscious to consciousness
-    		    @@ Probabilistic information is always unconscious
-
-		    @ Unconscious 
-                @@ Reflection
-        			@@@ Reflexive systems is not informational closured.
-        			@@@ Base	d on our theory,
-        			@@@ x -> s -> a
-        			@@@@ the system state is determined by environmental state, then it is not conscious.
-        			@@@ Therefore, in general, a simple policy network is not conscious.
-
-    			@@ Blindsight
-
-	    			@ Passive neural activity
-
-		\end{ants}
-
-		\subsection{reflexive behaviours is unconscious (or environment-state dependent processes)}\label{sec:reflexive}
-		\subsubsection{Reflection}
-		\begin{ants}
-			@ Reflexive systems is not informational closured.
-			@ Base	d on our theory,
-			@ $P(A|S)$ action policy is conditional on the sensory input data.
-			@ x -> s -> a
-			@@ the system state is determined by environmental state, then it is not conscious.
-			@ Therefore, in general, a simple policy network is not conscious.
-		\end{ants}
-
-		\subsubsection{Blindsight}
-		\begin{ants}
-			@ This also blindsight.
-			@ Blindsight patients and still make above chance judgement without conscious awareness of visual targets.
-			@ The stimulus-reaction policy network still intact, but it cannot form informational closure and therefore, patients has no conscious awareness of visual  targets
-			@ Patient B.F. reactions are stimulus driven.
-		\end{ants}
-
-		\subsubsection{procedure memory}
-
-		\subsection{Conscious Processing}
-		So far, previous consciousness research has identified a set of perceptual and cognitive functions which not exclusively but frequently associate with consciousness.
-
-		\begin{ants}
-            @ response inhibition 
-            @ goal
-            @ planning            
-            @ conflict resolution
-            @ error detection         
-            @ task-switching
-            @ working memory
-            @ cognitive control 
-            @ overriding automatic responses
-            @ self-monitoring 
-            @ global availability 
-            @ integration             
-            @ stabilisation
-            @ information for off-line processing
-            @ flexible routing of information
-            @ integrates behaviour across time            
-            @ tasks for long duration
-            @ flexibility and the strategic use of that information for complex operations and decision-making 
-            @ flexible and adjust our behavior to different contexts and goals
-            @ complex visuomotor abilities
-            @ conscious thought, reflection, reasoning, and temporally extended sense of self. 
-            @ multiple alternative possibilities
-            @ simulate alternative realities 
-            @ imagination
-            @ dreaming 
-            @ anticipation
-            @ intending
-            @ replaying
-            @ interpreting
-            @ reflecting
-            @ reasoning
-            @ problem solving 
-            @ deciding            
-		\end{ants}
-
-		To achieve high NTIC has evolutionary advantage.
-When a process achieves NTIC, the current state of the process contains the information about its future state (Eq.
-(5)).
-Therefore, the neural system can build forward models to predict the future state of the environment using the information encoded in the NTIC process.
-Cognitive functions recruiting forward models built upon it are conscious.
-(E.g., planning and imagination)
-
-		It is important to note that we do suggest any functionalism of consciousness.
-Rather, we believe that information is fundamentally linked to consciousness.
-The reason why consciousness is accompanied with some specific cognitive function is because NTIC is a powerful property that brings creatures a lot of advantage in the evolution \cite{Seth2009Encyclopediaofconsciousness}.
-
-	    \begin{WritingMaterials}
-	        @ importantly, evidence suggests that those functions in some conditions do not require the involvement of consciousness.
-This evidences an important fact that consciousness is not necessay to these functions.
-
-	        @@ Predictive information about the environment.
-
-	        @@ Stability
-
-	        @@ simulation environmental dynamics
-
-	        @ Replaying past events
-
-	        @ \rewrite{However, recent evidence also points out interesting dissociations between conscious and unconscious information processing when it comes to the duration, flexibility and the strategic use of that information for complex operations and decision-making} \cite{van2012role}
-
-	    \end{WritingMaterials}
-
-		\subsection{Unconscious Processing}
-		When processes fail to satisfy either of the two conditions, they remain unconscious.
-First, when processes do not meet the first condition, i.e.
-the information processed not at the certain coarse-grained level, the information will not be included in conscious contents.
-For example, we are never conscious of neural spike activities at microscopic levels (e.g.
-single cell activities) because information passing among individual neurons are not at the certain coarse-grained level.
-\todo{Rewording}Libet's free will experiment can be also explained by our theory.
-The random neural fluctuation under Libet's free will experiment happens at the microscopic scale \citep{SchurgerE2904}.
-
-		Second, when processes do not meet the second condition, i.e.
-processes which do not achieve high NTIC will remain unconscious.
-This can explain why many "policy-based" processes are not conscious.\todo{Need a better term/way here} Policy-based here features those processes taking sensory information as input and directly outputting actions.
-Therefore, the future states of policy-based processes largely depend on the environmental states and failed to achieve informational closure.
-Neural processes are included in this category, e.g.
-reflexive neural circuit, blindsight, procedure memory.
-
-		To summarise, our theory can well explain the various findings with parsimonious assumptions.
-
-	    \begin{ants}
-	        @ \rewrite{the nonsemantic processing of primes is enhanced and priming effects are boosted when the experimental context allows the formation of automatic stimulus–response mappings.}\cite{VandenBussche2009}
-	    \end{ants}
-
-	\section{Comparison with other theories}
-		\ideaBox{Main points should be same/diff, our advantages, and predictions}
-		In this section, we will discuss the relationship between our theory and other popular modern theories of consciousness.
-
-\rlstart{2}
-		\subsection{Theories about multilevel views on consciousness and cognition}
-        Previously, multilevel views on consciousness and cognition have been proposed.
-We shortly describe two theories which is \todo{XXX and XXX} related to our current proposal.	% We discussed the differences between our theory and other theories about multilevel views.
-
-            \subsubsection{level of Organisation \cite{wimsatt1994ontology}}
-                As mentioned previously, the level of coarse-graining is different from the anatomical level.
-                Pennartz focus more on multimodal representation as the most important factor (See the discussion in \cite{pennartz2015brain}).
-Our proposal is inline with Pennartz's Neurorepresentational  theory (Neurorepresentationalism) \cite{pennartz2018consciousness,pennartz2015brain}.
-However, it’s crucial to note that our theory claims only the level of coarse-graining achieving NTIC matters to consciousness rather than the anatomical level of sensory hierarchy.
-                \ideaBox{Should I also deal with Marr's level of abstraction?}
-
-			\subsubsection{Intermediate Level Theory} \label{IntermediateLevelTheory}
-                One important theory linking consciousness to multilevel views is the Intermediate Level Theory (ILT).
-ILT proposes that conscious experience only correlates specific levels of representations in the sensory processing the hierarchy.
-This theory claims that consciousness only associates with the representation at intermediate levels rather than the ones at lower-level or higher-level discribed as 2.5D.
-However, ILT focuses on the levels in terms of anatomical direction.
-As mentioned previously, a critical difference between ILT and our theory is that our theory doesn't assume the direction of coarse-graining should align with the direction of anatomical processing levels along cortical hierarchies (see fig \ref{fig:hierarchy}).
-
-                Different from ILT which suggests that the neural substrates responsible for the 2.5D computation is conscious, we predict that if information that is carried by v1 neurons are necessary to complete informational closure, the states of V1 neurons should also co-vary with conscious contents.
-
-			\subsubsection{Pennartz's neurorepresentational theory (Neurorepresentationalism)}
-			    Our theory shares some similar concepts with Pennartz's Neurorepresentationalism.
-However, Neurorepresentationalism focuses on multimodal representation \cite{pennartz2018consciousness,pennartz2015brain}.
-Another focus of neurorepresentationalism is on "making sense" between representations\todo{Need something here}.
-Different from neurorepresentationalism, conscious contents in our framework are grounded by the informational relations between variables in NTIC because NTIC provides a closed relationship between states in a system.
-
-			    Similar to Neurorepresentationalism, our framwork is more close to Marr ’ s original distinction between the levels of (neural) implementation, algorithms, and computational theory [122], but focuses on how conscious representations correspond to computational operations at levels with lower complexity and representational capacity.\cite{pennartz2018consciousness,pennartz2015brain}
-
-			    Neurorepresentationalism is also a functionalist perspective.
-However, e don't assume any functional properties as the criteria of consciousness.
-Instead, we propose information as a more fundamental principle correlates consciousness.
-
-		        \begin{WritingMaterials}
-				%% Back up materials
-
-				@ Prinz suggested that \rewrite{as.
-Cells in V1 are not promising candidates, because they do not reliably respond in ways that are consistent with features that we experience consciously.
-} \cite{prinz2007inter    mediate}
-
-				@ \rewrite{
-					The intermediate level theory originally proposed by Ray Jackendoff and further defended and specified by Jesse Prinz proposes that within the hierarchy of representations that are used to describe the cognitive system, conscious experience occurs only for specific levels of representation.
-The theory is rooted in Jackendoff ’s analysis of different cognitive systems such as vision, language, and music and the subsequent observation that consciousness does not arise anywhere within these systems.
-According to Jackendoff, consciousness is not associated with low-level, nor with high-level representations, but rather with those implying intermediate levels of processing.
-For instance, in the domain of object recognition, it is assumed that the visual system comprises a low level with local computations of visual features, an intermediate level reflecting binding and object recognition, and a higher level computing viewpoint invariance and representing abstract categories.
-According to Jackendoff and Prinz, conscious experience is not comprised of a disunified picture of visual features, nor is it represented by viewinvariant categories.
-Rather it is composed of bound and specific instances of objects that are assumed to be computed at the intermediate level of representation.
-In an analogous manner, speech perception can be decomposed into three levels: an acoustic representation of speech sounds at the lower level, a high level involving abstract lexical and syntactic categories, and in between a word recognition level relying on phonological representations.
-This theory explains why the conscious experience associated with speech perception mostly involves phonological representations, rather than other levels of representations.
-In Jackendoff and Prinz’ theory,the privileged role of the intermediate level of processing is based on the need for real-time computational efficiency.
-Indeed, this level of representation is assumed to be the most relevant one regarding ecological and functional needs.
-Another important aspect of this theory concerns the central role of attention during conscious experience.
-Here, attention is defined as a selection process that acts as a gate to working memory mechanisms.
-It performs the function of selecting the relevant information that is amplified afterward and then becomes conscious.
-Indeed, Prinz acknowledges that activation of an intermediatelevel representation on its own cannot be a sufficient condition for consciousness, given that those representations can be activated during subliminal perception.
-However, this theory makes the crucial postulate that the amplification of intermediatelevel representations by attention is a necessary and sufficient condition for consciousness.
-In sum, for each domain of processing, the content of consciousness at a particular moment is supported by a representational structure of intermediate level for that domain, which is selected to enter short-term memory, and enriched by attentional processing.} \cite{banks2009encyclopedia}
-
-				@ \rewrite{
-					In 1987, Ray Jackendoff published Consciousness and the Computational Mind.
-In it, he posed an important Where question: Where, in the fl ow of information, does consciousness arise?
-Most cognitive scientists agree that the mind is, in some sense, a computer.
-It is a device that processes information by transforming representations in accordance with rules.
-Computational devices decompose into various interconnected subsystems, each of which performs some aspect of a complex task.
-Given such a decompositional analysis, we can ask: in which subsystems does consciousness arise?
-If we depict the mind as a vast fl ow chart, and highlight the boxes whose rules and representations are conscious, which boxes should we mark?
-Jackendoff ’s answer is simple and elegant.
-He noticed that many of our mental capacities, including our senses and our language systems, are organized hierarchically.
-In each of these hierarchies, it makes sense to talk about low- , intermediate- , and high- level processing systems.
-We break down tasks into stages.
-Appealing to prevailing models of these stages, Jackendoff observed that the intermediate level seems to be privileged with respect to consciousness.
-Consciousness seems to arise in intermediate- level processing systems and not elsewhere.} \cite{prinz2007intermediate}
-
-				@ \cite{jackendoff1987consciousness}
-				@ \cite{prinz2007intermediate}
-				@ 2.5D
-
-				@ about why it is this level
-				@@ \rewrite{
-					Under the computational interpretation, the “why” question means: In what sense are intermediate level representations computationally important or distinctive?
-Th is is a tractable question, and it may lead to insights into the function of consciousness.
-Representations at the intermediate level are ideally suited for real- time deliberative behavioral responses.
-Low- level representations fail to bind features into coherent wholes.
-If we are going to interact with our environment, the low level is not a good guide.
-Th e high level is a good deal better for action, but also suboptimal.
-Th e high level tells us the category of the stimuli we perceive, but from an allocentric point of view.
-It abstracts away from stimulus features that are crucial for action.
-If we encounter a predator, the high- level visual representation does not tell us if it is facing toward us or away from us.
-Without that knowledge, we cannot decide what course of action to take.
-So, I propose that the intermediate level plays a distinctive role in information processing.
-It delivers representations that are coherent but viewpoint specifi c.
-Th ese representations are useful for determining what to do here and now.arg1} \cite{prinz2007intermediate}
-				@@ \rewrite{
-					I conclude that the intermediate level plays a distinctive and important computational role.
-Some researchers find this puzzling.
-In wondering why the intermediate level is privileged, they note the arbitrariness of the fact that perceptual hierarchies have three levels.
-Could they not have two?
-Or a hundred?
-Do the 50 or so areas that contribute to visual processing really divide neatly into three levels?
-I think these puzzles depend on a particular understanding of what the word “intermediate” amounts to.
-One might get caught up in the fact that the intermediate level is the second stage in a sequence.
-Call this the “serial understanding of the intermediate level.” Alternatively, one might think of the intermediate level semantically.
-On this reading, the intermediate level is one that is not abstract and categorical, but not piecemeal or disunifi ed.
-Th ese notions are all in need of some refi nement, but, as a fi rst approximation, the idea is that intermediate- level representations are neither too specifi c nor too general.}\cite{prinz2007intermediate}
-
-				%% Our theory
-				@ However, as we mentioned in Section \ref{sec:SensoryHierarchy}, \rewrite{The notion of ‘ levels ’ deployed here is functional and very different from that of successive anatomical processing stages along cortical hierarchies [75] or from anatomic scales in the brain.
-The multi-level concept in [2] is more akin to Marr ’ s original distinction between the levels of (neural) implementation, algorithms, and computational theory [122], but focuses on how conscious representations correspond to computational operations at levels with lower complexity and representational capacity.}\cite{pennartz2018consciousness,pennartz2015brain}
-			\end{WritingMaterials}
-
-\rlend
-
-\rlstart{2}	
-		\subsection{First-order theories}
-            The first-order theories suggest that consciousness is determined by early sensory information or neural activities\needref{First-order theories}.
-The first-orde view maintains that conscious awareness is determined by early sensory activity alone, independently of higher-order representations.
-\rewrite{According to first-order views, phenomenal consciousness consists in analog or fine-grained contents that are available to the first-order processes that guide thought and action.
-So a phenomenally-conscious percept of red, for example, consists in a state with the analog content red which is tokened in such a way as to feed into thoughts about red, or into actions that are in one way or another guided by redness.}
-
-            We predict that, if early sensory information or neural activities after coarse-graining take parts in the NTIC process, early sensory information or neural activities also contribute consciousness.
-However, due to coarse-graining, changes of early sensory information or neural activities do not necessarily accompany with changes of conscious contents.
-\todo{Need more here, espectially more counterintuitive predictions}
-
-			\begin{WritingMaterials}
-				@ \rewrite{
-					The first-order view maintains that conscious awareness is determined by early sensory activity alone, independently of higher-order representations.
-Thus the crucial difference between the first-order and higher-order views is that the latter but not the former predict that conscious awareness is determined at least in part by prefrontal and parietal activity.
-Therefore, in the group of first-order theorists we include here not only those commonly labeled as such in the philosophical literature [11] but also theorists, such as Ned Block [12,13], who hold that the phenomenal qualities of awareness depend on the biological substrate rather than merely the content of the first-order representations, as well as scientists who hold that visual awareness depends on activity in content-specific regions of the extrastriate cortex [24,25] or on feedback from these regions to the primary visual cortex [26].
-Most first-order theories explain the difference between awareness and unawareness by positing that the latter is associated with weak information [29] or with representations in alternative (e.g.
-subcortical) sensory pathways.
-Thus this view suggests that conscious and unconscious processing will have different functional consequences.
-Whereas some first-order theorists hold that some higher cognitive functions can be performed without conscious awareness [30–32], most first-order theorists take a difference in perceptual task performance (e.g.
-‘hits’ vs ‘misses’ in a detection task) as evidence for a difference in conscious awareness [12,13,25,26,33].
-In other words, they typically associate task performance with awareness..} \cite{lau2011empirical}
-
-				@ Among those are first-order theories, on which a mental state is conscious if being in that state results in one's being conscious of something;
-
-				@  According to first-order views, phenomenal consciousness consists in analog or fine-grained contents that are available to the first-order processes that guide thought and action.
-So a phenomenally-conscious percept of red, for example, consists in a state with the analog content red which is tokened in such a way as to feed into thoughts about red, or into actions that are in one way or another guided by redness.
-
-			\end{WritingMaterials}
-
-\rlend
-
-\rlstart{1}
-		\subsection{Higher Order Thought theory of consciousness}
-		    In contrast to first-order theories, higher-order thought theories suggest that consciousness depends on higher-order representations representing agents as being in particular internal states.
-Meta-cognition is also associated with many conscious cognitive function.
-However, we propose a new perspective and indicate that HOT may be a misunderstanding \critical{Very bad writing.
-I need to rewrite this part}.
-This may be the result of neural coarse-graining.
-Because contents in informational closure look like watching fine-grained information, people may have an wrong impression about it.
-Coarse-grained information can be summary statistics which may be misunderstood as higher-order representation.
-It is true that the neural system does create  meta-representation to represent xxx\needref{Maybe come studies about confidence represenatation}.
-The higher-order representation may resemble coarse-grained variables.
-This may cause misidentify the entity which correlates conscious experience.
-
-		    Moreover, the predictive information in NTIC is critical for other systems to build forward models for a wild range of tasks.
-Therefore, most of the high level cognition can utilise the state of informational closure.
-For example, mental planning needs a precise forward model to infer the environmental dynamics.
-
-			\begin{WritingMaterials}
-		    @ In contrast to first-order theories, higher-order thought theories suggest that consciousness depends on higher-order representations representing agents as being in particular internal states.
-
-		    @ Coarse-grained information can be summary statistics which may be misunderstood as higher-order representation.
-
-		    @ It is true that the neural system does create  meta-representation to represent xxx.\needref{Maybe come studies about confidence represenatation}
-
-		    @ The higher-order representation may resemble coarse-grained variables.
-
-		    @ This may cause misidentify the entity which correlates conscious experience.
-
-		    @ ----------------------------------------------------------------------------
-
-			@ Information closure directly is critical for other systems to construct forward models.
-
-			@ Therefore, most of the high level cognition can utilise the state of informational closure.
-
-			@ For example, mental planning needs a precise forward model to infer the environmental dynamics.
-
-			@ \idea{This is way HOT always involve consciousness }
-
-			@ \cite{rosenthal2005consciousness}
-
-            @ ============================================================================
-			@ \rewrite{
-				Higher-order theories of consciousness argue that conscious awareness crucially depends on higher-order mental representations that represent oneself as being in particular mental states.} \cite{lau2011empirical}
-
-			@ \rewrite{
-				According to this view, humans not only have first-order non-conceptual and/or analog perceptions of states of their environments and bodies, they also have second-order non-conceptual and/or analog perceptions of their first-order states of perception.
-And the most popular version of higher-order perception theory holds, in addition, that humans (and perhaps other animals) not only have sense-organs that scan the environment/body to produce fine-grained representations that can then serve to ground thoughts and action-planning, but they also have inner senses, charged with scanning the outputs of the first-order senses (i.e.
-perceptual experiences) to produce equally fine-grained, but higher-order, representations of those outputs (i.e.
-to produce higher-order experiences).
-A version of this view was first proposed by the British Empiricist philosopher John Locke (1690).
-In our own time it has been defended especially by Armstrong (1968, 1984) and by Lycan (1996).} \url{https://plato.stanford.edu/entries/consciousness-higher/#SelRepHigOrdThe}
-
-			@ \rewrite{
-				neutral about whether conscious awareness adds significant utility or immediate impact on behavior and task performance [1,27].
-This is because the view assumes that task performance in most perceptual and cognitive tasks depends mainly on first-order rather than higher-order representations.
-Because conscious awareness can differ even if all first-order representations remain completely unchanged, such awareness itself might serve little function [1,27].}\cite{lau2011empirical}
-				\ideaCallout{
-					My theory would have similar prediction.
-Because conscious contents are coarse-grained results from low-level information.
-It is possible that more than two low-level neural states all coarse-grained to a high-level state.
-}
-
-			@ \rewrite{
-					Metacognition: cognition that is about another cognitive process as opposed to about objects in the world.
-In this article we use it mainly to refer to sensory metacognition: a cognitive process that concerns the quality or efficacy of a perceptual process.
-The capacity of sensory metacognition is sometimes empirically assessed by the correspondence between subjective report and task performance: how closely are they associated with each other on a trial-by-trial basis}\cite{lau2011empirical}
-
-			\end{WritingMaterials}
-
-\rlend
-
-\rlstart{2}
-		\subsection{Global workspace theory}
-		Global workspace theory (GWT)\cite{baars1988cognitive, baars1997theatre, baars2002conscious} or Global Neuronal Workspace theory (GNWT)\cite{dehaene1998neuronal, dehaene2001towards, dehaene2011experimental} states that the neural system consists of many separate specialised modules and a central global workspace (GW) which integrates and passes information amount the modules.
-Only the information that is accessed by the global workspace can be conscious aware of.
-The modules competes with each other to gain the access to the global workspace and the information from the winner can trigger an all-or-none "ignition" in the global workspace and be globally broadcasted to other modules.
-Conscious contents then associates information which gains access to the internal global workspace \cite{Dehaene2017}.
-Our framework can well accommodate and interpret these claims by GWT.
-
-		Stability: Conscious perception necessitates representational stability. Our theory rests upon self-predictability which formally encompasses stability.
-
-		Broadcasting: When new sensory information from a modality is involved in NTIC, the information can be preserved in the following dynamic of NTIC.
-The neural system can extract the information for specific task goals.
-This is equivalent to the function of broadcasting.
-
-		Non-linear ignition: Because mapping microscopic to macroscopic states is many-to-one, it commonly shows a nonlinear relationship between microstates and macrostates.
-In our theory, new information presents in conscious perception corresponds to a transition in the state space of the NTIC process.
-This can cause a significant change of the brain states and resembles non-linear ignition of brain activities.
-Conscious access as an accumulation of evidence leading to an all-or-none ignition What, if anything, remains unique to conscious processing?
-Although many cognitive operations can be partially launched non-consciously, these operations rarely if ever run to completion in the absence of consciousness.
-A subliminal stimulus may induce above-chance performance, behavioural priming, and a small amount of brain activity in narrowly defined brain networks, but these measures often increase dramatically as soon as the subject reports seeing the stimulus, especially in high-level areas [46 60,61  ].
-Accumulation of evidence has been demonstrated with non-conscious stimuli [59], but only conscious stimuli cross the threshold beyond which an overt strategy can be fiexibly deployed.
-\todo{Cite similar opinion from other theories}
-
-		A difference between our theory and GWT is that our theory does not suggest a neuronal core anatomical area for consciousness.
-\todo{Link to Section 4}.
-Coarse-grained information in NTIC is more crucial for consciousness rather than neural substrates supporting the global workspace.
-
-		\begin{WritingMaterials}
-			%% Introduction
-			@ Global workspace theory (GWT)\cite{baars1988cognitive, baars1997theatre, baars2002conscious} or Global Neuronal Workspace theory (GNWT)\cite{dehaene1998neuronal, dehaene2001towards, dehaene2011experimental} states that the neural system consists of many separate specialised modules and a central global workspace (GW) which integrates and passes information amount the modules.
-Only the information that is accessed by the global workspace can be conscious aware of.
-The modules competes with each other to gain the access to the global workspace and the information from the winner can trigger an all-or-none "ignition" in the global workspace and be globally broadcasted to other modules.
-Conscious contents then associates information which gains access to the internal global workspace \cite{Dehaene2017}.
-
-			@ Submodule access and NTIC
-
-			%% Our theory
-
-			@ Our theory can well accommodate several claims by GWT.
-
-			@ Conscious perception necessitates representational stability: Our theory rests upon self-predictability which formally encompasses stability.
-
-			@ Broadcasting: When new sensory information from a modality is involved in NTIC, the information can be preserved in the following dynamic of NTIC.
-The neural system can extract the information for specific task goals.
-This is equivalent to the function of broadcasting.
-
-			@ Non-linear ignition: Because mapping microscopic to macroscopic states is many-to-one, it commonly shows a nonlinear relationship between microstates and macrostates.
-In our theory, new information presents in conscious perception corresponds to a transition in the state space of the NTIC process.
-This can cause a significant change of the brain states and resembles non-linear ignition of brain activities.
-
-			@ our theory re-explains the critical xxx from GWT.
-
-			@ The critical difference is that our theory does not suggest a neuronal core anatomical area for consciousness. We suggest coarse-grained information form NTIC is crucial for consciousness.
-
-			@ In sum, our theory is compatible with previous physiological evidence supporting GWT.
-
-		\end{WritingMaterials}
-
-% 			\subsubsection{Global availability and Broadcasting}
-% 			\subsubsection{Stability}
-				\begin{WritingMaterials}
-					@ the presence of contexts as stable coalitions shaping access to the workspace.
-
-					@ e ‘all-or-none’ behavior, whereby the incoming evidence either quickly dies out (corresponding to subliminal processing) or is accumulated and amplified non-linearly into a full-blown state of high-level activity.
-This global ‘ignition’ has been proposed as a marker of conscious perception [70].
-Indeed, empirically, when stimulus strength is varied, the early stages of non-conscious processing typically show a linear variation in activation, whereas conscious access is often characterized by a late non-linear amplification of activation which invades a distributed set of parietal, prefrontal and cingulate areas
-				\end{WritingMaterials}
-
-% 			\subsubsection{Broadcasting}
-
-			\subsubsection{Ignition}
-				\begin{WritingMaterials}
-					@ Conscious access as an accumulation of evidence leading to an all-or-none ignition What, if anything, remains unique to conscious processing?
-Although many cognitive operations can be partially launched non-consciously, these operations rarely if ever run to completion in the absence of consciousness.
-A subliminal stimulus may induce above-chance performance, behavioural priming, and a small amount of brain activity in narrowly defined brain networks, but these measures often increase dramatically as soon as the subject reports seeing the stimulus, especially in high-level areas [46 60,61  ].
-Accumulation of evidence has been demonstrated with non-conscious stimuli [59], but only conscious stimuli cross the threshold beyond which an overt strategy can be fiexibly deployed.
-				\end{WritingMaterials}
-
-			\begin{WritingMaterials}
-				@ GWT is one of the current popular consciousness theories.
-
-				@ \rewrite{AI system and corresponds to our first functional definition of consciousness: global availability} \cite{Dehaene2017}
-
-				@ C1: Global availability of relevant information The need for integration and coordination \cite{Dehaene2017}
-
-				@ Evidence for integration and broadcasting
-
-				@ Stability as a feature of consciousness \rewrite{“ meta-stability ” seems to be necessary for the nervous system to integrate information from a variety of modules and then broadcast it back to them, achieving flexible cross-module routing.}
-
-				@ \rewrite{integration of computational resources in a large-scale coordination and for the exchange of information among processors}
-
-				@ \rewrite{Grounded on the distinction between conscious and unconscious processes, Bernard Baars’ global workspace theory is one of the most influential cognitive theories of consciousness.
-This theory relies on the metaphor of a theater.
-In this theater, unconscious specialized processors (equivalent to modules) are assumed to be the actors and the audience.
-While the audience represents the set of passive processors, actors represents active processors playing on the stage of the theater (i.e., the workspace).
-These actors are engaged in a competition for being seen by the audience: by broadcasting their information they actually compete for more broadcasting.
-Active processors with the highest coherent activity can form local coalitions that strengthen them in this competition process.
-The strongest coalition in this competition dominates the workspace, in a winner-take-all fashion, and corresponds to the content of consciousness.
-The workspace is equated by Baars to working-memory, in which only the most active content becomes conscious.
-Additionally, the dominant coalition benefits from global broadcasting, which allows it to recruit new processors from the audience in order to form a global coalition.
-Here, consciousness allows for the integration of computational resources in a large-scale coordination and for the exchange of information among processors that would otherwise remain separated.
-In this theory, each processor can operate in the conscious mode if it benefits from global broadcasting through the workspace, or it can operate in the unconscious mode when disconnected from the workspace.
-An important feature of the global workspace theory is the presence of contexts as stable coalitions shaping access to the workspace.
-Contexts are constituted of unconscious processors reflecting, in a hierarchical manner, our expectations, our beliefs, our goals, and ultimately our self.
-In particular, attention is implemented as a goal context in this theory.
-It is described as a mechanism that controls access to the workspace, acting as a filter and biasing the competition process toward a particular set of actors.
-At any given moment, the dominant coalition is under the spotlight of attention, and its informational content becomes the content of conscious experience.
-A crucial aspect of Baars’ theory is that it avoids the problem of the homunculus by reducing it to an audience of multiple unconscious processors.
-Here, there is no need for a hypothetical single conscious observer in the system, and thus there is no issue of infinite regression with a homunculus inside another homunculus.
-Instead, consciousness is considered to reflect the global broadcasting of information to an audience of unconscious processors.
-As the audience is unconscious, unsupervised, and receptive rather than attending to the information, it does not constitute an internal homunculus.}
-
-			\end{WritingMaterials}
-\rlend
-
-		\subsection{Sensorimotor contingency}
-		Sensorimotor contingency (SMC) theory of consciousness is proposed to account of conscious perception.
-It suggests that different types of SMCs give rise to different characteristics of conscious perception \cite{o2001sensorimotor}.
-The theory radically rejects the view that conscious contents is associated with information encoded in internal representations in the neural system.
-Rather, the quality of conscious perception depends on agents' mastery of SMCs.
-It emphasises the interactions between a system (the neural system) and its environment are crucial to form conscious perception
-
-			\begin{ants}
-				%% SMC
-
-				@ Sensorimotor contingency (SMC) theory of consciousness is proposed to account of conscious perception.
-It suggests that different types of SMCs give rise to different characteristics of conscious perception \cite{o2001sensorimotor}.
-
-				@ The theory radically rejects the view that conscious contents is associated with information encoded in internal representations in the neural system.
-
-				@ Rather, the quality of conscious perception depends on agents' mastery of SMCs.
-
-				@ It emphasizes the importance of the interactions between a system (the neural system) and its.
-
-				@ Counter-intuitively, because consciousness inhabits in interactions between agents and environments, this theory suggests that consciousness is not driven by brain activities.
-Instead, consciousness should be shaped by the way of interaction, i.e.
-SMCs, between agents and environments.
-
-				%% Our theory
-
-				@ Similar to the SMC theory, our theory predicts that the interaction between the neural system and the environment shapes the quality of conscious perception.
-
-				@ This is because to achieve NTIC the neural system should maximise the conditional mutual information between the future state of the NTIC process and the environment given the agent's current action (see equation XXX \critical{I NEED A EQUATION!}).
-
-				@ This suggests the to maximise NTIC the NTIC process needs to involve the information about the environmental transition and dynamic after agent preforms an action.
-
-				@ Therefore, as a consequence of maximising NTIC, the representation forming NTIC implicitly encodes information about SMCs.
-
-				@ In the long-term, once NTIC neural dynamic interoperates the environmental state transition given actions via maximising NTIC, the state space of XXX then is shaped by the new learned SMC
-
-				@ Accordingly, the way how the agent interacts with the environment influences the structure of the NTIC representation.
-
-				@ \todo{Need to involve some sentence from  }
-
-				@ \idea{Do I need a figure here?}
-
-				@ However, in contrast to the SMC theory, our theory suggests the state of NTIC process correlate conscious contents.
-Therefore, if the NTIC process is formed inside the neural system, we should have correspondent conscious contents in our conscious experience without interacting with the environment.
-
-				@ \idea{Not sure here} This can easily explain that the conscious experience of dream is just induced by self-evolved state changes of the NTIC process.
-
-				@ Further more the SMC and our theories make complete different prediction about the relationship between SMC and consciousness.
-
-				@ Contrary to the SMC theory which suggests that consciousness resides on SMCs, our theory predicts that pure S-R contingency between the neural system and the environment can not achieve informational closure within the neural system and therefore is not conscious (please see section \ref{sec:reflexive})
-
-			\end{ants}
-
-			\begin{WritingMaterials} % materials
-
-				%% Intro about this theory
-				@ O’Regan and Noë
-
-				@ \rewrite{According to Noë, perceptual presence is explained by a “ sensorimotor theory ” on which perception depends on a practical mastery of sensorimotor dependencies or “ sensorimotor contingencies ” (SMCs) (O ’ Regan \& Noë, 2001).
-The theory inherits from Gibsonian notions of “ affordances ” (Gibson, 1979) and from enactive cognitive science (Thompson \& Varela, 2001) which stress the importance of brain-body-world interactions in cognitive processes.
-On sensorimotor theory, the perception of a tomato as a (perceptually present, real, subjectively veridical) tomato is given by practical mastery of the SMCs governing how the sensory responses elicited by the tomato will behave in a variety of situations.
-A strong point of this theory is that it suggests why there are differences in qualitative character between modalities, the reason being that different modalities instantiate different SMCs (O ’ Regan \& Noë, 2001).
-}
-
-				@ In their seminal article O’Regan and Noë (2001) introduce sensorimotor contingencies (SMCs) as the basis of a sensorimotor account of conscious perception.
-
-				@ In short, different types of SMCs give rise to different qualities of sensory experience
-
-				@  Second, vision, audition, touch, etc., correspond to domains of knowledge of the respective SMCs that are exercised by an agent as part of its habitual behavior.This ‘‘mastery of SMCs’’ is what lets an agent perceive its environment and adapt its behavior accordingly
-
-				@ And third, sensory awareness arises when SMCs are integrated with planning, reasoning, and generation of behavior
-
-				@ The theory is a radical departure from the classical view that the brain constructs an internal representation of the outside world on which higher cognitive processes such as memorizing, reasoning, and planning operat
-
-				@ perception depends on a practical mastery of sensorimotor dependencies or “sensorimotor contingencies” (SMCs)
-
-				@ s the importance of brain-body-world interactions in cognitive processes.
-On sensorimotor theory, the perception of a tomato as a (perceptually present, real, subjectively veridical) tomato is given by practical mastery of the SMCs governing how the sensory responses elicited by the tomato will behave in a variety of situations.
-
-				@ ways of acting or as something we do, rather than an internal phenomenal experience or an internal representation of the world (O’Regan \& Noë, 2001)
-
-				@ \rewrite{I advance this truly astonishing hypothesis: To understand consciousness in humans and animals, we must look not inward, into the recesses of our insides; rather, we need to look to the ways in which each of us, as a whole animal, carries on the processes of living in and with and in response to the world around us .
-.
-.
-You are not your brain .
-.
-.
-Meaningful thought arises only for the whole animal dynamically engaged with its environment .
-.
-.
-And indeed the same is true for the quality of our conscious episodes .
-.
-.
-The taste of licorice is not something that happens in our brains.} (Noë, 2009, pp.
-7–8)
-
-				@ Because consciousness resides in our behavioural interactions with the world rather than in our brain, the theory postulates that consciousness does not derive from brain activity at all.
-Consequently, there is no need to explain how brain activity causes or constitutes consciousness, because it does not.
-
-				@ O ’ Regan, J.K. and Noë, A. (2001) A sensorimotor account of vision and visual consciousness. Behav. Brain Sci. 24, 939 – 973
-
-				@ SMC theory argues that consciousness arises from the execution of SMCs, resulting in brain – environmental interactions.
-
-				@ The second variant of SMC theory postulates that ‘ it is not movement as such, but the consequences of potential movement that play a role ’ (in perceptual experience) ([5], p.
-1015; see also [9,10,19,20]).
-This ‘ non-acute ’ or dispositional variant marks a signi fi cant shift in position because it de-emphasizes actual movement.
-\cite{pennartz2017consciousness}
-
-				@ It stipulates that for us to be conscious of something in the environment (or of our way of interacting with the environment)
-
-			\end{WritingMaterials}
-
-		\subsection{Predictive Processing}
-			\begin{ants}
-				%% Introduce PP
-				@ The predictive processing is a powerful framework (PP) which integrates several influential ideas in the history of neuroscience including "perception as unconscious inference" from Helmholtz \citet{helmholtz1866concerning}, "analysis by synthesis", “predictive coding”, "Bayesian brain hypothesis"
-
-				@ is a powerful framework
-
-				@ a recent emerged theoretical framework of perception and brain function, which suggests that the brain continuously generates and updates predictions about incoming sensory signals, represents a general principle of neural functioning.
-
-				@ According to predictive processing (PP) account of perception, the neural system constantly performs unconscious statistical inference about hidden causes in the external environment.
-The perceptual contents are the "best guess" about the environment 	\cite{clark_2013}			\cite{Hohwy2013}
-
-				@ Bperceptual content is the result of probabilistic inference on the hidden causes of sensory signals.
-
-				@ Because it is well integrated with Bayesian brain hypothesis, the PP framework has been used to interpret conscious perception in many perceptual domain. \cite{Hohwy2013} \cite{SethPP2014}
-
-				%% The gaps between pp and consciousness
-				@ However, to link PP to consciousness, there are still two major gaps.
-
-					@@ First, previous studies have demonstrated many brain processes following the principle of Bayesian inference and Bayesian integration.
-But not all these processes are conscious.
-This indicates that PP is not a sufficient mechanism for conscious perception.
-Some other factors may be involved to determine which PPs can be conscious or not.
-
-					@@ Second, it has been emphasized that only the results of the inference or prediction can be consciously accessed. The process of inference in completely unconscious. So WHY?
-
-				@ Even though PP has been acquiring attention in different discipline in neuroscience, So far, to our knowledge, no detailed explanation has been given to account for the two questions.
-
-				%% Our theory
-
-				% 2018/06/15 15:10
-				@ We first hypothesize that predictive processing stays unconscious is because it is not able to achieve NTIC.
-
-					@@ \idea{Example from PID controller?}
-
-				@ Second, according to our theory, it is obvious that the computation of predictive processing is unconscious and only the result is conscious.
-Because the computational details is not at the coarse-grained level which achieves NTIC.
-
-					@@ So far, many neuronal models and coding schema have been proposed to explain how to implement Bayesian inference and prediction at the neuronal level.
-
-					@@ However?
-
-				@ We hypothesize that the distinction between conscious and unconscious predictive mechanisms is whether they build up on the information from the NTIC process.
-
-			\end{ants}
-
-			\begin{WritingMaterials}
-
-				%% About the unconscious Bayesian processing
-				@ \cite{lamme2015predictive}
-					@@ To my knowledge, this is the first time this has been so explicitly laid out—writers on predictive coding thus far have always stayed a little vague on where exactly consciousness sits in the Bayesian framework.
-
-					@@ Yet the two points seem contradictory. In the Bayesian predictive coding framework, consciousness is the result of the unconscious inferential processes.
-
-					@@ However, these authors have so far been very reticent about how exactly consciousness fits into the PC framework.
-For now, there is an emerging idea that understands consciousness as the final result of unconsciousness processing.
-According to Hohwy (2013), perceptual consciousness fits in the PC theory as the ‘upshot’ or ‘conclusion’ of unconscious perceptual inferences.
-Melloni (2014) also expects that inferential processes are conducted behind the curtain of consciousness and what we experience are the ‘outcomes’ or ‘results’ of an unconsciou inferential process.
-Lamme (2015) agrees with the idea that consciousness is based on the relation or more precisely conjunction of current inputs and priors, which together produce posterior beliefs.
-Karl Friston agrees to a certain extent with this interpretation of consciousness.
-According to Hobson and Friston (2016), consciousness is not a phenomenon but a process, a process of optimizing beliefs through inference (consciousness, dreams, and inference; the Cartesian theater revisited; a response to our theater critics).
-
-				@ Link PP and c
-					@@ \cite{hobson2016response}
-					@@ \cite{Melloni2015}
-
-				%% ----------------------------------------------------------------------------
-				@ \cite{SethPP2014}
-
-				@ When uncertainty is high, we should expect an increase in the ability of ever higher-level prior beliefs to determine conscious experience. I
-
-				@ determine conscious experience.
-
-				@ PP combines and builds upon previous ideas about the role of “unconscious inference” in perception (Helmholtz, 1925; Barlow, 1961; Gregory, 1970), the process of “analysis by synthesis” in psychology (Neisser, 1967), the “predictive coding” approach in neuroscience (Srinivasan et al., 1982; Rao and Ballard, 1999; Huang and Rao, 2011) and “generative models” and related probabilistic computational principles (MacKay, 1956; Mumford, 1992; Dayan et al., 1995; Hinton, 2007a,b; Tenenbaum et al., 2011).
-
-				@ \rewrite{The brain is constantly confronted with a wealth of sensory information that must be processed efficiently to facilitate appropriate reactions.
-One way of optimizing this processing effort is to predict incoming sensory information based on previous experience so that expected information is processed efficiently and resources can be allocated to novel or surprising information.
-Theoretical and computational studies led to the formulation of the predictive coding framework (Friston 2005, Hawkins and Blakeslee 2004, Mumford 1992, Rao and Ballard 1999).
-Predictive coding states that the brain continually generates models of the world based on context and information from memory to predict sensory input.
-In terms of brain processing, a predictive model is created in higher cortical areas and communicated through feedback connections to lower sensory areas.
-In contrast, feedforward connections process and project an error signal, i.e.
-the mismatch between the predicted information and the actual sensory input (Rao \& Ballard, 1999).
-The predictive model is constantly updated according to this error signal.
-}
-
-				@ \rewrite{Predictive inference and perception The concept of PC overturns classical notions of perception as a largely ‘bottom-up’ process of evidence accumulation or feature detection, proposing instead that perceptual content is specified by top-down predictive signals that emerge from hierarchically organized generative models of the causes of sensory signals.
-According to PC, the brain is continuously attempting to minimize the discrepancy or ‘prediction error’ between its inputs and its emerging models of the causes of these inputs via neural computations approximating Bayesian inference (Figure 1 and Box 1).
-Importantly, prediction errors can be minimized either by updating generative models (perceptual inference and learning; changing the model to fit the world) or by performing actions to bring about sensory states in line with predictions (active inference; changing the world to fit the model).}
-
-				@ \rewrite{In terms of brain function, Hermann von Helmholtz’s 19th Century notion of perception as unconscious inference has found new momentum in modern formulations of ‘predictive processing’, the Bayesian brain, and the ‘free energy principle’ (Clark, 2013; Friston, 2010; Hohwy, 2013).
-On these formulations, which can all be subsumed under the general term ‘prediction error minimization’ (PEM, (Hohwy, 2013)) perceptual content is the result of probabilistic inference on the hidden causes of sensory signals.
-}
-
-				@ \rewrite{Generative models encoded by brain structure and dynamics make predictions about sensory inputs, based on prior expectations.
-Action (e.g., body movements) and perception conspire to reduce sensory prediction errors, giving rise to perceptual content and}
-
-				@ \rewrite{More informally, what we perceive is the brain’s ‘best guess’ of what’s out there (or ‘in here’, for perceptions of body and self).}
-
-				@ \rewrite{“ predictive processing ” (PP) 1 or the “ Bayesian brain ” this holds that perceptual content is determined by hierarchically organized generative (i.e., predictive) models (HGMs) of the external causes of sensory signals, induced by a process approximating Bayesian inference (Friston, 2009).}
-
-				@ Not all predictive mechanism are conscious.
-
-				@ We hypothesize that the distinction between conscious and unconscious predictive mechanisms is whether they build up on the information from the NTIC process.
-
-				@ we can also explain why only the result (posterior) of predictive processing is conscious.
-
-				@ Because of this XXXX, the representation has the maximal \ac{ntic} also has the maximal predictive power of the external environment. \todo[inline]{I need math here!!}
-
-				@ Therefore, it's reasonably assume that if evolution wants to build predictive mechanisms, the mechanisms should be settled on the information at the \ac{cged} level.
-
-				@ More specifically, a forward model, which received state and action as input and compute transition and then output next states, should be build on the representation that forms the \acl{ic}.
-
-				@ Therefore, the state of predictive model can be conscious while it is linked to \acl{ic} representation.
-
-				@ Note that, a system showing some predictive power is not sufficient to be conscious.
-
-				@ For example, the proportional–integral–derivative controller (PID) controller shows predictive behaviours due to its derivative which computes and predict error value in the future.
-Derivative action predicts system behaviour and thus improves settling time and stability of the system.
-
-				@ However, the state of the whole PID system still be determined by the inputs, i.e. the states of the controlled process, thus cannot complete \acl{ic}.
-
-				.
-It can compute position, velocity, and acceleration of objects, and output control signals (action).
-However, the state of the PID controller is not information-closed.
-The state still fully determined by the input signals.
-Therefore, it fails to reach \ac{ic}.
-Hence, according to our theory, the PID system is not conscious.
-
-				@ Similarly, the neural system also has many circuits that show predictive power but do not have \ac{ic}.
-
-			\end{WritingMaterials}
-
-			\subsubsection{statistical learning/prediction is not conscious}
-				\begin{ants}
-					@ considers the brain as a predictive machine
-					@ According to predictive processing account, conscious contents are the inference results (posterior from Bayesian inference framework) of predictive mechanism.
-
-					@ However, we can see that not all predictive mechanisms in the neural system can be consciously aware of.
-
-					@ So what's the critical difference between them in terms of consciousness?
-
-					@ We argue that when predictive mechanisms utilise the information in the informational closure, the predictive result is conscious.
-
-					@ Because the forward model build on the informational closure representation can be seen as part of the closure. \critical{IS THIS TRUE? NEED DISCUSSION}
-
-					@ we can consider two scenarios
-
-						@@ Predictive information is encoded in neuron populations but there is high entropy of conditional probability which means it's not closure.
-Therefore, the conscious level could be very low even though the it still has some degree of predictability.
-
-						@@ Another scenario is a forward model but its state fully depends on external sensory input. This system is not informational closured and therefore is not conscious.
-
-						@@ Based on this point of view, predictive power for a system does not guarantee consciousness.
-
-						@@ For example, in active inference \needref{active inference}, action is guided by prediction error so the state of the system is non-closured.
-
-				\end{ants}
-
-\rlstart{1}
-		\subsection{Integrated information theory}
-			\begin{ants}
-
-			@ One common principle between our theory and IIT is that instead of NCC, both theories suggest information is the fundamental entity which correlates consciousness. \needref{cite David Chalmers}
-
-			@ Our theory is different from IIT which proposes that consciousness is information integration in a system.
-
-			@ For level of consciousness, IIT predicts a system with higher level of integration produces a higher level of consciousness.
-In our theory, the level of consciousness corresponds to the level of NTIC, which suggests that level of consciousness is determined by self-predictive information and the information about the environment encoded in the process.
-
-			@ In terms of conscious content, IIT suggests that the causal structure of a system determines the quality of conscious contents.
-In the current version of our theory, how the state of NTIC process maps to conscious content has not been sophisticatedly specified.
-More work is needed to understand the relationship between the state of NTIC process and conscious contents.
-
-		    @ --------------------------------------------------------------------
-			@ \toWrite{Information integration without awareness}\cite{Mudrik_Faivre_Koch}
-			@ \rewrite{consciousness is necessary for high-level but not low-level semantic integration}\cite{Mudrik_Faivre_Koch} we would argue an inverse relationship:"High-level information processing is necessary for consciousness." This is because higher-level information processing is more likely to create an informational closure representation.
-
-			@ Similarly, it is not \rewrite{consciousness is necessary for multisensory integration}.
-It should be multisensory integration is more likely to create an informational closure representation.
-Because in most situations, multisensory signals are generated from hidden causes which may have deterministic dynamic and relation with each other.
-Therefore, to infer the hidden causes and represent the deterministic relations can form informational closure representation which is conscious.
-
-			\end{ants}
-
-			\subsubsection{Hoel's theory\needhelp{Help from Martin?}}
-				\ideaBox{This is very important. Need to be careful here.}
-
-				\begin{ants}
-
-				    @ Our theory is closely related to causal emergence described by Hoel et al.
-(2013) which was examined by a following work using integrated information theory (Hoel et al.
-2016).
-More research on the precise mathematical relationship between causal emergence and our theory is needed
-
-					@ \cite{hoel2016can}
-					@ causal emergence
-					@ \cite{hoel2013quantifying} examined causal power at different coarse-grained scale and show that causal power can be stronger at macro rather than micro levels.
-
-					@ To answer the question about what is the best scale to compute Phi, \cite{hoel2016can} examined causal power at different coarse-grained scale.
-
-					@ Further instigation is needed to elucidate the relationship between our theory and causal emergence
-
-				\end{ants}
-
-\rlend
-
-		\subsection{Internal simulation and self-modelling theory}
-
-    \section{Limitation}
-
 \subsection{Finding potential coarse-graining functions}
@@
 
-            @
+        % about the coarse-graining function (aggregation function) 
+        @ \cite{PFANTE.2014}, the authors discuss the the implications of the types of aggregation function (deterministic or probabilistic) and its relationship with macroscopic processes.
+If the macroscopic process: \rewrite{Furthermore, we could prove that observational commutativity forces the aggregation to be deterministic if the upper process is invertible, i.e., ψ is invertible, and in the case of a soft (i.e., probabilistic) aggregation the third idea of commutativity really differs from the one of observational commutativity.
+}
 
@@
     \end{ants}
-
-	\section{Future works}
-		\begin{ants}
-
-			@ Lack of direct evidence because no one focus on informational closure.
-
-			@ Physiological location of NTIC
-
-			@ Practical measure of NTIC.
-
-		\end{ants}
-
-		\subsection{Finding coarse-grain function}
-			\begin{ants}
-				@ It's not clear what the coarse-graining function is.\critical{this should be explained by environmental deterministic}
-
-				@ \rewrite{
-					not all causal relationships (or relationships of nomological dependency) among micro-events aggregate up to causal relationships among coarse-grained macro-events that are constituted by those micro-events.
-Instead, whether one gets causation at the macroscopic level will depend (among other things) on the particular coarse-graining that is chosen.} \cite{price2007causation}
-
-				@ \rewrite{
-					It may seem surprising, even counterintuitive, that causal and statistical dependence relationships involving fine grained microscopic variables do not automatically show up in causal and dependence relationships among the macroscopic variables that are realized by the fine grained variables.} \cite{price2007causation}
-
-				@ \cite{jonas2017could} well demonstrated that it is difficult to understand higher-level information processing by the current neuroscience methods.
-
-			\end{ants}
-
-%	\section{Evolution of conscious mind (not sure but if I have time)}
-%		\cite{dennett2008kinds}
-
-	\section{Conclusion}
-		\begin{ants}
-			@ Why is this theory better than other theories of consciousness
-			@ NCC: To find NCC, it's not about where and when, it's about scale and level of description
-		\end{ants}
-
-	% ============================================================================ %
-	%                                      End                                     %
-	% ============================================================================ %
-
-	\section*{Funding}
-
-	\section*{Acknowledgements}
-
-	\section*{Supplemental Data}
-
-	\bibliographystyle{authordate1}
-	\bibliography{ref}
-
-\newpage
-\begin{backup}
-\part*{Backup}
-\addcontentsline{toc}{part}{Backup}
-\setcounter{section}{0}
-	\section*{Biological evidence of informational closure in neural system}
-		\begin{ants}
-			% ============================================================================ %
-			%                             sederberg2018learning                            %
-			% ============================================================================ %
-
-			@ So far, not so much research on non-trivial informational closure in biological neural systems.
-
-			@ However, \rewording{XXX}
-
-			% Internal self-predictive mechanism
-			@ Recent biological evidence suggests that low-level neurons encodes predictive information about external  and
-
-			@ \toWrite{
-				need to say this is exactly the non-trivial informational closure, and refer to equation XXX}
-
-			@ \cite{sederberg2018learning}
-			@ \rewrite{
-				in recordings of populations of RGCs of salamander retina driven by a simple stimulus with partially predictable dynamics, joint activity patterns transmit information that is predictive of future stimuli }
-
-			@ \rewrite{
-				We examined whether the temporal correlations within populations of RGCs can be used to guide the search for readouts of predictive information.}
-
-			@ \rewrite{
-				We showed that groups of cells with high external, stimulus-predictive information also had high internal predictive information on two classes of stimuli, }
-
-			@ \rewrite{
-				Very simple learning rules could find near-optimal readouts of predictive information without any external instructive signal.
-This suggests that bottom-up prediction may play an important role in sensory processing}
-
-			@ \rewrite{
-				Internal predictive information can guide stimulus prediction without explicit reference to stimulus parameters.}
-
-			@ \rewrite{
-				Word–word internal predictive information is correlated with word–stimulus predictive information across sets of four cells.}
-
-			@ They also showed generalization of internal predictability across stimulus. This suggests .... what?
-
-			@ \rewrite{
-				The generalization of internal predictability across stimulus classes partially reflects the ability of the retina to adapt to the statistics of stimuli}
-
-			@ \cite{Palmer2015}
-			@ \rewrite{
-				Groups of cells in the retina carry information about the future state of their own activity, and we show that this information can be compressed further and encoded by downstream predictor neurons that exhibit feature selectivity that would support predictive computations.}
-
-			@ \rewrite{
-				It seems natural to phrase the problem of prediction in relation to the visual stimulus, as in Fig.
-3, but the brain has no direct access to visual stimuli except that provided by the retina.
-Could the brain learn, in an unsupervised fashion, to predict the future of retinal outputs?
-More precisely, if we observe that a population of retinal ganglion cells generates the word w t at time t, what can we say about the word that will be generated at time t + delta t in the future?
-The answer to this question is contained in the conditional distribution of one word on the other, P ð w t +delta t j w t Þ } \url{http://tinyurl.com/y9zmhlln}
-
-			@ \rewrite{
-				larger groups of cells carry predictive information for hundreds of milliseconds, }
-
-		\end{ants}
-
-	\section*{Relation to empirical findings in neuroscience and studies of consciousness}
-
-		\subsection{Unconscious Processing}
-		\begin{ants}
-			@ According the theory, there are two factor that renders neural processes unconscious.
-
-			@ First, processes are reflexive. This causes non-closured
-
-			@ Second, the abstraction level of the information is below the non-trivial informational closure scale.
-		\end{ants}
-
-		\subsection{reflexive behaviours is unconscious (or environment-state dependent processes)}\label{sec:reflexive}
-		\subsubsection{Reflection}
-		\begin{ants}
-			@ Reflexive systems is not informational closured.
-			@ Base	d on our theory,
-			@ x -> s -> a
-			@@ the system state is determined by environmental state, then it is not conscious.
-			@ Therefore, in general, a simple policy network is not conscious.
-		\end{ants}
-
-		\subsubsection{Blindsight}
-		\begin{ants}
-			@ This also blindsight.
-			@ Blindsight patients and still make above chance judgement without conscious awareness of visual targets.
-			@ The stimulus-reaction policy network still intact, but it cannot form informational closure and therefore, patients has no conscious awareness of visual  targets
-			@ Patient B.F. reactions are stimulus driven.
-		\end{ants}
-
-		\subsubsection{procedure memory}
-
-		\subsubsection{cerebellum}
-		\begin{ants}
-			@ cerebellum feed-forward connections, maybe just a policy network.\needref{cerebellum}
-		\end{ants}
-
-		\subsection{Under the level of informational closure}
-		\subsubsection{statistical inference}
-		\begin{ants}
-			@ The computation of Bayesian brain is unconscious.
-		\end{ants}
-
-		\subsubsection{subliminal perception}
-		\begin{ants}
-			@ Above chance performance can be performed through non-closure pathway (reflexive behaviours)
-
-			@ Due to coarse-graining, mapping between changes of microstate
-		\end{ants}
-		\subsubsection{Libet Experiments}
-
-		\subsection{Deterministic vs probabilistic}
-		\cite{dehaene2017consciousness}
-		\cite{vul2008temporal, moreno2011bayesian, asplund2014attentional, vul2009attention}
-
-	\section*{About Phenomenology (conscious processing)}
-\subsection{Perceptual overflow}
-\subsection{Volition and freewill}
-\begin{ants}
-	@ Volition is a result of coarse-graining
-
-	@ Lebel's experiment can be well explained by the experiment.
-\end{ants}
-
-\subsection{Planning}
-\subsection{Imagination}
-\subsection{Dream vs non-dream sleep}
-\subsection{Binocular rivalry}
-\subsection{Hallucinations}
-\subsection{Synaesthesia}
-
-	\section*{Theory predictions (Counter-intuitive prediction)}
-
-\subsection{informational closure}
-\begin{ants}
-	@ We predict that through coarse-graining, conscious agents create
-\end{ants}
-
-\subsection{Prediction on split-brain (vs IIT)}
-* IIT suggests that cutting, two subparts may both still have MIP, therefore, have two conscious mind.
-
-* However, our theory suggests that if the cut largely destroy the \ac{ic}, then both part may not be conscious.
-
-\end{backup}
-
-\end{document}

### 2019-06-04 Paper_neural_coarse_graining_of_consciousness.tex
Updates from Overleaf

@@
 \documentclass[utf8]{article}
-
-%% Language and font encoding
-\usepackage[english]{babel}
-%\usepackage[utf8]{inputenc}
-\usepackage[T1]{fontenc}
-
-%% Sets page size and margins
-%\usepackage[a4paper, top=3cm,bottom=2cm,left=3cm,right=3cm,marginparwidth=4cm]{geometry}
-\usepackage[papersize={10in, 12in}, top=3cm,bottom=2cm,left=2in,right=2in,marginparwidth=1.8in]{geometry}
-
-%% Title style
-\usepackage{stringstrings}
-\usepackage[explicit]{titlesec}
-\usepackage{sectsty}
-
-%% ============================== Useful packages ============================= %
-\usepackage[dvipsnames,table,xcdraw]{xcolor}
-\usepackage[round]{natbib}
-\usepackage{amsmath}
-\usepackage{graphicx}
-\usepackage{svg}
-\usepackage[colorlinks=true, allcolors=blue]{hyperref}
-\usepackage{authblk}
-\usepackage{float}
-\usepackage{tikz}
-
-%% ================================== acronym ================================= %
-\usepackage{acronym}
-\newacro{ntic}{non-trivial informational closure}
-\newacro{ic}{informational closure}
-\newacro{cg}{coarse-grain}
-\newacro{cging}{coarse-graining}
-\newacro{cged}{coarse-grained}
-\newacro{ncg}{neural coarse-graining}
-
-% The name of our theory
-% ----------------------------------------------------------------------------
-\newcommand{\tnamefull}{The Neural Coarse-graining Theory of Consciousness}
-\newcommand{\tname}{NCGT} 	% TheoryNameShort
-\newacro{\tname}{\tnamefull}
-%\newacro{NCGT}{the neural coarse-graining theory of consciousness}
-
-% =================================== Macro ================================== %
-\usepackage[colorinlistoftodos]{todonotes}
-\usepackage[at]{easylist}
-\usepackage{tcolorbox}
-\tcbuselibrary{skins}
-\usepackage{comment}
-\usepackage[framemethod=tikz]{mdframed}
-\usetikzlibrary{shadows}
-\usepackage{soul}
-\usepackage{version}
-
-% Meaning of colours --------------------------------------------------------- %
-%	Red: Important and Critical
-%	Orange: Todo
-%	Blue: Topic and Guideline
-%	Purple: Murmur
-%	Green: Question, Call for help, Open for opinions and comments
-%	Brown: Need Wording
-% ---------------------------------------------------------------------------- %
-
-% Real content
-	% Outline items that can be integrated into main text
-		\newenvironment{ants}
-			{
-			 \begin{easylist}[itemize]
-		 	}
-			{
-			\end{easylist}
-			} %
-
-	% Writing Materials
-    \newenvironment{WritingMaterials} %
-    	{
-            \begin{tcolorbox}[enhanced,
-                title=-,
-                size=small,
-                colbacktitle=Aquamarine,
-                drop fuzzy shadow,
-                fontupper=\small,
-                boxrule=0.4pt,
-                colback=Aquamarine!10!white,
-                sharp corners]
-                Writing Materials
-            \end{tcolorbox}
-            \begin{easylist}[itemize]
-    	}
-    	{
-            \end{easylist}  
-            \begin{tcolorbox}[enhanced,
-                halign=flush right,
-                halign title=right,
-                size=small,
-                colbacktitle=Aquamarine,
-                drop fuzzy shadow,
-                fontupper=\small,
-                boxrule=0.4pt,
-                colback=Aquamarine,
-                colupper=White,
-                sharp corners]
-                Writing Materials -
-            \end{tcolorbox}        
-    	}
-
-    % \excludeversion{WritingMaterials}
-
-% Functional content
-	% Quotes: green
-		\newcommand{\rewrite}[1]{\textcolor{ForestGreen}{\textit{"#1"}}\newline}
-
-	% todo: orange
-		% text todo
-		\newcommand{\toWrite}[1]{\noindent
-			\textcolor{Orange}{\textbf{[[ #1 ]]}}}
-
-	% figure todo
-        \newcommand{\includegraphicsTodo}[2][]{%
-            \tcbox[enhanced,
-                center,
-            	adjusted title=\large To Be Modified ...,
-            	halign title=center,
-            	attach boxed title to top left={yshift=-3mm, xshift=1cm,yshifttext=-1mm}, boxed title style={drop fuzzy shadow},
-            	colbacktitle=RedOrange!70!black,
-            	coltitle=white,
-            	colframe=RedOrange!50!black,
-            	colback=white
-        	]{\includegraphics[#1]{#2}}}
-
-		% figure todo callout
-        \newcommand{\needfig}[1]{%
-			\ifthenelse{\equal{#1}{}}{%
-				\todo[color=White, linecolor=Orange, bordercolor=RedOrange]{\textcolor{RedOrange}{Fig}}}{%
-				\todo[color=White, linecolor=Orange, bordercolor=RedOrange]{\textcolor{RedOrange}{Fig: #1}}%
-			}%
-		}
-
-		% rewording
-		\newcommand{\rewording}[1]{\textcolor{RawSienna}{[[ REWORDING | #1 ]]}}
-
-		% Need reference
-		\newcommand{\needref}[1]{%
-			\ifthenelse{\equal{#1}{}}{%
-				\todo[color=White, linecolor=Orange, bordercolor=Orange]{\textcolor{Orange}{Ref}}}{%
-				\todo[color=White, linecolor=Orange, bordercolor=Orange]{\textcolor{Orange}{Ref: #1}}%
-			}%
-		}
-
-	% Highlight: Yellow or Red
-		% Highlight only
-		\newcommand{\highlight}[2][Yellow]{\sethlcolor{#1}\hl{#2}}
-
-		% Highlight and comment
-        \newcommand{\highlightAndComment}[3][Yellow]{\sethlcolor{#1}\hl{#2}\todo[color=#1, linecolor=Yellow]{#3}}
-
-		% Critical point
-		\newcommand{\critical}[1]{%
-			\todo[color=OrangeRed!80!white]{#1}
-		}
-
-	% idea: Purple
-		% text idea
-			\newcommand{\idea}[2][Plum]{\noindent
-				\textcolor{#1}{[[ #2 ]]}}
-
-		% box idea
-			\newcommand{\ideaBox}[1]{
-			    \vspace{2mm}
-				\begin{tcolorbox}[enhanced,%
-                    title=-,
-                    center,
-                    fontupper=\small,
-                    lifted shadow={1mm}{-2mm}{3mm}{0.1mm}{black!50!white},%
-                    boxrule=0.4pt,
-                    width=9cm,
-                    colback=Thistle!50!white,
-                    sharp corners]
-					#1
-				\end{tcolorbox}
-				\vspace{2mm}
-			}
-
-		% call-out idea
-			\newcommand{\ideaCallout}[1]{\todo[color=Thistle!50!white, size=\small]{#1}}
-
-	% communication: green
-		% call for help
-			\newcommand{\needhelp}[1]{\todo[color=SpringGreen]{[Need Help]: #1}}
-
-		% comment
-			% comment by authors
-			\newcommand{\addcomment}[3][\empty]{\todo[color=SkyBlue]{Comment [#2]:\newline#3}\colorbox{SkyBlue}{#1}}
-
-			% usage:
-			% \addcomment{auther}{comment text}
-			% or
-			% \addcomment[highlighted text]{auther}{comment text}
-			%
-			% e.g.
-			% It's a \addcomment[beautiful]{Acer}{need a reference} day
-
-    % backup: 
-    \newenvironment{backup}
-    {
-
-        \begin{tcolorbox}[enhanced,
-            title=-,
-            size=small,
-            colbacktitle=black!70!white,
-            colback=black!10!white,            
-            drop fuzzy shadow,
-            fontupper=\small,
-            boxrule=0.4pt,
-            sharp corners]
-            Backup
-        \end{tcolorbox}
-    }
-    {
-        \begin{tcolorbox}[enhanced,
-            halign=flush right,
-            halign title=right,
-            size=small,
-            colbacktitle=black!10!white,
-            colback=black!70!white,
-            drop fuzzy shadow,
-            fontupper=\small,
-            boxrule=0.4pt,
-            colupper=White,
-            sharp corners]
-            Backup -
-        \end{tcolorbox}    
-    }
-    % \excludeversion{backup}
-
-% review loop annotation
-    \usepackage[xcolor, outerbars]{changebar}
-    \cbcolor{red}
-
-    % start anchor: \rlstart
-    \newcommand{\rlstart}[1]{  %
-        \setlength\changebarwidth{#1pt*2}  %
-        \hspace*{-40pt}
-        \cbstart{\textcolor{red}{\newline\textbf{iteration #1}}\newline}}
-
-    % end anchor: \rlend
-    \newcommand{\rlend}{\cbend}
-
-% quote
-\newcommand{\myQuote}[1]{\textit{``#1''}}
+\usepackage{import}
+\usepackage{WritingToolsByAcer}
 
@@
             @ variable? node? element? member?
+            @ TODO:
+                @@ Change coarse-graining function to "aggregation function"
         \end{ants}
@@
 		\begin{figure}[H]
-			\includegraphicsTodo[width=\textwidth/2]{WritingMaterials/PDFXCview_2018-06-11_13-37-34.png}
+			\includegraphicsTodo[width=\textwidth/2]{WritingMaterials/Fig_temp/PDFXCview_2018-06-11_13-37-34.png}
 			\cite{pennartz2017consciousness}
@@
 				\begin{figure}
-					\includegraphics[width=\textwidth]{WritingMaterials/SystemAndEnv.pdf}
+					\includegraphics[width=\textwidth]{WritingMaterials/Fig_SystemAndEnv/SystemAndEnv.pdf}
 					\caption{Figure adapted from \cite{BERTSCHINGER.2006}}
@@
 			\begin{figure}[H]
-				\includegraphicsTodo[width=\textwidth]{WritingMaterials/Palmer2015.png}
+				\includegraphicsTodo[width=\textwidth]{WritingMaterials/Fig_temp/Palmer2015.png}
 				\caption{Figure adapted from \cite{sederberg2018learning}}
@@
 		\begin{figure}
-			\includegraphicsTodo[width=0.8\textwidth]{WritingMaterials/PDFXCview_2018-06-08_14-24-03.png}
+			\includegraphicsTodo[width=0.8\textwidth]{WritingMaterials/Fig_temp/PDFXCview_2018-06-08_14-24-03.png}
 			\caption{NCG \idea{I need to simplify this figure}\citep{guttenberg2016neural}}
@@
 						Neural population code: the set of response features of a population of neurons that carry all information about the considered stimuli.
-These features consist of spatio-temporal sequences of action potentials distributed across neurons and/or time.}
+These features consist of spatial-temporal sequences of action potentials distributed across neurons and/or time.}
 
@@
 
+% ============================================================================ %
+%               A neural coarse graining theory of consciousness               %
+% ============================================================================ %
 	\section{A neural coarse graining theory of consciousness}
@@
 				\begin{figure}[H]				
-				\includegraphics[width=\textwidth]{WritingMaterials/FoxitReader_2019-01-31_19-03-59.png}
+				\includegraphics[width=\textwidth]{WritingMaterials/Fig_temp/FoxitReader_2019-01-31_19-03-59.png}
 				\label{fig:LevelOfConsciousness}
@@
 			\begin{figure}[H]
-				\includegraphics[width=\textwidth]{WritingMaterials/SeperationOfCGandCortHierachy.pdf}
+				\includegraphics[width=\textwidth]{WritingMaterials/Fig_SeperationOfCGandCortHierachy/SeperationOfCGandCortHierachy.pdf}
 				\label{fig:hierarchy}
@@
 
-	\section{Conscious versus Unconscious Processing}
-		\ideaBox{The goal of this part is to combine empirical study and phenomenology}
-	    \ideaBox{I need to expend this section much more and more references}
-	    In this section, we suggest that our theory has a strong exploratory and predictive power but with minimal assumptions.  
-		Our theory indicates that, to make information conscious, a sufficient and a necessary conditions need to be satisfied.
+% ============================================================================ %
+%                    Conscious versus Unconscious Processing                   %
+% ============================================================================ %
+	\section{Conscious versus Unconscious Processing}\label{sec:Conscious versus Unconscious Processing}
+	    In this section, we show how our theory can explain and predict whether a process is conscious or unconscious.
+Our theory is based on minimal assumptions.
+Nonetheless, it demonstrates a strong exploratory and predictive power about the relationship between information processing in the neural system and conscious experience.
+
+		Our theory argues that, to make information conscious, a sufficient and a necessary conditions need to be satisfied.
 
@@
 
-		Take the neural system as an example, our theory can well explain previous empirical findings in consciousness science and further make strong and more precise predictions for future studies.
-In the following, we discussed the implication of the two necessary conditions with respect to the empirical data in the literature of consciousness.
-
+        We especially highlight the second condition because it is critically related to many empirical research results even though it is only a necessary condition.
+As we will describe in the followings, this theory can well explain enormous previous findings in consciousness science and further make strong predictions for future research.
+In this section, we discuss how the two informational-based conditions link to conscious experience.
+
+        % ---------------------------------------------------------------------------- %
+        %                            Unconscious Processing                            %
+        % ---------------------------------------------------------------------------- %
         \subsection{Unconscious Processing}
 
-        \subsubsection{Fail to meet 1\lowercase{st} condition}
-\rlstart{4}        	
-            As described above, if a process fails to fulfil either of the two conditions, information remains unconscious.
-First, We consider that a process fails to satisfy the first condition, i.e.
-the process fails to achieve NTIC.
-Many processes in the neural system fall into this category.
-
-        	Considering the objectives of achieving NTIC (Equation \ref{eq:nticObjective}), if a process fails to maximise $I(Y_{t+1};Y_{t})$ or minimise $I(Y_{t+1};Y_{t}|E_{t})$, this results in low NTIC.
-The failure to maximise $I(Y_{t+1};Y_{t})$ implies the past states has small influence on its future states.
-In the meantime, if the process still receives environmental information and produces outputs, the future state of the process is largely determined by the past environmental states (fig.\ref{Fig:reflexive}), i.e.
-the process is not informational closed (${J_{t}(E \rightarrow Y )} \not\approx 0$).
+        \subsubsection*{Fail to meet the 1\lowercase{st} condition}
+            If a process fails to fulfil either of the two conditions, information remains unconscious.
+We first consider the scenario that a process fails to satisfy the first condition, i.e.
+the process fails to achieve high degree of NTIC.
+In the neural system many processes fall into this category.
+
+        	Considering the objectives of achieving NTIC (Eq.
+\ref{eq:nticObjective}), if a process is unable to maximise the mutual information between its past and future states ($I(Y_{t+1};Y_{t})$), it results in low NTIC.
+The failure to maximise the mutual information implies the past states of the process itself has little influence on its future states.
+In the meantime, if environmental information is able to flow into the process, the process can still produces functional outputs based on the current state of the environment accordingly.
+However, in this circumstance, the future state of the process is largely determined by the environmental states.
+That is, the process is not informational closed (${J_{t}(E \rightarrow Y )} \not\approx 0$, Fig.\ref{fig:reflexive}).
+
+            % or minimise $I(Y_{t+1};Y_{t}|E_{t})$
 
@@
 
-            In the context of information processing in the neural system, regarding to perception, this indicates that the perceptual processes only passively responds to the sensory inputs.
-Regarding to action, this indicates that the process only produces reflective-like behaviour.
-Reflexive behaviours are commonly considered as automatic and non-conscious behavioural controls.
-\citep{casali2013theoretically}\needref{More referene}.
-We hypothesise that this is a natural consequence when a process fails to meet the first condition.
-
-            The same notion can be applied to blindsight and procedure memory \needref{blindsight}.
-            Blindsight patients are able to track objects, avoid obstacles,and make above chance level judgements without conscious awareness of visual targets within the visual field without having any visual conscious experience.
-The direct stimulus-response mapping ($S\rightarrow{}R$) makes the internal neural circuit a non-NTIC process and results in unconscious processing.
-In the case of procedure memory, processes often relies on both the current environmental and system states to determine the next state of the processes\needref{Do I need ref??}.
-Therefore, they also fail to achieve high NTIC as well.
-
-             This is similar to the model-free policy-based agents in the reinforcement learning framework.
-The process of a system only maps the input state space to the action state space \needref{11}.
+            In the neural system, this type of processes, for perception, shows the property that the perceptual processing mainly passively responds to the sensory inputs.
+For actions, this type of processes only produces "reflective-like" behaviours.
+Reflexive behaviours are commonly considered as automatic and non-conscious behavioural controls \citep{casali2013theoretically}\needref{More referene}.
+We argue that information carried by this type of processes is unconscious due to its failure of achieving high NTIC, i.e., the first condition.
+
+            The same principle can be applied to blindsight and procedure memory \needref{blindsight} which are often considered as unconscious processing.
+Blindsight patients are able to track objects, avoid obstacles, and make above chance-level judgements without having any conscious perception about visual stimuli.
+We believe that these behaviours can be guided by direct stimulus-response mappings ($S\rightarrow{}R$).
+However, the direct $S\rightarrow{}R$ mappings also lead to non-NTIC neural processes  and, therefore, are unconscious.
+Similarly, in the case of procedure memory, processes always rely on both the current environmental and system states to determine the next state of the processes\needref{Do I need ref??}.
+The information flow from the environment to the system is crucial to guide the state transition of procedural memory.
+Therefore, information processing of procedural memory also fails to achieve high NTIC and remain unconscious.
+
+             This type of processing is similar to the model-free policy-based agents in the reinforcement learning framework.
 The agent learns a policy $\pi$ which directly maps sensor values $S$ to output action $A$.
@@
 
-    		This can explain why the patient D.F., who has apperceptive agnosia, can perform online motor controls without visual awareness of the action targets  \citep{10.3389/fneur.2014.00255}.
-    		Our theory also explains why the unconscious processing in this category often fail when long delay periods are introduced in the tasks.
-Because without self-predicitve information in NTIC, the policies of motor outputs largely depends on the present sensory states implying that this type of processes can only perform online.
-With certain delays, sensory information is unable to guide the delayed motor outputs and leads to failure consequences.
-
-    		Finally, an interesting implication from our theory is that a pure feedforward neural network cannot be conscious because there is no way to maintain any form of memory of a system and such that there is zero influence from the system past states to its future state.
-On the contrary, with recurrent loops, a neural network can create information channels from its past to its future and becomes capable of achieving NTIC.
-This result coincide with some theories of consciousness which hypothesise the recurrent neural circuits as the NCC \needref{recurrent and NCC}.
-However, we derive this conclusion from a more fundamental informational-related hypothesis showing that our theory has a stronger explanatory power.
-\rlend
-
-        \subsubsection{Fail to meet 2\lowercase{ed} condition}
+    		Our theory can explain why the patients with visual apperceptive agnosia (e.g., the famous case D.F.\cite{james2003ventral}) can perform online motor controls without visual awareness of action targets \citep{10.3389/fneur.2014.00255}.
+The online visual information can be used to perform functional actions without forming a NTIC process.
+Our theory also explains why unconscious processes in this category often fail when a long delay periods is introduced in the tasks.
+Without self-predictive information in NTIC, the policies of motor outputs largely depends on the present environmental and sensory states implying that this type of processes often can only work online.
+With a long, sensory information is unable to guide the delayed motor outputs and leads to failure consequences.
+
+    		Finally, an interesting implication from our theory is that a pure feedforward neural network cannot be conscious because it is unable to maintain any form of memory so that there is no influence from the system past states to its future state.
+In contrast, with recurrent loops, a neural network is able to create information channels from its past to its future states and becomes capable of achieving NTIC.
+This result coincides with some theories of consciousness which emphasize the importance of recurrent circuits to consciousness \citep{lamme2006towards, edelman1992bright, tononi2008neural}.
+    		% if more references are needed, check Eklund_2012_RECURRENT PROCESSING AND THE CONSCIOUSNESS.pdf
+    		However, we derive this conclusion from a more fundamental informational-related hypothesis indicating the more generalised principle behind it.
+
+        % ---------------------------------------------------------------------------- %
+        %                                Fail to meet 2                                %
+        % ---------------------------------------------------------------------------- %
+
+        \subsubsection*{Fail to meet the 2\lowercase{ed} condition}
+        As mention above, information is level-dependent and can be virtually independent (closed) across different coarse-graining scales.
+If processes at some levels of a system are able to achieve high NTIC and become conscious, information at other levels still remains unconscious.
+The first implication of this argument is that processes at levels with high stochasticity are unable to achieve high NTIC and, therefore, unconscious.
+High stochasticity corrupts informational channel capacity and leads to low mutual information between past and future states of a process.
+In the neural system, the cellular level activities are highly noisy and are unable to reach high NTIC.
+Therefore, the information processed by the microscopic levels in the neural system are not conscious and we never can experience detail activities in the microscopic levels.
+
+        We argue that many mysterious results in previous research of consciousness are originated from inappropriate biological and behavioural measurement scale.
+In the following, we list some examples.
+
+        Unconscious processing in this category of
+
+        @ Evidence suggests that the neural system is able to encode probability distribution and perform probabilistic inference in a near optimal way\needref{bayesian brain}.
+However, an intriguing fact is that we are nearly ignorant of all the probabilistic computation of the inference processes but are only aware of "a sample" of the posterior distributions of the inferences \citep{dehaene2017consciousness, vul2009attention, asplund2014attentional, vul2008temporal, moreno2011bayesian}.
+The information of all alternative possible states is unable to enter conscious contents.
+In short, one needs to explain why the neural system can hold the joint probability distributions of inferred variables but, however, only a realisation of the inference outcome becomes conscious.
+Based on our theory, we argue that the computation of statistical inference is carried out at microscopic levels of the neural system and the NTIC process correlated with conscious contents only possesses the coarse-grained information of the computation.
+The mapping from the microscopic to macroscopic states naturally leads to a single and stable state at the macroscopic levels.
+
+        For example, Fig. \ref{fig:TemperatureExample} illustrates the relationship 
+        At the left panel, two cups contain water with different volumes $V_t$ and temperatures $T_t$.
+Even though we know volumes and temperatures are coarse-grained macroscopic variables, the states of mixed water ($V_{t+1}$, $T_{t+1}$) can still be predicted without knowing any information from the microscopic levels (the molecular level),i.e., the information closure at the macroscopic level.
+Similarly, taking Bayesian inference as an example, the microscopic neuron populations are able to represent probabilistic distributions about inferred target variables and the neural networks perform the statistical inference to obtain the posterior distributions.
+However, enormous microscopic neural states can be coarse-grained into the same state of summary statistics (e.g., the mean $\mu_{t}$  and standard deviation $\sigma_{t}$) at a macroscopic level.
+The state transition ($\mu_{t+1}$ and $\sigma_{t}$) is also predictable without any additional information from microscopic levels.
+Therefore, consciousness can only "observe" the coarse-grained states without the knowledge of how the statistical inference is implemented and performed at the microscopic levels.
 
@@
 		\end{figure}
-\rlstart{3}        
+
+        The same scenario can be applied to the results from Libet's volition experimental paradigm \citep{Libet1983TimeOC, Libet1985Dec}.
+Experiments using similar procedures usually show that the recorded neural activities start earlier than subjects' feeling of their own intention to act in the self-determined experimental settings.
+We argue that free actions are initiated at the microscopic levels, for example, the random fluctuation in the neural system \citep{schurger_accumulator_2012}.
+However, the feeling of volition is information at the macroscopic level with NTIC.
+Due to the information closure, there is no way for the NTIC process to observe the information of the microscopic states, i.e.
+the initiation of actions.
+
+        \idea{Not sure if I want to address this point}  Note that, some evidence suggests single-cell-level correlation of conscious experience, the Jennifer Aniston cell for example \citep{Quiroga2005Jun, Quiroga2012Jul}.
+This may seem to counter our argument that single-cell level information is incapable to be conscious.
+However, first, the correlations are always not the direct microscopic state changes of the cells, e.g.
+the action potentials.
+Instead, the correlated variables are always coarse-grained.
+The neuronal firing rate, for example, is a temporal coarse-grained variable.
+Second, it has been well established that heterogeneous nonlinearity is critical for neural populations to encode rich and high dimensional information.
+\citep{Chelaru2008, Rigotti2010Oct, Shamir2004Jun}.
+It is common to detecting a single neuron whose activity profile well align with a subspace which represents a single object within the state space of a population code.\needhelp{Maybe need to rewording here} We believe that multi-scale data and analyses are needed to elucidate whether single neuron behaviours are sufficiently representative for any type of conscious experience.
+
 		\begin{ants}
-                @ Due to the coarse-grained level-dependence of information processing, if a process is not at levels achieving NTIC, the information remains unconscious.
-
-        	    @ Even though a system can form NTIC processes at some certain coarse-grained levels, information processing outside these levels remains unconscious.
-
-        	    @ The first implication from this scenario is that processes at levels with high stochasticity are unable to achieve high NTIC and hence unconscious.
-High stochasticity corrupts informational channel capacity and leads to low mutual information between past and future states of a process.
-
-        	    @ In the neural system, the cellular level activities are highly noisy.
-
-        	    @ This prevents information from cellular activities from forming high NTIC processes.
-
-        	    @ Therefore, we never can be aware of detail activities at microscopic in the neural system.
-
-        	    @ Some may argue that empirical evidence suggests single cell level correlation of conscious experience, the Jennifer Aniston cell for example.
-
-        	    @ However, to note that, the correlation is always not the microscopic state changes of the cells, e.g.
-the action potentials.
-Instead, the correlated variables are always coarse-grained, for example the firing rate which is temporal coarse-grained variables.
-
-        	    @ Second, it has been well established that heterogeneous nonlinearity is crucial for neural populations to encode rich and high dimensional information.
-\citep{Chelaru2008, Rigotti2010Oct, Shamir2004Jun}.
-Finding a single neuron whose activities align with a subspace representing a single object within the state space of a population code.
-\ideaCallout{Not sure if I want to add this point}
-
-        	    @ This also explains why we are not aware of probabilistic inference performed by the neural system but only a "sample" of W
-
-        	    @ Previous studies have showed that the neural system is able to encode probability distribution and perform probabilistic inference in a near optimal way.
-
-        	    @ However, we are ignorant nearly all the computation when the neural system performs probabilistic inference.
-
-        	    @ Fig.
-\ref{fig:TemperatureExample} showed that because the computation is performed at microscopic levels, only the macroscopic variables, e.g.
-the summary statistics, are at the level with NTIC and become conscious.
-
-        	    % Libet's experient
-
-        	    @ The same scenario can also explain the results of Libet's experiment.
-In this experiment, in this experiment, Libet found that the neural activities (indicated by event-related potential) start earlier than the feeling of intention to perform an self-determined action.
-
-        	    @ \citeauthor{schurger2012accumulat}
-
-        	    @ The movement preparation initiates at the microscopic level.
-
-        	    @ However, coarse-graining always maps a larger state space at microscopic levels to a equal or smaller state space at macroscopic levels (i.e.
-a surjective function).
-As the result, the state transitions at microscopic levels do not always lead to state transitions at macroscopic levels.
-
-        	    @ Therefore, the initiative neural correlates of the free motor actions remained unconscious until the macroscopic state transition at the NTIC level.
-
+        	@ \idea{Should I write the following points? Is this too much?}
+        	@  === boundary conditions  === 
         	% multistable perception
-        	    In the case of multistable perception, at every moment, only a single macroscopic state is mapped from the microscopic levels, we can only be aware of one interpretation at every moment.
+        	    @ In the case of multistable perception, at every moment, only a single macroscopic state is mapped from the microscopic levels, we can only be aware of one interpretation at every moment.
 
@@
 
-        	   @  === boundary conditions  ===
         	   @ The third category is the boundary conditions.
@@
 
+		\subsection{Conscious Processing}
+		When the both conditions are fulfilled, our theory suggests that the states of a NTIC process correspond to particular conscious contents and the information incorporated in the NTIC process is conscious.
+Due to the predictive nature about the environment dynamics of NTIC processes, to achieve high NTIC and to construct functions within the process have a huge evolutionary advantage.
+It is important to emphasise that our theory does not suggest any functionalism of consciousness.
+Rather, we argue that information fundamentally associates with consciousness.
+Nevertheless, consciousness research still suggests a strong functional relation between consciousness and some specific types of cognition and behaviours \citep{Seth2009Encyclopediaofconsciousness}.
+We believe that this relation comes from several special properties of NTIC and these properties support the foundations of many cognitive functions in the neural system.
+
+		First, a NTIC process encodes predictive information about environmental dynamics.
+This is crucial for constructing forward models for predicting future states of the environment.
+Therefore, cognitive functions which require agent-scale prediction are likely to be accompanied by conscious experience.
+This properties is required by planning and also achieving long term goals.\needref{}
+
+		Second, a NTIC process can be considered as a close form simulation machine.
+With a given initial state, the process can self-evolve and follow a certain trajectory in the state space.
+This trajectory can be seem as a simulation about the environmental transition.
+Therefore, a NTIC process can serve cognitive functions as a perfect simulation engine \citep{BERTSCHINGER.2006}.
+Accordingly, mental simulation, imagination, computing alternative realities, and generating counterfactual outcomes can be implemented with a NTIC process.
+\needref{}
+
+	    Third, an important properties of NTIC processes is its high stability.
+The state transitions and trajectory are highly predictable.
+In such case, NTIC processes are more suitable for integrating information across larger time scales (above millisecond).
+Therefore, tasks which require to integrate information across time above the millisecond scale are often associated with conscious experience.
+
+	    Fourth, a NTIC process as a closed system can still provide predictive information without new information flowing into the process. This is crucial for many types of off-line processing.
+
+	    Fifth, any state of a NTIC process can be seem as a integration of multiple sources of information.
+For the human scale activities, to know certain transition about the environment, the NTIC process must include a high dimensional information from multiple modalities and have the knowledge about how the high dimensional data interact to each other.
+Without the knowledge and information, a process may not be capable of produce a stable state transitions which mimic the environmental dynamics.
+Thus, cognitive functions requiring this large scale integration are likely to be conscious.
+Furthermore, the high dimensional integrated information is also critical for an agent to learn new behaviours to achieve flexibility and the strategic behavioural controls and decision-making.
+
+	    In sum, we argue that having a NTIC process is critical for survival in the evolution.
+It is likely that biological creatures acquired NTIC process at some stages in the evolution.
+And due to the fundamental relationship between information and consciousness, these biological agents also acquired different degrees of consciousness depending on the physical scales and the complexity of the environments they live in.
+Our theory well explains why some processes and functions in the neural system are conscious and some are not with only two parsimonious conditions.
+
 		\begin{WritingMaterials}
-
-                @ \rewrite{Such unconscious systems compute with probability distributions, but only a single sample, drawn from this probabilistic distribution, becomes conscious at a given time ( 27 , 28 ).
-We may become aware of several alternative interpretations, but only by sampling their unconscious distributions over time ( 29 , 30 ).}
-
-            \end{WritingMaterials}
-
-\rlends
-
-		\subsection{Conscious Processing}
-
-		To achieve high NTIC has evolutionary advantage.
-When a process achieves NTIC, the current state of the process contains the information about its future state (Eq.
-(5)).
-Therefore, the neural system can build forward models to predict the future state of the environment using the information encoded in the NTIC process.
-Cognitive functions recruiting forward models built upon it are conscious.
-(E.g., planning and imagination)
-
-		It is important to note that we do suggest any functionalism of consciousness.
-Rather, we believe that information is fundamentally linked to consciousness.
-The reason why consciousness is accompanied with some specific cognitive function is because NTIC is a powerful property that brings creatures a lot of advantage in the evolution \cite{Seth2009Encyclopediaofconsciousness}.
-
-		\begin{ants}
-		    @ If both conditions are satisfied, information within the NTIC process becomes conscious. 
-		    @ Our theory suggests that conscious processing should be linked to cognitive functions that require forward models and predictive information \critical{Need to list items vary carefully here.}
-
 		    @ Previous research has identified a set of perceptual and cognitive functions which not exclusively but frequently associate with consciousness.
@@
 
-		\end{ants}
-
-	    \begin{WritingMaterials}
+            @ =============================================================================
+
 	        @ importantly, evidence suggests that those functions in some conditions do not require the involvement of consciousness.
@@
 
-		\subsection{Unconscious Processing}
-		When processes fail to satisfy either of the two conditions, they remain unconscious.
-First, when processes do not meet the first condition, i.e.
-the information processed not at the certain coarse-grained level, the information will not be included in conscious contents.
-For example, we are never conscious of neural spike activities at microscopic levels (e.g.
-single cell activities) because information passing among individual neurons are not at the certain coarse-grained level.
-\todo{Rewording}Libet's free will experiment can be also explained by our theory.
-The random neural fluctuation under Libet's free will experiment happens at the microscopic scale \citep{SchurgerE2904}.
-
-		Second, when processes do not meet the second condition, i.e.
-processes which do not achieve high NTIC will remain unconscious.
-This can explain why many "policy-based" processes are not conscious.\todo{Need a better term/way here} Policy-based here features those processes taking sensory information as input and directly outputting actions.
-Therefore, the future states of policy-based processes largely depend on the environmental states and failed to achieve informational closure.
-Neural processes are included in this category, e.g.
-reflexive neural circuit, blindsight, procedure memory.
-
-		To summarise, our theory can well explain the various findings with parsimonious assumptions.
-
-	    \begin{ants}
-	        @ \rewrite{the nonsemantic processing of primes is enhanced and priming effects are boosted when the experimental context allows the formation of automatic stimulus–response mappings.}\cite{VandenBussche2009}
-	    \end{ants}
-
+% ============================================================================ %
+%                        Comparison with other theories                        %
+% ============================================================================ %
 	\section{Comparison with other theories}
-		\ideaBox{Main points should be same/diff, our advantages, and predictions}
-		In this section, we will discuss the relationship between our theory and other popular modern theories of consciousness.
-
-\rlstart{2}
+	In this section, we compare our theory with other popular modern theories of consciousness. 1
+
 		\subsection{Theories about multilevel views on consciousness and cognition}
-        Previously, multilevel views on consciousness and cognition have been proposed.
-We shortly describe two theories which is \todo{XXX and XXX} related to our current proposal.	% We discussed the differences between our theory and other theories about multilevel views.
-
-            \subsubsection{level of Organisation \cite{wimsatt1994ontology}}
+		Previously, similar to our theory, several multilevel views on consciousness and cognition have been proposed. We shortly discuss two theories relevant to our current proposal.
+            \subsubsection*{Level of Organisation \cite{wimsatt1994ontology}}
                 As mentioned previously, the level of coarse-graining is different from the anatomical level.
@@
 
-			\subsubsection{Intermediate Level Theory} \label{IntermediateLevelTheory}
-                One important theory linking consciousness to multilevel views is the Intermediate Level Theory (ILT).
-ILT proposes that conscious experience only correlates specific levels of representations in the sensory processing the hierarchy.
-This theory claims that consciousness only associates with the representation at intermediate levels rather than the ones at lower-level or higher-level discribed as 2.5D.
-However, ILT focuses on the levels in terms of anatomical direction.
-As mentioned previously, a critical difference between ILT and our theory is that our theory doesn't assume the direction of coarse-graining should align with the direction of anatomical processing levels along cortical hierarchies (see fig \ref{fig:hierarchy}).
-
-                Different from ILT which suggests that the neural substrates responsible for the 2.5D computation is conscious, we predict that if information that is carried by v1 neurons are necessary to complete informational closure, the states of V1 neurons should also co-vary with conscious contents.
-
-			\subsubsection{Pennartz's neurorepresentational theory (Neurorepresentationalism)}
-			    Our theory shares some similar concepts with Pennartz's Neurorepresentationalism.
-However, Neurorepresentationalism focuses on multimodal representation \cite{pennartz2018consciousness,pennartz2015brain}.
-Another focus of neurorepresentationalism is on "making sense" between representations\todo{Need something here}.
-Different from neurorepresentationalism, conscious contents in our framework are grounded by the informational relations between variables in NTIC because NTIC provides a closed relationship between states in a system.
-
-			    Similar to Neurorepresentationalism, our framwork is more close to Marr ’ s original distinction between the levels of (neural) implementation, algorithms, and computational theory [122], but focuses on how conscious representations correspond to computational operations at levels with lower complexity and representational capacity.\cite{pennartz2018consciousness,pennartz2015brain}
-
-			    Neurorepresentationalism is also a functionalist perspective.
-However, e don't assume any functional properties as the criteria of consciousness.
-Instead, we propose information as a more fundamental principle correlates consciousness.
+			\subsubsection*{Intermediate Level Theory} \label{IntermediateLevelTheory}
+                One important theory tries to connect consciousness to multilevel views is the Intermediate Level Theory (ILT, \cite{jackendoff1987consciousness, prinz2007intermediate}).
+ILT proposes that conscious experience only correlates specific levels of representations in the hierarchy of sensory processing.
+ILT claims that consciousness only associates with the representation at intermediate levels (e.g., the 2.5D representation in terms of visual processing) rather than the ones at lower-level or higher-level.
+                One fundamental difference between ILT and our theory is the definitions of the level.
+In our theory, level is within the context of coarse-graining.
+However, ILT focuses more on the levels in terms of anatomical direction (see fig \ref{fig:hierarchy}).
+As mentioned previously, we emphasise that we doesn't assume the direction of coarse-graining should align with the direction of anatomical processing levels along cortical hierarchies.
+This leads to an important difference that the level of coarse-graining exists virtually.
+However, the level of cortical representation should be referred to neural substrates.
+Finally, different from ILT which suggests that some neural substrates responsible for the 2.5D computation are conscious, we predict that once information carried by coarse-grained variables is involved in the NTIC process, brain areas, not exclusively within 2.5D representation, should  co-vary with conscious contents.
+
+			\subsubsection*{Pennartz's neurorepresentational theory (Neurorepresentationalism)}
+			    Our theory shares some close concepts with Pennartz's Neurorepresentationalism \citep{pennartz2018consciousness,pennartz2015brain}.
+Similar to Neurorepresentationalism, our framework is also close to Marr's original distinction between the levels of analysis \citep{marr1982vision, pennartz2015brain, pennartz2018consciousness}.
+However, a fundamental difference between the two theories is that Neurorepresentationalism takes more functionalist point of view and suggests NCC should serve high-level world-modeling and makes a best guess about the interaction between the body and the environment.
+Neurorepresentationalism also suggests conscious experience is associated with integrated representation for multimodal and situational information.
+Out theory suggests that the association between the functions mentioned in Neurorepresentationalism is rooted in the more fundamental relationship between information and consciousness in which NTIC plays an important role.
 
@@
 Cells in V1 are not promising candidates, because they do not reliably respond in ways that are consistent with features that we experience consciously.
-} \cite{prinz2007inter    mediate}
+} \cite{prinz2007intermediate}
 
@@
 Th ese notions are all in need of some refi nement, but, as a fi rst approximation, the idea is that intermediate- level representations are neither too specifi c nor too general.}\cite{prinz2007intermediate}
-
-				%% Our theory
-				@ However, as we mentioned in Section \ref{sec:SensoryHierarchy}, \rewrite{The notion of ‘ levels ’ deployed here is functional and very different from that of successive anatomical processing stages along cortical hierarchies [75] or from anatomic scales in the brain.
-The multi-level concept in [2] is more akin to Marr ’ s original distinction between the levels of (neural) implementation, algorithms, and computational theory [122], but focuses on how conscious representations correspond to computational operations at levels with lower complexity and representational capacity.}\cite{pennartz2018consciousness,pennartz2015brain}
 			\end{WritingMaterials}
 
-\rlend
-
-\rlstart{2}	
 		\subsection{First-order theories}
             The first-order theories suggest that consciousness is determined by early sensory information or neural activities\needref{First-order theories}.
-The first-orde view maintains that conscious awareness is determined by early sensory activity alone, independently of higher-order representations.
-\rewrite{According to first-order views, phenomenal consciousness consists in analog or fine-grained contents that are available to the first-order processes that guide thought and action.
-So a phenomenally-conscious percept of red, for example, consists in a state with the analog content red which is tokened in such a way as to feed into thoughts about red, or into actions that are in one way or another guided by redness.}
-
-            We predict that, if early sensory information or neural activities after coarse-graining take parts in the NTIC process, early sensory information or neural activities also contribute consciousness.
-However, due to coarse-graining, changes of early sensory information or neural activities do not necessarily accompany with changes of conscious contents.
-\todo{Need more here, espectially more counterintuitive predictions}
+The first-order view maintains that conscious awareness is determined by early sensory activity alone, independently of higher-order representations.
+            First-order theories suggests that phenomenal consciousness is associated with fine-grained contents for the first-order processes.
+Different from the first-order theories, our theory suggests that, whether the early sensory activities show in the conscious content, it depends on information encoded in the early sensory areas is recruited in the NTIC process at the macroscopic level or not.
+As we mentioned in \ref{sec:Unconscious Processing}, if the sensory activities are only passively triggered by the environmental states, they are not able to form hign NTIC and remain unconscious.
+We predict that, if early sensory information or neural activities after coarse-graining take parts in the NTIC process, early sensory information or neural activities can contribute conscious content.
 
@@
 
+				@ However, due to coarse-graining, changes of early sensory information or neural activities do not necessarily accompany with changes of conscious contents.
+\todo{Need more here, espectially more counterintuitive predictions}
+
 			\end{WritingMaterials}
-
-\rlend
 
@@
 		\subsection{Higher Order Thought theory of consciousness}
-		    In contrast to first-order theories, higher-order thought theories suggest that consciousness depends on higher-order representations representing agents as being in particular internal states.
+		    \ideaBox{Okay, I don't know how to deal with HOT now. I don't understand it at all}
+		    In contrast to first-order theories, higher-order thought theories suggest that consciousness depends on higher-order representations which represent agents as being in particular internal states \citep{lau2011empirical}.
+First-order processing needs to be observed or represented by a higher-order observer to become conscious.
+
 		    Meta-cognition is also associated with many conscious cognitive function.
@@
 I need to rewrite this part}.
-This may be the result of neural coarse-graining.
-Because contents in informational closure look like watching fine-grained information, people may have an wrong impression about it.
+
+		    This may be the result of neural coarse-graining. Because contents in informational closure look like watching fine-grained information, people may have an wrong impression about it.
+
 		    Coarse-grained information can be summary statistics which may be misunderstood as higher-order representation.
@@
 			\begin{WritingMaterials}
+			@ Good reference: \myQuote{Higher- Order Th eories of Consciousness; PETER CARRUTHERS (The Blackwell Companion to Consciousness (Blackwell, 2007))}
+
 		    @ In contrast to first-order theories, higher-order thought theories suggest that consciousness depends on higher-order representations representing agents as being in particular internal states.
@@
             @ ============================================================================
-			@ \rewrite{
-				Higher-order theories of consciousness argue that conscious awareness crucially depends on higher-order mental representations that represent oneself as being in particular mental states.} \cite{lau2011empirical}
 
@@
 		\subsection{Global workspace theory}
-		Global workspace theory (GWT)\cite{baars1988cognitive, baars1997theatre, baars2002conscious} or Global Neuronal Workspace theory (GNWT)\cite{dehaene1998neuronal, dehaene2001towards, dehaene2011experimental} states that the neural system consists of many separate specialised modules and a central global workspace (GW) which integrates and passes information amount the modules.
-Only the information that is accessed by the global workspace can be conscious aware of.
-The modules competes with each other to gain the access to the global workspace and the information from the winner can trigger an all-or-none "ignition" in the global workspace and be globally broadcasted to other modules.
+		\ideaBox{Need ending and better difference }
+		Global workspace theory (GWT; \cite{baars1988cognitive, baars1997theatre, baars2002consciousk}) or Global Neuronal Workspace theory (GNWT; \cite{dehaene1998neuronal, dehaene2001towards, dehaene2011experimental}) states that the neural system consists of several specialised modules and a central global workspace (GW) which integrates and broadcasts information amount these modules.
+Only the information accessed by the global workspace can be consciously aware of.
+These modules competes with each other to gain the access to the GW and the information from the winner can trigger an all-or-none "ignition" in the GW.
+Information in the GW is able to be broadcasted to other modules.
 Conscious contents then associates information which gains access to the internal global workspace \cite{Dehaene2017}.
-Our framework can well accommodate and interpret these claims by GWT.
-
-		Stability: Conscious perception necessitates representational stability. Our theory rests upon self-predictability which formally encompasses stability.
-
-		Broadcasting: When new sensory information from a modality is involved in NTIC, the information can be preserved in the following dynamic of NTIC.
-The neural system can extract the information for specific task goals.
-This is equivalent to the function of broadcasting.
-
-		Non-linear ignition: Because mapping microscopic to macroscopic states is many-to-one, it commonly shows a nonlinear relationship between microstates and macrostates.
-In our theory, new information presents in conscious perception corresponds to a transition in the state space of the NTIC process.
-This can cause a significant change of the brain states and resembles non-linear ignition of brain activities.
-Conscious access as an accumulation of evidence leading to an all-or-none ignition What, if anything, remains unique to conscious processing?
-Although many cognitive operations can be partially launched non-consciously, these operations rarely if ever run to completion in the absence of consciousness.
-A subliminal stimulus may induce above-chance performance, behavioural priming, and a small amount of brain activity in narrowly defined brain networks, but these measures often increase dramatically as soon as the subject reports seeing the stimulus, especially in high-level areas [46 60,61  ].
-Accumulation of evidence has been demonstrated with non-conscious stimuli [59], but only conscious stimuli cross the threshold beyond which an overt strategy can be fiexibly deployed.
-\todo{Cite similar opinion from other theories}
-
-		A difference between our theory and GWT is that our theory does not suggest a neuronal core anatomical area for consciousness.
+
+		In many aspects, our theory can well accommodate GWT.
+NTIC processes shares several properties with the GW.
+Here we discuss three core properties, stability, broadcasting, and non-linear ignition, emphasised by the GWT.
+
+		% === Stability ===
+		Stability: GWT indicates that the conscious contents often show stronger stability which may be necessary for the neural system to integrate information from a variety of modules.
+Suggested by GWT, this is caused by top-down amplification from the GW to individual modules which gain the access to the GW \needref{}.
+In contrast, without assuming any additional mechanism, our theory argues that stability is a natural quality of NTIC due to its strong self-predictive characteristic.
+Our theory can even further quantify the stability of conscious contents by computing the mutual information between the current and the future states of a conscious process.
+
+		% === Broadcasting ===
+		\idea{A bit not sure about this part}Broadcasting: Because individual modules use different coding schemes, the neural system requires a mechanism for passing information between modules.
+GWT suggests that the GW is responsible for connecting the information source, translating the code, and finally making the information globally accessible.
+We argue that, because the NTIC process encodes high dimensional information about the environmental dynamics, it can be considered as an integrated informational entity \todo{Need rewording}.
+These with the coarse-graining variables involved in the NTIC process together.
+Other modules outside the NTIC process can decode and extract needed information for the current goal of the task.
+
+        % === Non-linear ignition ===
+        Non-linear ignition: Non-linear ignition: Because mapping microscopic to macroscopic states is many-to-one, it commonly shows a nonlinear relationship between microstates and macrostates \needhelp{Is this statement correct?}.
+Therefore, a continuous state transition at microscopic levels may lead to a discrete and non-linear state transition at macroscopic levels.
+Based on our theory, when new information enters conscious contents, the NTIC process must undergo a corresponding state transition.
+This transition can trigger a significant change of the brain states and resembles non-linear ignition of brain activities.
+
+		% -------------------------------- Difference -------------------------------- %
+		\todo{Finish this part}
+		However, there are still fundamental differences between the two theories. 
+		In GWT, modules rival with each other to gain access to the GW.
+Our theory suggests that the one enters conscious contents is the one which can create the higher NTIC with other coarse-grained information.
+This difference leads very different predictions and implications.
+For GWT, to find the biological implementation of the rivalry mechanism (attention, for example) is critical.
+However, we do not assume any rivalry mechanism.
+Instead, we argue that, if  information carried by the coarse-grained variables can increase the predictability of the process and form high NTIC,  it naturally form a informational closed boundary and
+
+		Up to now, GWT does not indicate a firm criteria of the boundary of GW. It is difficult to determine the expanse of the GW.\todo{Do something here}
+
+		Another difference between our theory and GWT is that our theory does not suggest a neuronal core anatomical area for consciousness.
 \todo{Link to Section 4}.
@@
 
+		In sum, our theory is compatible with previous physiological evidence supporting GWT.  
+\rlend
 		\begin{WritingMaterials}
-			%% Introduction
-			@ Global workspace theory (GWT)\cite{baars1988cognitive, baars1997theatre, baars2002conscious} or Global Neuronal Workspace theory (GNWT)\cite{dehaene1998neuronal, dehaene2001towards, dehaene2011experimental} states that the neural system consists of many separate specialised modules and a central global workspace (GW) which integrates and passes information amount the modules.
-Only the information that is accessed by the global workspace can be conscious aware of.
-The modules competes with each other to gain the access to the global workspace and the information from the winner can trigger an all-or-none "ignition" in the global workspace and be globally broadcasted to other modules.
-Conscious contents then associates information which gains access to the internal global workspace \cite{Dehaene2017}.
-
-			@ Submodule access and NTIC
-
-			%% Our theory
-
-			@ Our theory can well accommodate several claims by GWT.
-
-			@ Conscious perception necessitates representational stability: Our theory rests upon self-predictability which formally encompasses stability.
 
@@
 
-			@ Non-linear ignition: Because mapping microscopic to macroscopic states is many-to-one, it commonly shows a nonlinear relationship between microstates and macrostates.
-In our theory, new information presents in conscious perception corresponds to a transition in the state space of the NTIC process.
-This can cause a significant change of the brain states and resembles non-linear ignition of brain activities.
-
-			@ our theory re-explains the critical xxx from GWT.
-
-			@ The critical difference is that our theory does not suggest a neuronal core anatomical area for consciousness. We suggest coarse-grained information form NTIC is crucial for consciousness.
-
-			@ In sum, our theory is compatible with previous physiological evidence supporting GWT.
-
-		\end{WritingMaterials}
-
-% 			\subsubsection{Global availability and Broadcasting}
-% 			\subsubsection{Stability}
-				\begin{WritingMaterials}
 			@ the presence of contexts as stable coalitions shaping access to the workspace.
 
-					@ e ‘all-or-none’ behavior, whereby the incoming evidence either quickly dies out (corresponding to subliminal processing) or is accumulated and amplified non-linearly into a full-blown state of high-level activity.
+			@ e ‘all-or-none’ behaviour, whereby the incoming evidence either quickly dies out (corresponding to subliminal processing) or is accumulated and amplified non-linearly into a full-blown state of high-level activity.
 This global ‘ignition’ has been proposed as a marker of conscious perception [70].
 Indeed, empirically, when stimulus strength is varied, the early stages of non-conscious processing typically show a linear variation in activation, whereas conscious access is often characterized by a late non-linear amplification of activation which invades a distributed set of parietal, prefrontal and cingulate areas
-				\end{WritingMaterials}
-
-% 			\subsubsection{Broadcasting}
-
-			\subsubsection{Ignition}
-				\begin{WritingMaterials}
+
 			@ Conscious access as an accumulation of evidence leading to an all-or-none ignition What, if anything, remains unique to conscious processing?
@@
 Accumulation of evidence has been demonstrated with non-conscious stimuli [59], but only conscious stimuli cross the threshold beyond which an overt strategy can be fiexibly deployed.
-				\end{WritingMaterials}
-
-			\begin{WritingMaterials}
-				@ GWT is one of the current popular consciousness theories.
-
-				@ \rewrite{AI system and corresponds to our first functional definition of consciousness: global availability} \cite{Dehaene2017}
 
@@
 In this theory, each processor can operate in the conscious mode if it benefits from global broadcasting through the workspace, or it can operate in the unconscious mode when disconnected from the workspace.
-An important feature of the global workspace theory is the presence of contexts as stable coalitions shaping access to the workspace.
+An important feature of the global workspace theory is the presence of contexts as stable coalitions shaping access to qeqthe workspace.
 Contexts are constituted of unconscious processors reflecting, in a hierarchical manner, our expectations, our beliefs, our goals, and ultimately our self.
@@
 		\end{WritingMaterials}
-\rlend
 
@@
 Rather, the quality of conscious perception depends on agents' mastery of SMCs.
-It emphasises the interactions between a system (the neural system) and its environment are crucial to form conscious perception
-
-			\begin{ants}
-				%% SMC
-
-				@ Sensorimotor contingency (SMC) theory of consciousness is proposed to account of conscious perception.
-It suggests that different types of SMCs give rise to different characteristics of conscious perception \cite{o2001sensorimotor}.
-
-				@ The theory radically rejects the view that conscious contents is associated with information encoded in internal representations in the neural system.
-
-				@ Rather, the quality of conscious perception depends on agents' mastery of SMCs.
-
-				@ It emphasizes the importance of the interactions between a system (the neural system) and its.
-
-				@ Counter-intuitively, because consciousness inhabits in interactions between agents and environments, this theory suggests that consciousness is not driven by brain activities.
-Instead, consciousness should be shaped by the way of interaction, i.e.
-SMCs, between agents and environments.
-
-				%% Our theory
-
-				@ Similar to the SMC theory, our theory predicts that the interaction between the neural system and the environment shapes the quality of conscious perception.
-
-				@ This is because to achieve NTIC the neural system should maximise the conditional mutual information between the future state of the NTIC process and the environment given the agent's current action (see equation XXX \critical{I NEED A EQUATION!}).
-
-				@ This suggests the to maximise NTIC the NTIC process needs to involve the information about the environmental transition and dynamic after agent preforms an action.
-
-				@ Therefore, as a consequence of maximising NTIC, the representation forming NTIC implicitly encodes information about SMCs.
-
-				@ In the long-term, once NTIC neural dynamic interoperates the environmental state transition given actions via maximising NTIC, the state space of XXX then is shaped by the new learned SMC
-
-				@ Accordingly, the way how the agent interacts with the environment influences the structure of the NTIC representation.
-
-				@ \todo{Need to involve some sentence from  }
-
-				@ \idea{Do I need a figure here?}
-
-				@ However, in contrast to the SMC theory, our theory suggests the state of NTIC process correlate conscious contents.
-Therefore, if the NTIC process is formed inside the neural system, we should have correspondent conscious contents in our conscious experience without interacting with the environment.
-
-				@ \idea{Not sure here} This can easily explain that the conscious experience of dream is just induced by self-evolved state changes of the NTIC process.
-
-				@ Further more the SMC and our theories make complete different prediction about the relationship between SMC and consciousness.
-
-				@ Contrary to the SMC theory which suggests that consciousness resides on SMCs, our theory predicts that pure S-R contingency between the neural system and the environment can not achieve informational closure within the neural system and therefore is not conscious (please see section \ref{sec:reflexive})
-
-			\end{ants}
+SMC emphasises that the interaction between a system (the neural system) and its environment is crucial to form any specific form of conscious experience.
+
+	    Our theory in general rejects this proposal based on the fundamental assumptions of SMC.As we mentioned in \ref{sec:Conscious versus Unconscious Processing}, a process directly maps the sensory state space to the action space should not be able to achieve NTIC.
+Because learning of contingencies between sensory input and action output doesn't guarantee to form any NTIC process, our theory predicts that sensorimotor contingency is neither a necessary nor a sufficient condition for conscious experience.
+In fact, with extensive practice on a sensorimotor task with a fixed contingency, the task usually can be gradually performed unconsciously \needref{}.
+We believe that the neural system has established a process to directly map sensory evidence to action selection, and therefore, decrease the level of NTIC which against the basic assumption of SMC.
+
+	    Nevertheless, our theory does appreciate the notion that interactions between agents and environment is crucial to shape specific types of conscious experience.
+This is because, for an agent to form a NTIC process with action output, the process needs to encode how agents' actions influence state transitions in the environment.
+Therefore, information of interaction should be encoded in the NTIC process and also determines the state of NTIC which associates a particular conscious content.
+
+        Finally, it is worth to mention a recent new version of SMC called Predictive Processing of SensoriMotor Contingencies (PPSMC) proposed by \cite{seth2014predictive, seth2015presence}.
+PPSMC combines SMC and predictive coding framework together and emphasise the importance of action counterfactual (i.e.
+potential actions that an agent can perform) to conscious experience.
+To compute counterfactuals the existence of generative models is the prerequisite equipped by the agents.
+So far, PPSMC is deviating from simple $S\rightarrow{}R$ mappings and links the predictive information to consciousness.
+We argue that if predictive information for the computation of conterfactual is involved in the NTIC process, PPSMC may have strong explanatory power on some phenomenally special experience.
 
@@
 
+        % =========================== Predictive Processing ========================== %
 		\subsection{Predictive Processing}
-			\begin{ants}
-				%% Introduce PP
-				@ The predictive processing is a powerful framework (PP) which integrates several influential ideas in the history of neuroscience including "perception as unconscious inference" from Helmholtz \citet{helmholtz1866concerning}, "analysis by synthesis", “predictive coding”, "Bayesian brain hypothesis"
-
-				@ is a powerful framework
-
-				@ a recent emerged theoretical framework of perception and brain function, which suggests that the brain continuously generates and updates predictions about incoming sensory signals, represents a general principle of neural functioning.
-
-				@ According to predictive processing (PP) account of perception, the neural system constantly performs unconscious statistical inference about hidden causes in the external environment.
-The perceptual contents are the "best guess" about the environment 	\cite{clark_2013}			\cite{Hohwy2013}
-
-				@ Bperceptual content is the result of probabilistic inference on the hidden causes of sensory signals.
-
-				@ Because it is well integrated with Bayesian brain hypothesis, the PP framework has been used to interpret conscious perception in many perceptual domain. \cite{Hohwy2013} \cite{SethPP2014}
+    		Predictive processing is a powerful framework (PP) which integrates several influential ideas in the history of neuroscience including "perception as unconscious inference" from Helmholtz \citet{helmholtz1866concerning}, "analysis by synthesis", “predictive coding”, and "Bayesian brain hypothesis".
+This recent emerged theoretical framework of perception and brain function suggests that the neural system constantly generates predictions about incoming sensory signals and updates predictions based on prediction error between predictions and real sensory signals.
+According to PP, the neural system constantly performs unconscious statistical inference about hidden causes in the external environment.
+The perceptual contents are the "best guess" about the environment states including these hidden causes \citep{clark_2013, Hohwy2013}.
+Because it is well integrated with Bayesian brain hypothesis, the PP has been used to interpret conscious perception in many perceptual domain.
+\cite{Hohwy2013} \cite{SethPP2014}.
 
     		%% The gaps between pp and consciousness
-				@ However, to link PP to consciousness, there are still two major gaps.
-
-					@@ First, previous studies have demonstrated many brain processes following the principle of Bayesian inference and Bayesian integration.
-But not all these processes are conscious.
-This indicates that PP is not a sufficient mechanism for conscious perception.
-Some other factors may be involved to determine which PPs can be conscious or not.
-
-					@@ Second, it has been emphasized that only the results of the inference or prediction can be consciously accessed. The process of inference in completely unconscious. So WHY?
-
-				@ Even though PP has been acquiring attention in different discipline in neuroscience, So far, to our knowledge, no detailed explanation has been given to account for the two questions.
-
-				%% Our theory
-
-				% 2018/06/15 15:10
+    		PP is a powerful explanatory framework for diverse brain functions.
+However, to serve as a theory of consciousness, PP is still incomplete due to two theoretical gaps.
+First, there are enormous predictive mechanisms in the neural systems.
+It is  obvious that that not all the predictive information from these mechanisms is able to be part of conscious contents.
+Therefore, PP needs to explain the difference between conscious and unconscious predictive mechanisms.
+Second, if we closely look at a conscious predictive system, the only part can be consciously aware of is the result.
+Other details of the computation remain unconscious.
+PP also needs to explain how unconscious inferences is able to give rise to conscious results.
+In short, the two explanatory gaps prevent PP from been a complete theory of consciousness.
+
+    		Here, from more fundamental principles, we  argue that our theory is able to well fill the two gaps simply by considering the two conditions mentioned in section \ref{sec:Conscious versus Unconscious Processing}.
+
+    		First, predictive processes do not necessitate NTIC.
+A neural mechanisms is able to generate prediction does not guarantee it is an NTIC process.
+For example, an algorithm can take the current states of a target entity as the inputs and compute future states of the target.
+In this case, this algorithm can compute predictive information.
+However, the states of the internal variables are fully determined by the external input, implying that this algorithm is not informational closed.
+We suggests that if a predictive process is not a NTIC process, predictions from this process will not be able to show in conscious contents (i.e., fail to meet the 1\lowercase{st} condition in section \ref{sec:Conscious versus Unconscious Processing}).
+In contrast, predictive information in the NTIC process is conscious and makes the process achieve information closure.
+
+    		Second, as mentioned in section \ref{sec:Conscious versus Unconscious Processing}, if a process is not at the coarse-grained level achieving NTIC, this process will not be conscious (Fail to meet the 2\lowercase{ed} condition).
+We have provides an example in section \ref{sec:Conscious versus Unconscious Processing} in which computation can be implemented at microscopic levels.
+However, if the coarse-grained result of the computation is included in the macroscopic NTIC process, only the result rather than the process itself can be consciously aware of.
+Therefore, we predict that the statistical inferences under PP are implemented in microscopic levels.
+The NTIC process is ignorant to the detail information of their computations.
+
+            In sum, our theory provides fundamental reasons that strengthens PP as a theory of consciousness. Our theory well explains the relationship between predictive processing and consciousness.
+        \todo{Need ending}
+
+        \begin{WritingMaterials}
     		@ We first hypothesize that predictive processing stays unconscious is because it is not able to achieve NTIC.
@@
     		@ We hypothesize that the distinction between conscious and unconscious predictive mechanisms is whether they build up on the information from the NTIC process.
-
-			\end{ants}
-
-			\begin{WritingMaterials}
 
@@
 
-				@ Not all predictive mechanism are conscious.
-
-				@ We hypothesize that the distinction between conscious and unconscious predictive mechanisms is whether they build up on the information from the NTIC process.
-
-				@ we can also explain why only the result (posterior) of predictive processing is conscious.
-
-				@ Because of this XXXX, the representation has the maximal \ac{ntic} also has the maximal predictive power of the external environment. \todo[inline]{I need math here!!}
-
     		@ Therefore, it's reasonably assume that if evolution wants to build predictive mechanisms, the mechanisms should be settled on the information at the \ac{cged} level.
@@
     		@ Similarly, the neural system also has many circuits that show predictive power but do not have \ac{ic}.
-
-			\end{WritingMaterials}
-
-			\subsubsection{statistical learning/prediction is not conscious}
-				\begin{ants}
     		@ considers the brain as a predictive machine
@@
 
-						@@ Another scenario is a forward model but its state fully depends on external sensory input. This system is not informational closured and therefore is not conscious.
+    			@@ Another scenario is a forward model but its state fully depends on external sensory input. This system is not informational closed and therefore is not conscious.
 
@@
 
-						@@ For example, in active inference \needref{active inference}, action is guided by prediction error so the state of the system is non-closured.
-
-				\end{ants}
-
-\rlstart{1}
+    			@@ For example, in active inference \needref{active inference}, action is guided by prediction error so the state of the system is non-coloured
+	\end{WritingMaterials}
+
+        % ---------------------------------------------------------------------------- %
+        %                                      IIT                                     %
+        % ---------------------------------------------------------------------------- %
+
 		\subsection{Integrated information theory}
+		Integrated information theory (IIT) states that system's consciousness is determined by its causal properties.
+Consciousness is integrated information.
+As a computational theory of consciousness, the degree of discrimination and integration can be expressed in mathematical terms $\Phi$.
+Different from most of other scientific theory of consciousness, IIT asserts that the fundamental physical property associated with consciousness is causality.
+
+		% Similarity
+		IIT and our theory shares some common principles in many aspects.
+First common principle between our theory and IIT is that instead of NCC, both theories suggest information is the fundamental entity which correlates consciousness \needref{cite David Chalmers}.
+Therefore, both theories are capable of extrapolation and infer the states of consciousness in other systems beyond the human neural system.`
+
+		% Difference
+
 			\begin{ants}
@@
 
+			@ Different prediction!!!
+
 			\end{ants}
@@
 
-					@ Further instigation is needed to elucidate the relationship between our theory and causal emergence
+					@ Further examination of the Hoel's theory and our theory is needed to elucidate the relationship between our theory and causal emergence.
+
+					@ Both theory
 
@@
 
-\rlend
-
+        % =============== Internal simulation and self-modelling theory ============== %
 		\subsection{Internal simulation and self-modelling theory}
 
-    \section{Limitation}
-
-    \subsection{Finding potential coarse-graining functions}
-    To empirically verify the current theory, it is important to know what coarse-graining functions which maps microscopic variables to macroscopic variables in the neural system.
-So far, in this article, we have not speculated potential candidates of the coarse-graining function (or functions) that creates NTIC in the neural system.
+% ============================================================================ %
+%                                  Limitation                                  %
+% ============================================================================ %
+    \section{Limitation and Future work}
+        % Can't solve the hard problem
+        It's important to clarify that our theory does not intend to completely solve the hard problem of consciousness\citep{chalmers1995facing}.
+Our theory claim that different states of a NTIC process should map to difference conscious contents.
+However, knowing the state of a conscious process does not allow us to answer "What is it like to be this system"\citep{nagel1974like}.
+We can consider a simplified version of the inverted spectrum argument \citep{Shoemaker1982-SHOTIS, Block1990-BLOIE, Locke1979-LOCTCE-2}.
+Two NTIC creatures (Alice "$A$" and Bob "$B$") living in a simple environment($E$) which has only two states $E_1$ and $E_2$.
+In this simple case, Alice and Bob should have only two states ($A_1, A_2$ and $B_1, B_2$) when they achieve the maximal level of NTIC (i.e.
+1 bit).
+Our theory can only claim that Alice has different conscious experience $\hat{A}_1$ and $\hat{A}_2$ at state $A_1$ and $A_2$, respectively (same as for $\hat{B}_1$ and $\hat{B}_2$ map to $B_1$ and $B_2$).
+However, there is no way to know whether $\hat{A}_1$ is the same as $\hat{B}_1$ or $\hat{B}_2$.
+
+        Instead, we believe that this is an ill-posed problem.
+Assuming that one day we know $\hat{A}_1$ is or is not the same as $\hat{b}_1$, this implies that we acquire at least 1 additional bit of information to make this judgement which does not exist within this simple system.
+Therefore, our theory is unable to answer the subjective quality that a conscious system feel like.
+
+        % Finding potential coarse-graining functions
+        \needhelp{I think I need Martin's help here, I don't know how much we should say in this paper. Or just leave this to the future studies}
+        A major empirical difficulty of our theory is to find appropriate aggregation functions which map microscopic variables to macroscopic variables forming a NTIC process.
+In this paper, we do not speculate any form of aggregation functions.
+It seems very difficult to find an appropriate one among infinite candidates.
+Nevertheless, relevant research has been exploring the mathematical relationship between aggregation functions and macroscopic processes \citep{PFANTE.2014}.
 
@@
         \begin{ants}
-            @ Our theory does not intent to solve the Hard problems. 
-            @ Inverted spectrum Inverted Qualia \citep{Shoemaker1982-SHOTIS, Block1990-BLOIE, Locke1979-LOCTCE-2}
+        % ========================== Theoretical limitation ========================== %
+
+        @ ====
+        @ We believe that information is the fundamental channel connecting objective and subjective events.
+
+        @ Our theory cannot solve inverted spectrum argument
+
+        @ there are two one-bit NTIC process, our theory can not whether they feel the two states feel like black-white or black-red.
+
+        @ Assuming two NTIC agents live in a simple environment with only 4 possible states.
+Therefore, Only 2 bits are needed to achieve NTIC in this environment.
+Our theory can say they have very limited form of consciousness (2 bits).
+However, our theory is not able to tell you that whether their phenomenological experience is the same.
+
+        @ If we assume the outcome is we finally can know the feel differently.
+In this situation, we must acquire an additional bit from the system to answer this question.
+This is impossible because we already have complete information about the entire system.
+
+        @ ====
+
+        % Future work to overcome the limitation
+
+        % finding a suitable CG function
+
+        @ However, there are still some ways to narrow down the potential candidates. 
+        @ \cite{PFANTE.2014} reviewed 4 different methods of level identification (one of them is informational closure). 
+        @ The authors discuss potential 
+        @ These analyses help us to narrow down the range and target specific mathematical properties of the function
+
+        @ another possibility is that information in the NTIC process need to be readout for agents' action output.
+Therefore, investigating the decoder may also help to understand coarse-graining function.
+        1
+        @ Third, with artificial neural networks, which can be used as a universal function approximator, we are able to experiment and train the neural network with NTIC as the objective.
+And analyse the network topology of trained networked.
+
+        @ Finally, to revisit data may be helpful to identify the appropriate scale of measurements.
+
+        % =========================== Empirical Limitation =========================== %
+        % Empirical evidence
+        @ Since, NTIC to neuroscience is a relatively new concept, So far, no much empirical studies have examined this property in the neural system. 
+        @ The lack of 
+        @ Future studies should focus more on NTIC
+
+		\end{ants}
+
+        \begin{WritingMaterials}
+            % finding a suitable CG function
+            @ It's not clear what the coarse-graining function is.\critical{this should be explained by environmental deterministic}
+
+			@ \rewrite{
+				not all causal relationships (or relationships of nomological dependency) among micro-events aggregate up to causal relationships among coarse-grained macro-events that are constituted by those micro-events.
+Instead, whether one gets causation at the macroscopic level will depend (among other things) on the particular coarse-graining that is chosen.} \cite{price2007causation}
+
+			@ \rewrite{
+				It may seem surprising, even counterintuitive, that causal and statistical dependence relationships involving fine grained microscopic variables do not automatically show up in causal and dependence relationships among the macroscopic variables that are realized by the fine grained variables.} \cite{price2007causation}
+
+			@ \cite{jonas2017could} well demonstrated that it is difficult to understand higher-level information processing by the current neuroscience methods.
 
@@
 
-            @ Our theory does not explain the mapping
-        \end{ants}
-
-	\section{Future works}
-		\begin{ants}
-
-			@ Lack of direct evidence because no one focus on informational closure.
-
 			@ Physiological location of NTIC
@@
 
-		\end{ants}
-
-		\subsection{Finding coarse-grain function}
-			\begin{ants}
-				@ It's not clear what the coarse-graining function is.\critical{this should be explained by environmental deterministic}
-
-				@ \rewrite{
-					not all causal relationships (or relationships of nomological dependency) among micro-events aggregate up to causal relationships among coarse-grained macro-events that are constituted by those micro-events.
-Instead, whether one gets causation at the macroscopic level will depend (among other things) on the particular coarse-graining that is chosen.} \cite{price2007causation}
-
-				@ \rewrite{
-					It may seem surprising, even counterintuitive, that causal and statistical dependence relationships involving fine grained microscopic variables do not automatically show up in causal and dependence relationships among the macroscopic variables that are realized by the fine grained variables.} \cite{price2007causation}
-
-				@ \cite{jonas2017could} well demonstrated that it is difficult to understand higher-level information processing by the current neuroscience methods.
-
-			\end{ants}
-
-%	\section{Evolution of conscious mind (not sure but if I have time)}
-%		\cite{dennett2008kinds}
-
+		\end{WritingMaterials}
+
+% ============================================================================ %
+%                                  Conclusion                                  %
+% ============================================================================ %
 	\section{Conclusion}
@@
 			@ NCC: To find NCC, it's not about where and when, it's about scale and level of description
+			% scale dependent is critical 
 		\end{ants}
